### 2019-10-07 proposal/A-Talking/talk.tex
Initial commit

% Created 2019-09-26 Thu 12:44
% Intended LaTeX compiler: pdflatex
\documentclass[margin=0.05in, tmargin=0.01in]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{minted}
\usepackage[margin=1.5in, tmargin=1.0in]{geometry}
\author{Stanislav Arnaudov}
\date{\textit{<2019-09-26 Thu>}}
\title{Was muss gesagt werden}
\hypersetup{
 pdfauthor={Stanislav Arnaudov},
 pdftitle={Was muss gesagt werden},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.1 (Org mode 9.2.1)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section{Introduction}
\label{sec:org7efff8f}
Hallo, mein Name ist Stanislav und heute präsentiere ich euch den Forschung-Antrag zu meinem PdF Projekt.

\section{Motivation}
\label{sec:orga66f5f0}

\subsection{PDEs}
\label{sec:orgfc5d8d0}
Wir fangen mit der Motivation an. Ich beschäftige mich teilweise mit partiellen Differentialgleichungen. Die treten ganz oft in der Natur und Physik auf. Mit ihnen kann man numerische Simulationen durchführen, zum Beispiel von Strömungen. Bei diesen Simulationen geht es sogar um eine Folge von Gleichungen, die gelöst werden müssen. Und zwar, die Lösung von einer der Gleichungen, bewirkt die (Anfangs)Bedingungen für die nächste. Zu bemerken ist, dass die Gleichungen schwer zu lösen sind und zwar im Sinn von, dass man viel Rechenleistung investieren muss, um mit einer Lösung aufzukommen. Die klassische Ansätze zum Lösen sind mittels numerischen Lösern und durch die Finite Elemente Methode.

Die Haupteigenschaft für unsere Arbeit - die Lösungen haben eine natürliche Repräsentation - Bilder. Wie das Bild hier, es zeigt die Strömung um eine Kugel. Unsere erste Idee ist jetzt, die Möglichkeit zu untersuchen, diese Lösungen auf eine alternative Weise zu generieren.

\subsection{Netze}
\label{sec:org5cd85d4}
Heutzutage, immer wenn Bilder erwähnt werden, denk man DNNs (oder CNNs). Die sind ein echt heißes Thema in letzten Jahren. Immer mehr Forschung wird in diesem Bereich dediziert und unser Projekt ist als Teil von dieser Forschung gedacht. Es hat sich gezeigt, dass DNNs bei Bildverarbeitung Aufgaben beeindruckende Ergebnisse liefern können. Und deswegen unsere Idee ist, die Mächtigkeit von DNNs im Kontext von PDEs zu untersuchen und zwar auf Basis von den Bildrepresentationen der Lösungen.

Thema: Die Anwendbarkeit von DNNs beim Generieren von Lösungen von PDEs.

\subsection{Konkretes Problem}
\label{sec:org8d4f92d}
Bis jetzt alles gesagte ich aber zu breit und allgemein. Jetzt stellen wir ein konkretes Problem vor, wo wir unsere Forschung durchführen wollen.

\begin{itemize}
\item Wir beschränken uns zum 2D Fall.
\item und nehmen uns einen Kanal mit Flüssigkeit da drin - oder Fluid
\item Es gibt außerdem ein Objekt im Kanal und das Fluid fließt um das Objekt herum; auf einer Seite haben wir Einfließbedingung, auf der anderen Abfließ
\item das Fluid ist außerdem inkompressibel, damit wir dies leichter beschreiben können (unelastisch)
\end{itemize}

die ganze Physik jetzt wird mit der Navier-Stoke Gleichung beschrieben. Die exakte Mathematik ist nicht so wichtig, wir wollen nur explizit sagen, dass dies DIE Gleichung ist, die wir betrachten wollen und mit DNNs versuchen zu lösen.

Die beschriebene Simulation besitzt gewisse Eingangsparameter:
\begin{itemize}
\item Viskosität und Dichte von dem Fluid
\item die Einfließ-Geschwindigkeit - wie schnell fließt das Fluid ein
\item das Objekt selbst, die Geometrie im Raum
\end{itemize}
One thing is cahnged, the whole simulation must be restarted

\noindent\rule{\textwidth}{0.5pt}

Die Gleichung wird für jeden Zeitpunkt gelöst und die Lösungen sind:
\begin{itemize}
\item das Geschwindigkeitsfeld
\item das Drucksfeld
\end{itemize}

\subsection{DNNs in unserem Kontext}
\label{sec:org69f29ac}
Ok, jetzt haben wir ein konkretes Problem, springen wir mal zurück zu DNNs. Die Lösungen von der Gleichung, die wir gerade besprochen haben, können als Bilder visualisiert werden. Und wie schon gesagt, DNNs haben die Möglichkeit gut mit Bildern umzugehen. Damit kommt unsere grundlegende Idee, können wir nicht mit DNNs die Lösungsbilder der Simulation Vorhersagen. Und zwer, unter Verwendung der Lösungsbild von dem vorherigen Zeitpunkt. Die Annahme hier ist, dass ein solches Bild schon existiert.

Das zu untersuchende System hat also die folgende Gestalt. Stellen wir uns vor, diese sind drei Zeitpunkte von einer Simulation. Am Anfang haben wir gewisse Anfangsbedingungen und dann müssen wir zunächst die  quasi ``erste'' Gleichung mit einem numerischen Löser lösen, damit wir eine Lösung betrachten können. Diese wird dann als Bild codiert und durch das Netz propagiert. Das Netz vorhersagt dann das Bild von der nächsten Lösung. In diesem sind, wird die Gleichung im Netz codiert.

Zu Bemerken ist, dass der numerische Löser nicht komplett ersetzt wird. Wie gesagt, wir gehen von einem schon vorliegenden Bild aus.

\subsection{Die zwei Fragen}
\label{sec:org08d5d74}
Jetzt entstehen aber zwei Fragen, Nämlich:

\begin{itemize}
\item erstmals: Warum würden wir diese Bilder als Eingabe fürs Netz verwenden?
\begin{itemize}
\item Ansatz nicht probiert
\item die roh Daten sind kontinuierlich, man muss die so und so irgendwie abtasten
\item gut definierter Eingaberaum, Zahl-Bereich ist fest, man muss die Information hier, so und so irgendwie abtasten; nah dazu, hier ist die Information kontinuierlich
\item DNNs sind gut etabliert für Bildverarbeitung-Aufgaben
\end{itemize}
\item auf andere Seite: die nächste Folie zeigt genau dass; diese sind Bilder, die wir schon generiert haben (mit Löser) und repräsentieren die Geschwindigkeit in x-Richtung für 4 Zeitpunkte der Simulation;
\begin{itemize}
\item in machen Situationen, diese sind die Ergebnisse, die man ansehen will. Interessante Strukturen werden sichtbar, man kann sich überlegen und passend Simulations-Parameter auswählen;
\item genug wenn der Fehler nicht das wichtigste ist; die grobe Simulations-Ergebnisse werden verlangt;
\end{itemize}

Bemerkung: die Bilder sind ähnlich mit erfassbare Unterschied dazwischen - die DNNs können diesen Unterschied ``lernen''.
\end{itemize}

\section{Forschungsthema und Forschungsfrage}
\label{sec:org19a54ef}
Damit haben wir alles definiert und motivierte, um die Forschungsthema und Forschungsfrage festlegen zu können.

\begin{itemize}
\item Thema: Die Anwendbarkeit von DNNs beim Generieren von Lösungen von PDEs im Kontext von numerischen Simulationen
\begin{itemize}
\item immer noch allgemein gehalten
\end{itemize}

\item Frage bzw. Unterfragen: Inwiefern können DNNs die Parameter von der beschriebenen Simulation generalisieren. Die Simulation - inkompressible Fluid-Strömung um ein Objekt nach der Navier-Stoke Gleichung. Die Parameter, für die wir uns interessieren:
\begin{itemize}
\item Viskosität und Dichte vom Fluid
\item Einfließgeschweindigkeit
\item Objekt im Raum
\end{itemize}
\end{itemize}
Das Modell, das wir untersuchen wollen ist ein DNN, das auf Basis von Bildern funktioniert.

Wir haben bis jetzt gesagt, dass das Modell mit Bildern funktionierte, aber nun soll es klar sein, dass wir wollen auch diese Parameter betrachten.

\section{Related Work}
\label{sec:orgf396764}
Jetzt diskutieren wir kurz wo genau unsere Arbeit in de Forschungsfeld liegt
\begin{itemize}
\item zwei Rictungen beim Recherchieren
\item Bildverrbeitung; fokusiert auf bild-zu-bild abbildung;
\item das paper, das wir diskutieren wollen ist pix2pix - da wird ein allgemeines vorghenen vorgestellt;
\item it is nottested for simulation data in the form of images
\item wir wollen pix2pix weiter engwickeln
\end{itemize}

\noindent\rule{\textwidth}{0.5pt}
\begin{itemize}
\item 
\end{itemize}

\section{Methodologie}
\label{sec:org349e811}
Ok, jetzt fangen wir an zu erklären, was unsere Ansatz ist, damit wir eine Antwort für die Forschungsfrage angeben können.

\subsection{Grundlegende Aspekte}
\label{sec:org5f1dcb5}
Grundsätzlich ist unsere Projekt eine Untersuchung von Machine Learning Modellen. Deswegen folgen wir den üblichen Ansatz für solche Untersuchungen. Nämlich, die Aufgaben können sich in drei Aspekte unterteilen
\begin{enumerate}
\item Generieren von Trainingsdaten:
\item Aufbauen und trainieren von einem Modell, in unserem Fall ein DNN:
\item Evaluieren vom Modell:
\end{enumerate}

Erstmal müssen wir das Generieren von echten Simulationsdaten berücksichtigen. Diese sind die Daten, mit denen wir später das Modell trainiere wollen, also müssen die schon in Bildform sein. Hier kommen die Tools HiFlow und ParaView ins Spiel. HiFlow ist ein allgemeiner Rahmenwerk für Lösen von Differentialgleichungen. Da ist unsere Simulation schon implementiert und wir können die mit beliebigen Parametern laufen lassen. Dann werden die Ergebnisse generiert aber nicht als Bilder visualisiert. Dafür müssen wir ParaView verwenden, was ein Tool für das visualisieren von Daten von Experimente ist. ParaView kann letztendlich alle Zeitpunkte der Simulation als Sequenz von Bilder speichern.

Danach kommt das implementieren vom Modell selbst. Hier werden wir PyTorch als ML-Library benutzen. Unser Plan ist der Ansatz von pix2pix zu folgen, weil da allgemeine Architektur und Methode für Bild-zu-Bild Netze vorgestellt werden. Die gedachte Architektur basiert sich auf ResNet -- ein bekanntes und beliebtes Netz -- und GAN ist unserer allgemeiner Fortschritt beim Trainieren. Die Architektur muss natürlich irgendwann modifiziert werden, damit auch die Parameter von der Simulation betrachtet werden können.

Für das Evaluieren wollen wir zwei Dinge Bemerken. Zunächst, der Fehlermaß ist offensichtlich die Abweichung von dem echten Lösungsbild für den entsprechenden Zeitpunkt der Simulation. Will wollen diese Abweichung als Prozent angeben, weil falls dies unter 10 Prozent ist, können wir behaupten, dass die Methode wirklich für grobe Simulationen geeignet ist. Die andre Sache - wir haben zwei so zu sagen Evaluationsszenarient. 
\begin{itemize}
\item Was ist der Fehler beim Anwenden auf einzelnen Bilder - also es werden immer echte Daten als Eingabe verwendet.
\item Was passiert mit dem Fehler wenn das Model rekursiv angewandt ist - also Ausgabe ist wieder als Eingabe genommen; wie akkumuliert der Fehler dann
\end{itemize}
Diese sind quasi die zu untersuchende Anwendungsfällen

\subsection{Zurück zu Definition}
\label{sec:orgaee98a2}
Jetzt kommen wir kurz zu der Forschungsfrage zurück. Da haben wir gesagt, dass wir die Generalisierung von diesen Parametern untersuchen wollen. Es ist aber klar, dass vom Anfang ein Netz zu entwickeln, dass alles kann, schwierig wäre. Deswegen, haben wir und entschieden, ein separates Modell für jeden Fall zu entwickeln. In diesem Sinn wollen wir iterativ arbeiten und das ganze Stück für Stück aufbauen.

\subsection{Arbeitsplan und Methodologie}
\label{sec:org0517a2d}
Damit können wir den Arbeitsplan eingehen. Wir unterteilen den in vier allgemeinen Phasen:

\begin{enumerate}
\item Initiale System - hier geht um das Entwickeln von alles was wir brauchen, um das Trainieren und Evaluieren von Modellen zu ermöglichen. Hier zählen wir das generieren von Trainingssaten und das Implementieren von einer quasi Library. Die Library ist nichts anderes als eine Sammlung von python-Skripts, die eine Pipeline bilden. Also Data Loader - damit das Laden von den Bilder in Speicher in geeigneter Form bequem ist, das Modell selbst und Evaluieren und Trainieren Infrastruktur, damit das Trainer und Evaluieren teilweise automatisch durchgeführt werden können.
Hier haben wir auch ein Baseline-Modell gedacht, das nur auf Bildbasis funktionieren sollte. Also das Modell wird mit 80\% der Daten aus einer Simulation trainiert und dir Frage ist, können die anderen 20\% vorhergesagt werden. Das soll als eine Basis für dir Entwicklung von den weiteren Modellen dienen. Und  Außerdem hätten wir dann bestimmte baseline Ergebnisse zum Vergleich.

\item Fluid Parameter - hier wollen das Model so anpassen, so dass es die Viskosität und die Dichte des Fluids berücksichtigen kann. Die Hauptaufgabe ist mit der Architektur des Modells ein bisschen umzuspielen und zu überprüfen, was gut funktioniert, also wie können wir diese zwei reelle Zahlen als Eingabe fürs Netz verwenden. Nach gewisser Zeit kommt auch das Evaluieren nach den besprochenen Weisen.

\item Genau dasselbe gilt auch für die Einfließ-Geschwindigkeit Modell. Hier haben wir einen Parameter, den wir ins Modell integrieren wollen. Das Evaluieren ist klar

\item Die Situation beim letzten Modell ist aber unterschiedlich. Jetzt wollen wir den ganzen Eingaberaum betrachten. Unsere Überlegung für jetzt ist, den Raum durch eine binäre Maske zu beschreiben. Also 1 da wo Geometrie gibt und 0 da wo ``Freiraum'' ist. Das angepasste Modell soll dann diese Maske als quasi extra Eingabesbild bekommen.
\end{enumerate}

Die letzten drei Phasen sind ziemlich ähnlich bezüglich Vorgehen und es sieht folgendermaßen aus. Also, wir machen irgendwelche Modifikationen zum Modell, dann schauen was passiert, dann überlegen ob das gut genug ist und falls notwendig, nehmen wir weitere Modifikationen vor und so weiter und so fort.

Diese Iteration motiviert auch unsere konkrete Zeitplanung für Projekt

\section{Zeitplanung}
\label{sec:org6c62664}
Der Zeitplan sieht so aus. Wir haben hier die 4 Phasen. Am Anfang ist auch die Datengenerierung, weil wir relativ sicher sind, dass dies auch parallel zu der Entwicklung passieren kann. Für jede Phase haben wir uns 3 oder 4 Wochen angerechnet. Eine Woche mehr am Anfang. Ich vermuten wir werden dann ein bisschen mehr Zeit brauchen als wir müssen von Grund auf neu viel Implementieren. Wir haben Vier Meilensteine am Ende jeder Phase festgelegt, wo wir ein fertiges und evaluiertes Modell haben sollen, spricht Ergebnisse.

\section{Schluss}
\label{sec:orgcfac6d1}
Damit bin ich zum Ende. Ich bedanke mich für die Aufmerksamkeit.
\end{document}

### 2019-10-07 proposal/figures/flow.tex
Initial commit

\documentclass{standalone}

\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{tkz-euclide}

\pgfplotsset{compat=1.6}

\usetikzlibrary{positioning,calc}
\usetikzlibrary{arrows} 
\usetikzlibrary{patterns} 
\usetikzlibrary{shapes}
\usetikzlibrary{decorations.pathmorphing}

\usetkzobj{all} 
\usetikzlibrary{through}

\pgfdeclarepatternformonly{mydots}{\pgfqpoint{-1pt}{-1pt}}{\pgfqpoint{1pt}{1pt}}{\pgfqpoint{2pt}{2pt}}% original definition: \pgfqpoint{3pt}{3pt}
{%
  \pgfpathcircle{\pgfqpoint{0pt}{0pt}}{.5pt}%
  \pgfusepath{fill}%
}%

\begin{document}

\def\BeforeLight{2}                  % Light path before particle cloud
\begin{tikzpicture}

  \draw[step=0.5cm, gray!20!white, very thin] (-0.9, -0.9) grid (7.9, 3.9);

  \fill[blue!10!white, pattern=dots, pattern color=blue!20!white] (0,0) rectangle (7,3);
  \draw[line width=0.25mm] (0,0) -- (7,0);
  \draw[line width=0.25mm] (0,3) -- (7,3);

  \fill[pattern=north west lines, pattern color=blue!40!white] (1.0, 1.0) rectangle (2.0, 2.0);
  \draw[line width=0.15mm] (1.0, 1.0) rectangle (2.0, 2.0);

  \fill[pattern=north west lines, pattern color=gray] (0, 0) rectangle (7, -0.5);
  \fill[pattern=north west lines, pattern color=gray] (0, 3) rectangle (7, 3.5);

  \draw[red,
  decoration = {markings,
    mark = at position 0.18 with {\arrow[]{latex }},
    mark = at position 0.77 with {\arrow[]{latex }}}, postaction = {decorate}]
  (-1, 0.25) --++ (5.5, 0) node[midway, above, black]{};

  \draw[red,
  decoration = {markings,
    mark = at position 0.18 with {\arrow[]{latex }},
    mark = at position 0.77 with {\arrow[]{latex }}}, postaction = {decorate}]
  (-1, 0.75) --++ (5.5, 0) node[midway, above, black]{};

  \draw[red,
  decoration = {markings, width=0.3mm,
    mark = at position 0.5 with {\arrow[]{latex}}}, postaction = {decorate}]
  (-1, 1.25) --++ (2.0, 0) node[midway, above, black]{$\Gamma_{in}$};

  \draw[red,
  decoration = {markings, width=0.3mm,
    mark = at position 0.5 with {\arrow[]{latex}}}, postaction = {decorate}]
  (-1, 1.75) --++ (2.0, 0) node[midway, above, black]{};

  \draw[red,
  decoration = {markings,
    mark = at position 0.18 with {\arrow[]{latex }},
    mark = at position 0.77 with {\arrow[]{latex }}}, postaction = {decorate}]
  (-1, 2.25) --++ (5.5, 0) node[midway, above, black]{};

  \draw[red,
  decoration = {markings,
    mark = at position 0.18 with {\arrow[]{latex }},
    mark = at position 0.77 with {\arrow[]{latex }}}, postaction = {decorate}]
  (-1, 2.75) --++ (5.5, 0) node[midway, above, black]{};

  \draw[blue,
  decoration = {markings, width=0.3mm,
    mark = at position 0.5 with {\arrow[]{latex}}}, postaction = {decorate}]
  (4.5, 0.25) --++ (3.5, 0) node[midway, above, black]{};

  \draw[blue,
  decoration = {markings, width=0.3mm,
    mark = at position 0.5 with {\arrow[]{latex}}}, postaction = {decorate}]
  (4.5, 0.75) --++ (3.5, 0) node[midway, above, black]{};

  \draw[blue,
  decoration = {markings, width=0.3mm,
    mark = at position 0.5 with {\arrow[]{latex}}}, postaction = {decorate}]
  (4.5, 1.25) --++ (3.5, 0) node[midway, above, black]{$\Gamma_{out}$};

  \draw[blue,
  decoration = {markings, width=0.3mm,
    mark = at position 0.5 with {\arrow[]{latex}}}, postaction = {decorate}]
  (4.5, 1.75) --++ (3.5, 0) node[midway, above, black]{};

  \draw[blue,
  decoration = {markings, width=0.3mm,
    mark = at position 0.5 with {\arrow[]{latex}}}, postaction = {decorate}]
  (4.5, 2.25) --++ (3.5, 0) node[midway, above, black]{};

  \draw[blue,
  decoration = {markings, width=0.3mm,
    mark = at position 0.5 with {\arrow[]{latex}}}, postaction = {decorate}]
  (4.5, 2.75) --++ (3.5, 0) node[midway, above, black]{};

  \draw[red,
  decoration = {markings, width=0.3mm,
    mark = at position 0.5 with {\arrow[]{latex}}}, postaction = {decorate}]
  (2.0, 1.25) --++ (2.5, 0) node[midway, above, black]{};

  \draw[red,
  decoration = {markings, width=0.3mm,
    mark = at position 0.5 with {\arrow[]{latex}}}, postaction = {decorate}]
  (2.0, 1.75) --++ (2.5, 0) node[midway, above, black]{};

  % \draw[black!60!white, width=0.15mm] (0, -1) -- (0,4) node[at start, right, black]{$(1)$ Inflow};
  % \draw[black!60!white, width=0.15mm] (7, -1) -- (7,4) node[at start, right, black]{$(2)$ Outflow};

  % \node (A) at (4.1, -1) {$(3)$ No-slip};

  % \draw[->, line width = 0.155mm] (1.75, 1.0) -- (A)
  % \draw[->, line width = 0.155mm] (3.5, 0) -- (A)
  % \draw[->, line width = 0.155mm] (4.2, 3) -- (A)

\end{tikzpicture}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-10-07 proposal/figures/gannt.tex
Initial commit

\documentclass{standalone}

\usepackage{color}
\usepackage{tikz}
\usepackage{pgfgantt}

\begin{document}

\begin{ganttchart}[
  hgrid,
  vgrid,
  group peaks height=.2,
  expand chart=\textwidth*2]{1}{23}

  \gantttitle{Project plan}{23} \\

  \gantttitle{October 2019}{4}
  \gantttitle{November 2019}{4}
  \gantttitle{December 2019}{4}
  \gantttitle{January 2020}{4}
  \gantttitle{February 2020}{3}
  \gantttitle{March 2020}{4} \\

  \gantttitlelist{1,...,23}{1} \\

  \ganttbar{Data Generation}{1}{4}
  \ganttnewline[thick]

  \ganttgroup[inline, group inline label anchor = east]{Initial system development}{1}{4} \\
  \ganttgroup[inline, group inline label anchor = east]{Fluid viscosity and density generalization}{5}{7} \\
  \ganttgroup[inline, group inline label anchor = east]{Inflow speed generalization}{8}{10} \\

  \ganttgroup[inline, group inline label anchor = east]{Object generalization}{11}{13}

  \ganttnewline

  \ganttbar{Implementing a data loader}{1}{1} \\
  \ganttbar[name=inital_model]{Implementing the initial models}{1}{2} \\
  \ganttbar[name=eval_framework]{Implementing an evaluation infrastructure}{2}{2} \\

  \ganttbar[name=training_0]{Training and adjusting models}{3}{4}
  \ganttbar[name=training_1]{}{6}{7}
  \ganttbar[name=training_2]{}{9}{10}
  \ganttbar[name=training_3]{}{12}{13}

  \ganttnewline

  \ganttbar[name=eval_0]{Evaluation of the models}{3}{4}
  \ganttbar[name=eval_1]{}{6}{7}
  \ganttbar[name=eval_2]{}{9}{10}
  \ganttbar[name=eval_3]{}{12}{13}

  \ganttnewline

  \ganttmilestone[name=mile_0, inline, milestone inline label node/.append style={below=4mm}]{Milestone 1}{4}
  \ganttmilestone[name=mile_1, inline, milestone inline label node/.append style={below=4mm}]{Milestone 2}{7}
  \ganttmilestone[name=mile_2, inline, milestone inline label node/.append style={below=4mm}]{Milestone 3}{10}
  \ganttmilestone[name=mile_3, inline, milestone inline label node/.append style={below=4mm}]{Milestone 4}{13}

  \ganttnewline

  \ganttlink[link mid=0.8]{inital_model}{training_0}
  \ganttlink[link mid=0.53]{inital_model}{eval_0}

  \ganttlink[link mid = 0.5, link tolerance=0.1]{mile_0}{training_1}
  \ganttlink[link mid = 0.5, link tolerance=0.1]{mile_1}{training_2}
  \ganttlink[link mid = 0.5, link tolerance=0.1]{mile_2}{training_3}

  \ganttlink[link mid = 0.5, link tolerance=0.1]{mile_0}{eval_1}
  \ganttlink[link mid = 0.5, link tolerance=0.1]{mile_1}{eval_2}
  \ganttlink[link mid = 0.5, link tolerance=0.1]{mile_2}{eval_3}

  \ganttlink[link mid=0.53]{eval_0}{mile_0}
  \ganttlink[link mid=0.53]{eval_1}{mile_1}
  \ganttlink[link mid=0.53]{eval_2}{mile_2}
  \ganttlink[link mid=0.53]{eval_3}{mile_3}

  \ganttnewline[thick]

  \ganttgroup[group peaks height=0,]{Buffer time}{14}{17}
  \ganttgroup[group peaks height=0,]{}{5}{5}
  \ganttgroup[group peaks height=0,]{}{8}{8}
  \ganttgroup[group peaks height=0,]{}{11}{11}

  \ganttnewline[thick]

  \ganttgroup[inline]{Paper}{18}{23} \\
  \ganttbar{Writing out an academic paper}{18}{23} \\  
  \ganttbar{Preparing a presentation}{21}{23}

  % \ganttbar[name=modify_1]{Modifying models}{5}{5} \\
  % \ganttlinkedbar{Training and adjusting models}{6}{7} \\
  % \ganttbar[name=eval_1]{Evaluation of the models}{6}{7} \\
  % 
  % \ganttlink[link mid=.25]{modify_1}{eval_1}
  % \ganttlink{eval_1}{elem12}

  % \ganttnewline[thick]

  %  \\
  % \ganttbar[name=modify_2]{Modifying models}{8}{8} \\
  % \ganttlinkedbar{Training and adjusting models}{9}{10} \\
  % \ganttbar[name=eval_2]{Evaluation of the models}{9}{10} \\
  % \ganttlink[link mid=.25]{modify_2}{eval_2}
  % 
  % \ganttlink[]{eval_2}{elem17}

  % \ganttnewline[thick]

  % 
  % \ganttbar[name=modify_3]{Modifying models}{11}{11} \\
  % \ganttlinkedbar{Training and adjusting models}{12}{13} \\
  % \ganttbar[name=eval_3]{Evaluation of the models}{12}{13} \\
  % 
  % \ganttlink[link mid=.25]{modify_3}{eval_3}
  % \ganttlink[]{eval_3}{elem22}

  % \ganttnewline[thick]

\end{ganttchart}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "flow"
%%% End:

### 2019-10-07 proposal/figures/meth.tex
Initial commit

\documentclass{standalone}

\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{tkz-euclide}

\pgfplotsset{compat=1.6}

\usetikzlibrary{positioning,calc}
\usetikzlibrary{arrows} 
\usetikzlibrary{patterns} 
\usetikzlibrary{shapes}
\usetikzlibrary{decorations.pathmorphing}

\begin{document}

\def\BeforeLight{2}
\begin{tikzpicture}
  % \draw[step=1cm, gray!20!white, very thin] (-5,-5) grid (5,5);

  \node[draw, minimum height=1cm,minimum width=3cm] at (0, 3) (n_1)             {Initial System};
  \node[draw, minimum height=1cm,minimum width=3cm, pattern=north west lines, pattern color=blue!20!white] (n_2) [below=0.75cm of n_1] {Fluid parameters};
  \node[draw, minimum height=1cm,minimum width=3cm, pattern=north west lines, pattern color=blue!20!white] (n_3) [below=0.75cm of n_2] {Inflow speed};
  \node[draw, minimum height=1cm,minimum width=3cm, pattern=north west lines, pattern color=blue!20!white] (n_4) [below=0.75cm of n_3] {Object in space};

  \draw [->, shorten >=3pt, shorten <=3pt, thick ] (n_1) edge (n_2);
  \draw [->, shorten >=3pt, shorten <=3pt, thick ] (n_2) edge (n_3);
  \draw [->, shorten >=3pt, shorten <=3pt, thick ] (n_3) edge (n_4);

\end{tikzpicture}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-10-07 proposal/figures/mod_train.tex
Initial commit

--- 2019-10-07 proposal/figures/meth.tex
@@
 
-  \node[draw, minimum height=1cm,minimum width=3cm] at (0, 3) (n_1)             {Initial System};
-  \node[draw, minimum height=1cm,minimum width=3cm, pattern=north west lines, pattern color=blue!20!white] (n_2) [below=0.75cm of n_1] {Fluid parameters};
-  \node[draw, minimum height=1cm,minimum width=3cm, pattern=north west lines, pattern color=blue!20!white] (n_3) [below=0.75cm of n_2] {Inflow speed};
-  \node[draw, minimum height=1cm,minimum width=3cm, pattern=north west lines, pattern color=blue!20!white] (n_4) [below=0.75cm of n_3] {Object in space};
+  \node[draw, minimum height=1cm,minimum width=4cm] at (0, 3) (mod)             {Modifications};
+  \node[draw, minimum height=1cm,minimum width=4cm] (train) [below=1cm of mod] {Training \& Evaluating};
 
-  \draw [->, shorten >=3pt, shorten <=3pt, thick ] (n_1) edge (n_2);
-  \draw [->, shorten >=3pt, shorten <=3pt, thick ] (n_2) edge (n_3);
-  \draw [->, shorten >=3pt, shorten <=3pt, thick ] (n_3) edge (n_4);
+  \draw [->, thick] (mod.east) to [out = 0, in = 0, looseness = 2] (train.east);
+  \draw [->, thick] (train.west) to [out = 180, in = 180, looseness = 2] (mod.west);
 
 \end{tikzpicture}
-
 \end{document}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2019-10-07 proposal/figures/time.tex
Initial commit

\documentclass{standalone}

\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{tkz-euclide}

\usetikzlibrary{positioning,calc}
\usetikzlibrary{arrows} 
\usetikzlibrary{patterns} 
\usetikzlibrary{shapes}
\usetikzlibrary{decorations.pathmorphing}
\usetkzobj{all} 
\usetikzlibrary{through}

\begin{document}

\begin{tikzpicture}
  \draw[step=2cm, gray!20!white, very thin] (-5, -3) grid (5, 6);

  \node[draw, minimum height=1cm,minimum width=3cm] at (-4, 4)     (n_1) {Initial System};
  \node[draw, minimum height=1cm,minimum width=3cm] at (-1.5, 2.7) (n_2) {Fluid parameters};
  \node[draw, minimum height=1cm,minimum width=3cm] at (1, 1.4)  (n_3) {Inflow speed};
  \node[draw, minimum height=1cm,minimum width=3cm] at (3.5, 0.1)    (n_4) {Object in space};

  \node[draw, minimum height=1cm,minimum width=3cm] [above=0.25cm of n_1] (n_0) {Data Generation};

  \draw [->, thick] (n_1.east) to [bend left=45] (n_2.north);
  \draw [->, thick] (n_2.east) to [bend left=45] (n_3.north);
  \draw [->, thick] (n_3.east) to [bend left=45] (n_4.north);

  \path[->,thick] (n_1) edge [loop below, looseness=15] node[text width=3cm, align=center] {Iterating} (n_1);
  \path[->,thick] (n_2) edge [loop below, looseness=15] node[text width=3cm, align=center] {Iterating} (n_2);
  \path[->,thick] (n_3) edge [loop below, looseness=15] node[text width=3cm, align=center] {Iterating} (n_3);
  \path[->,thick] (n_4) edge [loop below, looseness=15] node[text width=3cm, align=center] {Iterating} (n_4);

  \path[dashed, black!50!white] (-2.75, 5) edge (-2.75, -2);
  \path[dashed, black!50!white] (-0.25, 5) edge (-0.25, -2);
  \path[dashed, black!50!white] (2.25, 5) edge (2.25, -2);
  \path[dashed, black!50!white] (4.75, 5) edge (4.75, -2);

  \node [below=5.75cm of n_1] {4 weeks};
  \node [below=4.5cm of n_2] {3 weeks};
  \node [below=3.25cm of n_3] {3 weeks};
  \node [below=2.0cm of n_4] {3 weeks};

  \node at (4.75, -2)  [draw, diamond, fill=black, scale=0.7] {} ; 
  \node at (2.25, -2)  [draw, diamond, fill=black, scale=0.7] {} ; 
  \node at (-0.25, -2) [draw, diamond, fill=black, scale=0.7] {} ; 
  \node at (-2.75, -2) [draw, diamond, fill=black, scale=0.7] {} ;

\end{tikzpicture}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-10-07 state-of-the-art/SoA-Presi/soa-presi.tex
Initial commit

\documentclass[18pt]{beamer}
\usepackage{templates/beamerthemekit}
\usepackage[export]{adjustbox}
\usepackage{tikz}
\usepackage{url}

\title[State of the Art]{Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks}
\subtitle{State of the Art, Supervisor - Markus Hoffmann}
\author{Stanislav Arnaudov}
\institute{Chair for Computer Architecture and Parallel Processing}
\selectlanguage{english}

\usepackage[style=verbose,backend=bibtex]{biblatex}
\bibliography{bib}
\bibliographystyle{plain}

\begin{document}

\begin{frame}
 \titlepage
\end{frame}

\section{Motivation}
\begin{frame}

  \frametitle{Problem definition and motivation}

  \begin{columns}

    \begin{column}{0.5\textwidth}
      Partial differential equation (PDEs)
      \begin{itemize}
      \item used in simulations
      \item solutions have image representation
      \item hard to solve numerically
      \end{itemize}
      \vspace{0.25cm}
      \textbf{Goal}: solve PDEs based on their image representation 
      \vspace{-0.5cm}
    \end{column}

    \begin{column}{0.5\textwidth}
      \begin{center}
        \begin{figure}[htb]
          \includegraphics[scale=0.35]{images/pde}
          \caption{Flow Simulation\footnotemark}
        \end{figure}
      \end{center}
    \end{column}

    \footnotetext{``Team for Advanced Flow Simulation and Modeling'', Professor Tayfun E. Tezduyar, Sunil Sathe}
  \end{columns}

\end{frame}

\begin{frame}
  \frametitle{Problem definition and motivation}
  Convolutional neural networks (CNNs)
  \begin{itemize}
  \item hot topic in recent years
  \item impressive results in image processing
  \end{itemize}
  \textbf{Idea}: Use CNNs for the image representation of PDEs.
  \vspace{0.8cm}
  \begin{center}
    \includegraphics[scale=0.35]{images/general}
  \end{center}

\end{frame}

\begin{frame}
  \frametitle{General Goals}
  \begin{center}
    \includegraphics[scale=0.50]{images/bringing_cnn_and_pde}
  \end{center}  
\end{frame}

\begin{frame}
  \frametitle{Important Questions}

  \begin{enumerate}

  \item CNNs for image-to-image mapping?
    \vspace{0.7cm}
    \begin{center}
      \includegraphics[scale=0.45]{images/image_to_image_cnn}
    \end{center}

    \vspace{0.5cm}
  \item CNNs for numerical simulations?
    \vspace{0.5cm}
    \begin{center}
      \includegraphics[scale=0.45]{images/system_to_system_cnn}
    \end{center}

  \end{enumerate}  
\end{frame}

\section{CNNs for image processing}
\begin{frame}
  \frametitle{CNNs for image processing}

  \begin{columns}
    \begin{column}{0.5\textwidth}
      We focus on an area where CNNs show good results:
      \begin{itemize}
      \item Image Segmentation
        \begin{itemize}
        \item pixelwise decision about a class belonging
        \item a new image is generated
        \end{itemize}
      \end{itemize}
    \end{column}

    \begin{column}{0.5\textwidth}
      \begin{center}
        \begin{figure}
          \centering
          \includegraphics[scale=0.35]{images/segm}
          \caption{Image Segmentation\footnotemark}
        \end{figure}
      \end{center}
    \end{column}
  \end{columns}

  \footnotetext{``Exploring Computer Vision in Deep Learning: Object Detection and 
    Semantic Segmentation'', Long et al.,SAS Institute Inc.}

\end{frame}

\begin{frame}
  \frametitle{CNNs for image processing}
  Image segmentation
  \begin{itemize}
  \item ``Fully Convolutional Networks for Semantic Segmentation''\footcite{long2014}
    \begin{itemize}
    \item Encoder-Decoder Architecture
    \item Only convolutional layers
    \end{itemize}
  \end{itemize}
  \vspace{0.5cm}
  \begin{center}
    \begin{figure}[htb]
      \includegraphics[scale=0.35]{images/auto_enc}
      \caption{The encoder-decoder network}
    \end{figure}
  \end{center}
\end{frame}

\begin{frame}
  \frametitle{CNNs for image processing}

  Image segmentation
  \begin{itemize}
  \item ``Semantic Segmentation using Adversarial Networks'' \footcite{luc2016}
    \begin{itemize}
    \item Generative Adversarial Networks\footcite{goodfellow2014}
    \item The Discriminator Network enforces contagiously segmented regions
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{CNNs for image processing}
  \begin{center}
    \begin{figure}[htb]
      \includegraphics[width=11cm,height=5cm]{images/gan}
      \caption{Generative Adversarial Network\footnotemark}
    \end{figure}
  \end{center}
  \footnotetext{``A Beginner's Guide to Generative Adversarial Networks (GANs)'', \url{https://skymind.ai/wiki/generative-adversarial-network-gan} }
\end{frame}

\begin{frame}
  \frametitle{CNNs for image processing}
  Semantic Image Synthesis
  \begin{itemize}
  \item ``Semantic Image Synthesis with Spatially-Adaptive Normalization'' \footcite{park2019}
    \begin{itemize}
      \item Segmentation in reverse
    \end{itemize}

    \begin{center}
      \begin{figure}[htb]
        \includegraphics[width=10cm,height=3cm]{images/gaugan}
        \caption{Example of ``reversed image segmentation''}
      \end{figure}
  \end{center}
  \end{itemize}
\end{frame}

\section{CNNs for numerical applications}
\begin{frame}
  \frametitle{CNNs for numerical applications}
  Long standing interest in bringing together neural networks and formal mathematics.
  \begin{itemize}
  \item It is shown to be possible -  ``Performing basic mathematics with neurons/nets'' (2002)  \footcite{neville2002}
  \item Even for PDEs - ``Artificial Neural Networks for Solving Ordinary 
and Partial Differential Equations'' (1998) \footcite{lagaris1998}
  \end{itemize}

\end{frame}

\begin{frame}
  \frametitle{CNNs for numerical applications}
  Nowadays CNNs are applied to complex physical simulations.
  \begin{itemize}
  \item CNNs for calculating physical properties of objects in simulations
  \item CNNs in flow simulation
  \end{itemize}

\end{frame}

\begin{frame}
  \frametitle{CNNs for numerical applications}
  \begin{itemize}

  \item ``Learning Soft Tissue Behavior of Organs for Surgical Navigation with Convolutional Neural Networks''\footcite{pfeiffer2019}
    \begin{itemize}
    \item Prediction for how organs in the human body move during operation
    \item Encoder-Decoder Architecture
    \end{itemize}
    \vspace{0.25cm}

    \begin{center}
      \begin{figure}[htb]
        \includegraphics[scale=0.35]{images/organs_move_1}
        \caption{Given and predicted displacement of an organ}
      \end{figure}
    \end{center}

  \end{itemize}

\end{frame}

\begin{frame}
  \frametitle{CNNs for numerical applications}
  \begin{itemize}
  \item ``Accelerating Eulerian Fluid Simulation With Convolutional Networks''\footcite{tompson2016}
    \begin{itemize}
    \item CNN for predicting fluid-flow
    \item Calculate pressure given velocity divergence and geometry
    \end{itemize}
  \end{itemize}
  \vspace{0.1cm}
  \begin{center}
    \includegraphics[width=11cm, height=4cm]{images/sim_1}
  \end{center}

\end{frame}

\section{Conclusion}
\begin{frame}
  \frametitle{Conclusion}

  To reiterate
  \begin{itemize}
  \item \textit{Problem:} Solve PDEs 
  \item \textit{Approach:} Use CNNs for image-to-image mapping
  \item \textit{Goal:} Efficiency and acceptable error
  \end{itemize}

  \rule{10cm}{0.4pt}

  The conducted research illustrates:
  \begin{itemize}
  \item A research gap
  \item Evidence suggesting the proposed method is viable
  \item Typical CNN architectures that should be considered
  \end{itemize}  
\end{frame}

\begin{frame}
  \frametitle{}
  \begin{center}
    \huge{Thank you for your attention.}    
  \end{center}
\end{frame}

\begin{frame}
  \frametitle{}
  \begin{center}
    \huge{Questions?}
  \end{center}
\end{frame}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-10-07 project/data/gen_data.sh
Adding data generation scripts

@@ -1,0 +1,37 @@
+#!/bin/bash
+
+PARAMS_FILE=$(realpath $1)
+CONFIG_FILE=$(realpath $2)
+GEOMETRY_DATA="$(realpath $3)/"
+ROOT_DATA_DIR=$(realpath $4)
+
+FLOW_EXEC="/home/arnaud/code_sys/Hiflow3_2.0/build/examples/flow/flow_tutorial"
+
+set_params_f()
+{
+    sed -i -e "s#<Viscosity>.*</Viscosity>#<Viscosity>$1</Viscosity>#g" ${CONFIG_FILE}
+    sed -i -e "s#<Density>.*</Density>#<Density>$2</Density>#g" ${CONFIG_FILE}
+    sed -i -e "s#<InflowSpeed>.*</InflowSpeed>#<InflowSpeed>$3</InflowSpeed>#g" ${CONFIG_FILE}
+}
+
+
+# ec="echo"
+# eval "${ec} 213"
+
+mkdir -p ${ROOT_DATA_DIR}
+
+count=1
+while IFS=" " read -r visc dens inflow prefix
+do
+    output=${prefix}_$count
+
+    sed -i -e "s#<OutputPrefix>.*</OutputPrefix>#<OutputPrefix>${output}</OutputPrefix>#g" ${CONFIG_FILE}
+    
+    echo "Running simulation: ${output}"
+    set_params_f $visc $dens $inflow
+    mkdir -p "${ROOT_DATA_DIR}/${output}"
+    cd "${ROOT_DATA_DIR}/${output}"
+    # mpirun -np 4 ${FLOW_EXEC} "${CONFIG_FILE}" "${GEOMETRY_DATA}"
+    cd - > /dev/null
+    count=`expr $count + 1`
+done < <(tail -n +2 ${PARAMS_FILE} | sed -e 's/\,/ /g') 

### 2019-10-07 project/data/gen_param_file.py

@@ -1,0 +1,79 @@
+#!/usr/bin/env python
+import os
+import sys
+import itertools
+
+
+##########################################################
+#  ____                                _                 #
+# |  _ \ __ _ _ __ __ _ _ __ ___   ___| |_ ___ _ __ ___  #
+# | |_) / _` | '__/ _` | '_ ` _ \ / _ \ __/ _ \ '__/ __| #
+# |  __/ (_| | | | (_| | | | | | |  __/ ||  __/ |  \__ \ #
+# |_|   \__,_|_|  \__,_|_| |_| |_|\___|\__\___|_|  |___/ #
+##########################################################
+
+# baseline model
+simple_speed = 3.5
+simple_viscosity = 0.1
+simple_density = 4
+
+# constant parameters to be used when the other ones are varied
+const_speed = 0.3
+const_viscosity = 0.3
+const_density = 1
+
+# viscosity and density model
+viscosity_start = 0.015
+viscosity_end = 0.03
+
+density_start = 1
+density_end = 22
+
+# inflow speed model
+speed_start = 0.5
+speed_end = 10
+
+# count of the range devisions
+inflow_range_divisions = 40
+fluid_range_divisions = 20
+
+##########################################################
+##########################################################
+
+def main():
+
+    file_name = sys.argv[1]
+    print("Generating parameters list in file:", file_name)
+
+    with open(file_name, 'w') as output:
+        output.write("viscosity, density, inflow_speed, prefix\n")
+
+        print('Baseline parameters: visc - {}, dens - {}, inflow - {}'.format(simple_viscosity, simple_density, simple_speed))
+        output.write("{}, {}, {}, {}\n".format(simple_viscosity, simple_density, simple_speed, "c"))
+
+        l = range(inflow_range_divisions)
+        print('Generating inflow speeds:')
+        print('    range: [{}, {}]'.format(speed_start, speed_end))
+        print('    intervals count: {}'.format(len(l)))
+        print('    viscosity: {}'.format(const_viscosity))
+        print('    density: {}'.format(const_density))
+        
+        for i in l:
+            speed = speed_start + i*(speed_end - speed_start)/(inflow_range_divisions - 1)
+            output.write("{}, {}, {}, {}\n".format(const_viscosity, const_density, speed, "s"))        
+
+        densities = [density_start + i*(density_end - density_start)/(fluid_range_divisions - 1) for i in range(fluid_range_divisions)]
[…]

### 2019-10-07 project/data/gen_data.sh
Adding support for custom -np argument for the mpirun command

@@ -5,7 +5,11 @@ CONFIG_FILE=$(realpath $2)
 GEOMETRY_DATA="$(realpath $3)/"
 ROOT_DATA_DIR=$(realpath $4)
 
-FLOW_EXEC="/home/arnaud/code_sys/Hiflow3_2.0/build/examples/flow/flow_tutorial"
+# FLOW_EXEC="/home/arnaud/code_sys/Hiflow3_2.0/build/examples/flow/flow_tutorial"
+FLOW_EXEC=${FLOW_EXEC:-"/home/arnaud/code_sys/Hiflow3_2.0/build/examples/flow/flow_tutorial"}
+MPI_NP=${MPI_NP:-4}
+
+
 
 set_params_f()
 {
@@ -18,20 +22,20 @@ set_params_f()
 # ec="echo"
 # eval "${ec} 213"
 
+echo "Hiflow executable: " $FLOW_EXEC
+echo "MPI workers count:" $MPI_NP
 mkdir -p ${ROOT_DATA_DIR}
 
 count=1
 while IFS=" " read -r visc dens inflow prefix
 do
     output=${prefix}_$count
-
     sed -i -e "s#<OutputPrefix>.*</OutputPrefix>#<OutputPrefix>${output}</OutputPrefix>#g" ${CONFIG_FILE}
-    
     echo "Running simulation: ${output}"
     set_params_f $visc $dens $inflow
     mkdir -p "${ROOT_DATA_DIR}/${output}"
     cd "${ROOT_DATA_DIR}/${output}"
-    # mpirun -np 4 ${FLOW_EXEC} "${CONFIG_FILE}" "${GEOMETRY_DATA}"
+    mpirun -np ${MPI_NP} ${FLOW_EXEC} "${CONFIG_FILE}" "${GEOMETRY_DATA}"
     cd - > /dev/null
     count=`expr $count + 1`
 done < <(tail -n +2 ${PARAMS_FILE} | sed -e 's/\,/ /g') 

### 2019-10-10 project/data/anim.py
Creating some of the data generation files

@@ -1,0 +1,237 @@
+#### import the simple module from the paraview
+from paraview.simple import *
+#### disable automatic camera reset on 'Show'
+paraview.simple._DisableFirstRenderCameraReset()
+
+# create a new 'XML Partitioned Unstructured Grid Reader'
+c_1_solution0 = XMLPartitionedUnstructuredGridReader(FileName=['<!file_place!>'])
+c_1_solution0.CellArrayStatus = ['Material Id', '_remote_index_', '_sub_domain_']
+c_1_solution0.PointArrayStatus = ['p', 'u', 'v']
+
+# get animation scene
+animationScene1 = GetAnimationScene()
+
+# update animation scene based on data timesteps
+animationScene1.UpdateAnimationUsingDataTimeSteps()
+
+# set active source
+SetActiveSource(c_1_solution0)
+
+# get active view
+renderView1 = GetActiveViewOrCreate('RenderView')
+# uncomment following to set a specific view size
+# renderView1.ViewSize = [1567, 782]
+
+# get color transfer function/color map for 'a_sub_domain_'
+a_sub_domain_LUT = GetColorTransferFunction('a_sub_domain_')
+a_sub_domain_LUT.LockDataRange = 0
+a_sub_domain_LUT.InterpretValuesAsCategories = 0
+a_sub_domain_LUT.ShowCategoricalColorsinDataRangeOnly = 0
+a_sub_domain_LUT.RescaleOnVisibilityChange = 0
+a_sub_domain_LUT.EnableOpacityMapping = 0
+a_sub_domain_LUT.RGBPoints = [0.0, 0.231373, 0.298039, 0.752941, 1.5, 0.865003, 0.865003, 0.865003, 3.0, 0.705882, 0.0156863, 0.14902]
+a_sub_domain_LUT.UseLogScale = 0
+a_sub_domain_LUT.ColorSpace = 'Diverging'
+a_sub_domain_LUT.UseBelowRangeColor = 0
+a_sub_domain_LUT.BelowRangeColor = [0.0, 0.0, 0.0]
+a_sub_domain_LUT.UseAboveRangeColor = 0
+a_sub_domain_LUT.AboveRangeColor = [1.0, 1.0, 1.0]
+a_sub_domain_LUT.NanColor = [1.0, 1.0, 0.0]
+a_sub_domain_LUT.Discretize = 1
+a_sub_domain_LUT.NumberOfTableValues = 256
[…]

### 2019-10-10 project/data/gen_data.sh

@@ -34,6 +34,7 @@ do
     echo "Running simulation: ${output}"
     set_params_f $visc $dens $inflow
     mkdir -p "${ROOT_DATA_DIR}/${output}"
+    echo "${dens}, ${visc}, ${inflow}" > ${ROOT_DATA_DIR}/${output}/params.txt
     cd "${ROOT_DATA_DIR}/${output}"
     mpirun -np ${MPI_NP} ${FLOW_EXEC} "${CONFIG_FILE}" "${GEOMETRY_DATA}"
     cd - > /dev/null

### 2019-10-10 project/data/gen_dataconf_files.py

@@ -1,0 +1,65 @@
+#!/usr/bin/env python
+import os
+import sys
+import re
+
+def key_func(obj1):
+    l = re.findall(r'\d+', obj1)
+    return int(l[0])
+
+def main():
+    params_file = sys.argv[1]
+    root_dir = sys.argv[2]
+
+    prexises = set()
+    with open(params_file, 'r') as handle:
+        handle.readline()
+        prefix = handle.readline().rstrip('\n').split(',')[-1].strip()
+        while prefix:
+            prexises.add(prefix)
+            prefix = handle.readline().rstrip('\n').split(',')[-1].strip()
+
+    print('Prefixes:', ', '.join(prexises))
+
+    for pref in prexises:
+        print('Handling prefix: ', pref)
+
+        dirs = [os.path.join(root_dir, d) for d in os.listdir(root_dir)
+                if os.path.isdir(os.path.join(root_dir, d)) and str(d).startswith(pref)]
+
+        print('Directories with thie prefix:', ', '.join(dirs))
+
+        dataconf_file_name = os.path.join(root_dir, pref + '_dataconf.txt')
+        with open(dataconf_file_name, 'w') as config_handle:
+            print('Creating dataconf file', dataconf_file_name)
+            if pref == 'c':
+                config_handle.write('plain\n')
+
+            if pref == 'vd':
+                config_handle.write('fluid\n')
+
+            if pref == 's':
+                config_handle.write('speed\n')
+           
+            for sim_dir in dirs:
+                img_dir = os.path.join(sim_dir, 'images')
+                params_file = os.path.join(sim_dir, 'params.txt')
+
+                params = open(params_file, 'r').readline().rstrip('\n').split(',')
+
+                imgs = os.listdir(img_dir)
+                imgs.sort(key=key_func)
+
+                for a, b in zip(imgs[0:-1],imgs[1:]):
+                    a = os.path.join(os.path.basename(sim_dir), 'images', a)
+                    b = os.path.join(os.path.basename(sim_dir), 'images', b)
+                    if pref == 'c':
+                        config_handle.write('{}, {}\n'.format(a,b))
+                    if pref == 'vd':
+                        config_handle.write('{}, {}, {}, {}\n'.format(a, b, params[0], params[1]))
+                    if pref == 's':
+                        config_handle.write('{}, {}, {}\n'.format(a, b, params[2]))
+
+
+if __name__ == '__main__':
+    main() 

### 2019-10-10 project/data/anim.py
Addign a script that can render all of the image data

@@ -1,10 +1,12 @@
 #### import the simple module from the paraview
 from paraview.simple import *
+
 #### disable automatic camera reset on 'Show'
 paraview.simple._DisableFirstRenderCameraReset()
 
 # create a new 'XML Partitioned Unstructured Grid Reader'
-c_1_solution0 = XMLPartitionedUnstructuredGridReader(FileName=['<!file_place!>'])
+c_1_solution0 = XMLPartitionedUnstructuredGridReader(FileName=['<file_place>'])
+
 c_1_solution0.CellArrayStatus = ['Material Id', '_remote_index_', '_sub_domain_']
 c_1_solution0.PointArrayStatus = ['p', 'u', 'v']
 
@@ -20,7 +22,7 @@ SetActiveSource(c_1_solution0)
 # get active view
 renderView1 = GetActiveViewOrCreate('RenderView')
 # uncomment following to set a specific view size
-# renderView1.ViewSize = [1567, 782]
+renderView1.ViewSize = [1567, 782]
 
 # get color transfer function/color map for 'a_sub_domain_'
 a_sub_domain_LUT = GetColorTransferFunction('a_sub_domain_')
@@ -150,7 +152,7 @@ a_sub_domain_PWF.AllowDuplicateScalars = 1
 a_sub_domain_PWF.ScalarRangeInitialized = 1
 
 # set scalar coloring
-ColorBy(c_1_solution0Display, ('POINTS', 'u'))
+ColorBy(c_1_solution0Display, ('POINTS', '<var>'))
 
 # Hide the scalar bar for this color map if no visible data is colored by it.
 HideScalarBarIfNotNeeded(a_sub_domain_LUT, renderView1)
@@ -162,7 +164,7 @@ c_1_solution0Display.RescaleTransferFunctionToDataRange(True, False)
 c_1_solution0Display.SetScalarBarVisibility(renderView1, True)
 
 # get color transfer function/color map for 'u'
-uLUT = GetColorTransferFunction('u')
+uLUT = GetColorTransferFunction('<var>')
 uLUT.LockDataRange = 0
 uLUT.InterpretValuesAsCategories = 0
 uLUT.ShowCategoricalColorsinDataRangeOnly = 0
@@ -188,7 +190,7 @@ uLUT.ActiveAnnotatedValues = []
 uLUT.IndexedColors = []
 
 # get opacity transfer function/opacity map for 'u'
[…]

### 2019-10-10 project/data/gen_data.sh

@@ -1,5 +1,9 @@
 #!/bin/bash
 
+set +e
+
+BASEDIR=$(dirname $0)
+
 PARAMS_FILE=$(realpath $1)
 CONFIG_FILE=$(realpath $2)
 GEOMETRY_DATA="$(realpath $3)/"
@@ -7,8 +11,11 @@ ROOT_DATA_DIR=$(realpath $4)
 
 # FLOW_EXEC="/home/arnaud/code_sys/Hiflow3_2.0/build/examples/flow/flow_tutorial"
 FLOW_EXEC=${FLOW_EXEC:-"/home/arnaud/code_sys/Hiflow3_2.0/build/examples/flow/flow_tutorial"}
-MPI_NP=${MPI_NP:-4}
+FLOW_EXEC=${FLOW_EXEC:-"/home/arnaud/code_sys/Hiflow3_2.0/build/examples/flow/flow_tutorial"}
 
+RENDER_SCRIPT=$(realpath "${BASEDIR}/render_images.sh")
+
+echo $RENDER_SCRIPT
 
 
 set_params_f()
@@ -17,10 +24,6 @@ set_params_f()
     sed -i -e "s#<Density>.*</Density>#<Density>$2</Density>#g" ${CONFIG_FILE}
     sed -i -e "s#<InflowSpeed>.*</InflowSpeed>#<InflowSpeed>$3</InflowSpeed>#g" ${CONFIG_FILE}
 }
-
-
-# ec="echo"
-# eval "${ec} 213"
 
 echo "Hiflow executable: " $FLOW_EXEC
 echo "MPI workers count:" $MPI_NP
@@ -37,6 +40,7 @@ do
     echo "${dens}, ${visc}, ${inflow}" > ${ROOT_DATA_DIR}/${output}/params.txt
     cd "${ROOT_DATA_DIR}/${output}"
     mpirun -np ${MPI_NP} ${FLOW_EXEC} "${CONFIG_FILE}" "${GEOMETRY_DATA}"
+		eval "sh ${RENDER_SCRIPT} ${ROOT_DATA_DIR} ${output}"
     cd - > /dev/null
     count=`expr $count + 1`
 done < <(tail -n +2 ${PARAMS_FILE} | sed -e 's/\,/ /g') 

### 2019-10-10 project/data/render_images.sh

@@ -1,0 +1,48 @@
+#!/bin/bash
+
+set +e
+
+SOLUTION_LIST=""
+PVPYTHON_EXE=${PVPYTHON_EXE:-"/usr/bin/python"}
+
+ROOT_FOLDER=$(realpath $1)
+SOLUTION_FOLDER=$2
+
+
+# Get the solution files
+for sol in $(ls ${ROOT_FOLDER}/${SOLUTION_FOLDER}/images/ | sort --general-numeric-sort -r)
+do
+		sol="${ROOT_FOLDER}/${SOLUTION_FOLDER}/${sol}"
+		SOLUTION_LIST="'${sol}', ${SOLUTION_LIST}"
+done
+echo "Solution files: ${SOLUTION_LIST}"
+sed -e "s#'<file_place>'#$SOLUTION_LIST#g" anim.py > anim_temp.py
+
+
+# render the U-Direction of velocity
+IMAGES_DEST="${ROOT_FOLDER}/${SOLUTION_FOLDER=}/images_x"
+echo "Rendeting images in $IMAGES_DEST"
+mkdir -p ${IMAGES_DEST}
+script=$(sed -e "s#<output_place>#${IMAGES_DEST}#g
+			 			 		 s#<var>#u#g" anim_temp.py)
+eval "${PVPYTHON_EXE} -c '${script}'"
+
+
+# render the V-Direction of velocity
+IMAGES_DEST="${ROOT_FOLDER}/${SOLUTION_FOLDER=}/images_y"
+echo "Rendeting images in $IMAGES_DEST"
+mkdir -p ${IMAGES_DEST}
+script=$(sed -e "s#<output_place>#${IMAGES_DEST}#g
+				 			 	 s#<var>#v#g" anim_temp.py)
+eval "${PVPYTHON_EXE} -c '${script}'"
+
+
+# render the pressure
+IMAGES_DEST="${ROOT_FOLDER}/${SOLUTION_FOLDER=}/images_p"
+echo "Rendeting images in $IMAGES_DEST"
+mkdir -p ${IMAGES_DEST}
+scirpt=$(sed -e "s#<output_place>#${IMAGES_DEST}#g
+						 		 s#<var>#p#g" anim_temp.py)
+eval "${PVPYTHON_EXE} -c '${script}'"
+
+# rm -f anim_temp.py

### 2019-10-10 project/data/cropper.py
Adding a cropper script that selects the important parts of the images

@@ -1,0 +1,35 @@
+#!/usr/bin/env python
+import os
+import sys
+import itertools
+import PIL
+from PIL import Image
+
+HEIGHT_BEGIN = 245
+HEIGHT_END = 535
+
+WIDTH_BEGIN = 0
+WIDTH_END = -1
+
+def main():
+
+    input_file = sys.argv[1]
+    output_file = sys.argv[2]
+    print("Cropping file:", input_file)
+
+    im = Image.open(input_file)
+    
+    w, h = im.size
+
+    w_begin = 0 if WIDTH_BEGIN == -1 else WIDTH_BEGIN
+    w_end = w if WIDTH_END == -1 else WIDTH_END
+    h_begin = 0 if HEIGHT_BEGIN == -1 else HEIGHT_BEGIN
+    h_end = h if HEIGHT_END == -1 else HEIGHT_END
+    
+    img_new = im.crop((w_begin, h_begin, w_end, h_end))
+
+    img_new.save(output_file)
+    
+
+if __name__ == '__main__':
+    main()

### 2019-10-10 project/data/render_images.sh

@@ -1,13 +1,24 @@
 #!/bin/bash
 
 set +e
+BASEDIR=$(dirname $0)
 
 SOLUTION_LIST=""
 PVPYTHON_EXE=${PVPYTHON_EXE:-"/usr/bin/python"}
 
+CROPPER_SCRIPT="${BASEDIR}/cropper.py"
+
 ROOT_FOLDER=$(realpath $1)
 SOLUTION_FOLDER=$2
 
+crop_images()
+{
+
+		FOLDER=$1
+
+		ls -d $FOLDER/* -1 | xargs -I "{}" python ${CROPPER_SCRIPT} "{}" "{}"
+		
+}
 
 # Get the solution files
 for sol in $(ls ${ROOT_FOLDER}/${SOLUTION_FOLDER}/images/ | sort --general-numeric-sort -r)

### 2019-10-10 project/data/cropper.py
Fixing a paragraph in the proposal

@@ -13,12 +13,6 @@ WIDTH_END = -1
 
 def main():
 
-    input_file = sys.argv[1]
-    output_file = sys.argv[2]
-    print("Cropping file:", input_file)
-
-    im = Image.open(input_file)
-    
     w, h = im.size
 
     w_begin = 0 if WIDTH_BEGIN == -1 else WIDTH_BEGIN

### 2019-10-10 project/data/render_images.sh

@@ -1,6 +1,7 @@
 #!/bin/bash
 
 set +e
+
 BASEDIR=$(dirname $0)
 
 SOLUTION_LIST=""
@@ -13,11 +14,9 @@ SOLUTION_FOLDER=$2
 
 crop_images()
 {
-
 		FOLDER=$1
-
+		echo "Cropping images in ${FOLDER}"
 		ls -d $FOLDER/* -1 | xargs -I "{}" python ${CROPPER_SCRIPT} "{}" "{}"
-		
 }
 
 # Get the solution files
@@ -30,9 +29,11 @@ echo "Solution files: ${SOLUTION_LIST}"
 sed -e "s#'<file_place>'#$SOLUTION_LIST#g" anim.py > anim_temp.py
 
 
+
 # render the U-Direction of velocity
 IMAGES_DEST="${ROOT_FOLDER}/${SOLUTION_FOLDER=}/images_x"
-echo "Rendeting images in $IMAGES_DEST"
+crop_images ${IMAGES_DEST}
+echo "Rendering images in $IMAGES_DEST"
 mkdir -p ${IMAGES_DEST}
 script=$(sed -e "s#<output_place>#${IMAGES_DEST}#g
 			 			 		 s#<var>#u#g" anim_temp.py)
@@ -41,7 +42,8 @@ eval "${PVPYTHON_EXE} -c '${script}'"
 
 # render the V-Direction of velocity
 IMAGES_DEST="${ROOT_FOLDER}/${SOLUTION_FOLDER=}/images_y"
-echo "Rendeting images in $IMAGES_DEST"
+crop_images ${IMAGES_DEST}
+echo "Rendering images in ${IMAGES_DEST}"
 mkdir -p ${IMAGES_DEST}
 script=$(sed -e "s#<output_place>#${IMAGES_DEST}#g
 				 			 	 s#<var>#v#g" anim_temp.py)
@@ -50,7 +52,8 @@ eval "${PVPYTHON_EXE} -c '${script}'"
 
 # render the pressure
 IMAGES_DEST="${ROOT_FOLDER}/${SOLUTION_FOLDER=}/images_p"
-echo "Rendeting images in $IMAGES_DEST"
+crop_images ${IMAGES_DEST}
+echo "Rendering images in ${IMAGES_DEST}"
 mkdir -p ${IMAGES_DEST}
 scirpt=$(sed -e "s#<output_place>#${IMAGES_DEST}#g
 						 		 s#<var>#p#g" anim_temp.py)

### 2019-12-02 project/config.py
Fixing the simulation

@@ -3,25 +3,52 @@ config = {}
 config['input_width'] = 1024
 config['input_height'] = 256
 
-config['g_input_nc'] = 3
-config['g_output_nc'] = 2
+config['g_input_nc'] = 3*2
+config['g_output_nc'] = 3
 
 config['g_nfg'] = 34
 config['g_layers'] = 5
 
 config['d_input_nc'] = 12
 
-config['d_nfg'] = 22
-config['d_layers'] = 4
+config['d_nfg'] = 38
+config['d_layers'] = 6
 
 config['output_dir'] = './model_output'
 
-config['evaluation_snapshots_cnt'] = 5
-config['evaluation_recursive_samples'] = 5
-config['full_simulaiton_samples'] = 5
+config['evaluation_snapshots_cnt'] = 7
+config['evaluation_recursive_samples'] = 20
+config['full_simulaiton_samples'] = 25
 
 config['lambda_L1'] = 100
 
-config['adam_lr'] = 0.001
+config['adam_lr'] = 0.0002
 config['adam_b1'] = 0.9
 config['adam_b2'] = 0.999
+
+
+# config['input_width'] = 1024
+# config['input_height'] = 256
+
+# config['g_input_nc'] = 3
+# config['g_output_nc'] = 2
+
+# config['g_nfg'] = 34
+# config['g_layers'] = 5
+
+# config['d_input_nc'] = 12
+
+# config['d_nfg'] = 22
+# config['d_layers'] = 4
+
+# config['output_dir'] = './model_output'
+
+# config['evaluation_snapshots_cnt'] = 5
+# config['evaluation_recursive_samples'] = 5
+# config['full_simulaiton_samples'] = 5
+
+# config['lambda_L1'] = 100
+
+# config['adam_lr'] = 0.001
+# config['adam_b1'] = 0.9
+# config['adam_b2'] = 0.999

### 2019-12-02 project/eval_models.sh

@@ -1,19 +1,24 @@
 #!/bin/bash
 
-MODEL_FILE=$1
-MODEL_TYPE=$2
-
-while IFS=" " read -r model_weights
-do
-    model_name=$(basename ${model_weights%".pth"})
-
-		output_dir="./eval/eval_${model_name}"
-
-		sed ./config.py -i -e "s#config\['output_dir'\]\s=\s'.*'#config['output_dir'] = '${output_dir}'#g"
-
-		echo python train.py --data ./data/generated_data/ --model-type "${MODEL_TYPE}" --test-train-split 0.8 --cuda --model-name 'c_res_l3_nfg64' --threads --batch-size 30 --shuffle --epochs 100 --lr_policy step --model-path "${model_weights}" --evaluate --no-train
-		echo $output_dir
-
-done < ${MODEL_FILE}
+MODEL_DIRS="$@"
 
 
+
+for model_dir in ${MODEL_DIRS[@]}; do
+
+    SEED=$(grep "seed" "${model_dir}/log.txt" | grep "[0-9]*" -o)
+
+    if [ $SEED ] ; then
+
+        if [ ! -d ${model_dir}/test ] ; then
+
+            echo "Evaluating ${model_dir}"
+
+            echo python train.py --data ./data/generated_data/ --model-type 'c' --model-name "unet" --threads 4 --batch-size 3 --shuffle --epochs 50 --lr_policy step --seed $SEED --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "${model_dir}_new" --evaluate --use-pressure  --no-train --model-path ${model_dir}/c_unet_*/* --no-mask
+
+        fi        
+
+        
+    fi
+    
+done

### 2019-12-02 project/evaluate.py

@@ -105,36 +105,21 @@ class Evaluator:
             else:
                 predicted = net(input_img)
 
+            target = dataset[index][1].expand(1,-1,-1,-1).to(self.device)
+
             if self.args.mask:
                 for i,j in itertools.product(range(predicted.shape[0]), range(predicted.shape[1])):
                     predicted[i][j] = self.MASK * predicted[i][j]
-                    input_img = torch.cat((torch.tensor(predicted[0][0:3]).expand(1,-1,-1,-1), self.MASK.expand(1,-1,-1,-1)), 1)
+                    input_img = torch.cat((torch.tensor(predicted.clone().detach()[0][0:3]).expand(1,-1,-1,-1), self.MASK.expand(1,-1,-1,-1)), 1)
             else:
-                input_img = predicted
-
-
-
-            target = dataset[index][1].expand(1,-1,-1,-1).to(self.device)
+                input_img = predicted.clone().detach()
+                
 
             cur_mse = self.criterionMSE(predicted, target).item()
 
-            predicted_img = self.denormalize(predicted).detach().cpu().numpy()
-            target_img = self.denormalize(target).detach().cpu().numpy()
-
-            mse += [cur_mse]
-            psnr += [10 * math.log10(1 / cur_mse)]
-            cor += [np.average(np.array([correlation(predicted_img[i], target_img[i]) for i in range(predicted_img.shape[0])]))]
-            ssim += [np.average(np.array([ssim_metr(predicted_img[i].T, target_img[i].T, multichannel=True) for i in range(predicted_img.shape[0])]))]
-
-            diff_avrg_, _, diff_max_ = imgs_perc_diff(target_img, predicted_img)
-            diff_avrg.append(diff_avrg_)
-            diff_max.append(diff_max_)
-
-            diff_x.append(imgs_perc_diff(target_img[0][0], predicted_img[0][0])[0])
-            diff_y.append(imgs_perc_diff(target_img[0][1], predicted_img[0][1])[0])
-
+            
             if not self.args.use_pressure:
-                predicted_x, predicted_y = self._prepare_tensor_img(predicted_img[0])
+                predicted_x, predicted_y = self._prepare_tensor_img(predicted[0])
                 target_x, target_y = self._prepare_tensor_img(dataset[index][1])
             else:
                 predicted_x, predicted_y, predicted_p = self._prepare_tensor_img(predicted[0])
@@ -148,6 +133,24 @@ class Evaluator:
[…]

### 2019-12-02 project/models.py

@@ -93,7 +93,7 @@ def define_D(input_nc, ndf, n_layers_D=3, norm='batch', use_sigmoid=False, init_
 
 
 
-class ResnetGenerator(nn.Module):#
+class ResnetGenerator(nn.Module):
 
     def __init__(self, input_nc, output_nc, ngf=64, norm_layer=nn.BatchNorm2d, use_dropout=True, n_blocks=4, padding_type='reflect', params=False):
         super(ResnetGenerator, self).__init__()

### 2019-12-02 project/plotter.py

@@ -175,7 +175,7 @@ def plot_recursive(model_name, mse_test, mse_train, ssim_test, ssim_train, test_
     plt.clf()
         
     
-def plot_model_comparision(self, labels, test_metr, test_metr_p, train_metr, train_metr_p, filename):
+def plot_model_comparision(metric, labels, test_metr, test_metr_p, train_metr, train_metr_p, filename):
 
   barWidth = 0.2
   spacing = 0.05
@@ -187,13 +187,15 @@ def plot_model_comparision(self, labels, test_metr, test_metr_p, train_metr, tra
 
   plt.subplot(2,1,1)
   plt.title("Test")
-  plt.barh(r1, test__metr[0], barWidth, edgecolor='black', label='Without pressure', alpha=0.5, xerr=test_metr[1])
-  plt.barh(r2, test_metr_p[1], barWidth, edgecolor='black', label='With pressure' , alpha=0.5, xerr=test_metr_p[1])
+  plt.barh(r1, test_metr[0], barWidth, edgecolor='black', label='Without pressure', alpha=0.5, xerr=test_metr[1])
+  plt.barh(r2, test_metr_p[0], barWidth, edgecolor='black', label='With pressure' , alpha=0.5, xerr=test_metr_p[1])
   plt.grid(b=True, which='major', color='#999999', linestyle='-', alpha=0.2)
   plt.minorticks_on()
   plt.grid(b=True, which='minor', color='#999999', linestyle='-', alpha=0.2)
   plt.ylabel('Model', fontweight='bold')
-  plt.yticks([r + barWidth - spacing/2 for r in range(len(metr))], x)
+
+  plt.yticks([r + barWidth - spacing/2 for r in range(len(test_metr))], labels)
+  
   plt.legend(loc='upper left', bbox_to_anchor=(0.7, 1.1), ncol=3, fancybox=True, shadow=True)
 
 
@@ -204,9 +206,12 @@ def plot_model_comparision(self, labels, test_metr, test_metr_p, train_metr, tra
   plt.grid(b=True, which='major', color='#999999', linestyle='-', alpha=0.2)
   plt.minorticks_on()
   plt.grid(b=True, which='minor', color='#999999', linestyle='-', alpha=0.2)
+
   plt.xlabel(metric.upper(), fontweight='bold')
   plt.ylabel('Model', fontweight='bold')
-  plt.yticks([r + barWidth - spacing/2 for r in range(len(metr))], x)
+
[…]

### 2019-12-02 project/train.py

@@ -389,33 +389,35 @@ if args.evaluate:
     net_g.eval()
     with torch.no_grad():
 
-        # print('===> Evaluating with test set:')
-        # evaluator.set_output_name('test')
-        # evaluator.snapshots(net_g, test_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
-        # evaluator.individual_images_performance(net_g, test_loader)
-        # evaluator.recusive_application_performance(net_g, dataset, len(train_indices) + len(val_indices) , samples=config['evaluation_recursive_samples'])
+        print('===> Evaluating with test set:')
+        evaluator.set_output_name('test')
+        evaluator.snapshots(net_g, test_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
+        evaluator.individual_images_performance(net_g, test_loader)
+        evaluator.recusive_application_performance(net_g, dataset, len(train_indices) + len(val_indices) , samples=config['evaluation_recursive_samples'])
 
-        # print('===> Evaluating with train set:')
-        # evaluator.set_output_name('train')
-        # evaluator.snapshots(net_g, train_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
-        # evaluator.individual_images_performance(net_g, train_loader)
-        # evaluator.recusive_application_performance(net_g, dataset, 5, samples=config['evaluation_recursive_samples'])
+        print('===> Evaluating with train set:')
+        evaluator.set_output_name('train')
+        evaluator.snapshots(net_g, train_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
+        evaluator.individual_images_performance(net_g, train_loader)
+        evaluator.recusive_application_performance(net_g, dataset, 5, samples=config['evaluation_recursive_samples'])
 
         if args.model_type == 'c':
             print('===> Running simulations:')
+
             evaluator.set_output_name('simulations')
             evaluator.run_full_simulation(net_g, dataset, 20, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(20))
-            # evaluator.run_full_simulation(net_g, dataset, 100, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(100))
-            # evaluator.run_full_simulation(net_g, dataset, 200, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(200))
-            # evaluator.run_full_simulation(net_g, dataset, 300, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(300))
[…]

### 2019-12-02 project/plotter.py
Developing the plotter

@@ -194,7 +194,7 @@ def plot_model_comparision(metric, labels, test_metr, test_metr_p, train_metr, t
   plt.grid(b=True, which='minor', color='#999999', linestyle='-', alpha=0.2)
   plt.ylabel('Model', fontweight='bold')
 
-  plt.yticks([r + barWidth - spacing/2 for r in range(len(test_metr))], labels)
+  plt.yticks([r + barWidth - spacing/2 for r in range(len(test_metr[0]))], labels)
   
   plt.legend(loc='upper left', bbox_to_anchor=(0.7, 1.1), ncol=3, fancybox=True, shadow=True)
 
@@ -210,7 +210,7 @@ def plot_model_comparision(metric, labels, test_metr, test_metr_p, train_metr, t
   plt.xlabel(metric.upper(), fontweight='bold')
   plt.ylabel('Model', fontweight='bold')
 
-  plt.yticks([r + barWidth - spacing/2 for r in range(len(train_metr))], labels)
+  plt.yticks([r + barWidth - spacing/2 for r in range(len(train_metr[0]))], labels)
 
   plt.savefig(filename, bbox_inches='tight')
   plt.clf()
@@ -260,7 +260,7 @@ class PlotProcessor():
                 if metric in line:
                     return float(line.split(':')[1].strip())
 
-    def get_recursive_list(self, mod, metric='psnr', test=True):
+    def get_recursive_list(self, mod, metric='psnr'):
       
       rec_dirs = []
 
@@ -270,12 +270,13 @@ class PlotProcessor():
           continue
 
         if os.path.isfile(os.path.join(mod, di, 'recursive_application.txt')):
-         rec_dirs.append(die)
+         rec_dirs.append(di)
 
       rec_lists = {}
-
+      
       for di in rec_dirs:
-        with open(os.path.isfile(os.path.join(mod, di, 'recursive_application.txt')), 'r') as fh:
+        
+        with open(os.path.join(mod, di, 'recursive_application.txt')) as fh:
           for line in fh.readlines():
             if metric in line:
               rec_lists[di] = [float(f.strip()) for f in line.split(':')[1].strip().split(',')]
@@ -339,9 +340,6 @@ class PlotProcessor():
         train_metr_err = []
         train_metr_p_err = []
 
-        print(met)
-        print(hel_d)
-        
         for mod, m_d in hel_d.items():
 
           test_metr.append(np.mean(m_d['test_without_p']))
@@ -361,39 +359,58 @@ class PlotProcessor():
         
[…]

### 2019-12-03 project/eval_models.sh
Working on the plotter

@@ -10,13 +10,13 @@ for model_dir in ${MODEL_DIRS[@]}; do
 
     if [ $SEED ] ; then
 
-        if [ ! -d ${model_dir}/test ] ; then
+        # if [ ! -d ${model_dir}/test ] ; then
 
-            echo "Evaluating ${model_dir}"
+        echo "Evaluating ${model_dir}"
 
-            echo python train.py --data ./data/generated_data/ --model-type 'c' --model-name "unet" --threads 4 --batch-size 3 --shuffle --epochs 50 --lr_policy step --seed $SEED --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "${model_dir}_new" --evaluate --use-pressure  --no-train --model-path ${model_dir}/c_unet_*/* --no-mask
+        python train.py --data ./data/generated_data/ --model-type 'c' --model-name "unet" --threads 4 --batch-size 3 --shuffle --epochs 50 --lr_policy step --seed $SEED --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "${model_dir}_new" --evaluate --use-pressure  --no-train --model-path ${model_dir}/c_unet_*/* --no-mask
 
-        fi        
+        # fi        
 
         
     fi

### 2019-12-03 project/models.py

@@ -67,7 +67,8 @@ def init_net(net, init_gain=0.02, gpu_id='cuda:0'):
 
 def define_G(input_nc, output_nc, ngf, norm='batch', use_dropout=True, init_gain=0.02, gpu_id='cuda:0', n_blocks=9, args={}):
     if args.model_path is not None:
-        net = torch.load(args.model_path).to(gpu_id)
+        # net = torch.load(args.model_path).to(gpu_id)
+        net = torch.load(args.model_path, map_location=lambda storage, loc: storage).to(gpu_id)
         return net
     else:
         norm_layer = get_norm_layer(norm_type=norm)

### 2019-12-03 project/plotter.py

@@ -376,19 +376,75 @@ class PlotProcessor():
 
 
 
+    def _averge_recursive_plot(self, metrics):
+      rec = {}
+      
+      for mod in self.get_model_dirs():
+        name = self.get_model_name(mod)
+        for metric in metrics:
+          rec.setdefault(metric, [])
+          rec[metric].append(self.get_recursive_list(mod, metric=metric))
 
-    def recursive_plot(self):
 
+
+      plt.figure(figsize=(10,13), dpi=100)
+
+      def _add_plot(rec, metric, i):
+        mats = {}
+        for vals in rec[metric]:
+          mse_lists = vals
+          for eval_type, val_list in mse_lists.items():
+            if 'recursive' not in eval_type:
+              continue
+            mats.setdefault(eval_type, [])
+            mats[eval_type].append(val_list[0:20])
+
+
+        plt.subplot(3,2,i)
+        for eval_type, eval_mat in list(mats.items()):
+          arr = np.array(eval_mat)
+          std = np.std(arr, axis=0)
+          avrg = np.average(arr, axis=0)
+          plt.plot(np.arange(len(avrg)), avrg, linewidth=1, label=eval_type)
+          # plt.fill_between(np.arange(len(avrg)), avrg+0.95*std, avrg-0.95*std, linewidth=4, linestyle='dashdot', antialiased=True, alpha=0.2)
+
+        plt.grid(True)
+        plt.legend()
+        plt.ylabel(metric)
+        plt.title('Average {} drop'.format(metric.upper()), fontsize=14)
+
+
+
+      cnt = 1
+      for metric in metrics:
+        _add_plot(rec, metric, cnt)
+        cnt += 1
+
+        
+      plt.tight_layout(rect=[0, 0.03, 1, 0.95])
+      plt.savefig(os.path.join(self.root_dir, 'average_recursive_application.png'))
+      plt.clf()
+
+
+    def averge_recursive_plot(self):
+      self._averge_recursive_plot(['psnr', 'cor', 'ssim', 'mse'])
+      
+    def recursive_plots(self):
+
+      rec = []
+      
       for mod in self.get_model_dirs():
         
         name = self.get_model_name(mod)
+        
         mse = self.get_recursive_list(mod, metric='mse')
         psnr = self.get_recursive_list(mod, metric='psnr')
         cor = self.get_recursive_list(mod, metric='cor')
[…]

### 2019-12-03 project/train.py

@@ -392,21 +392,22 @@ if args.evaluate:
         print('===> Evaluating with test set:')
         evaluator.set_output_name('test')
         evaluator.snapshots(net_g, test_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
-        evaluator.individual_images_performance(net_g, test_loader)
-        evaluator.recusive_application_performance(net_g, dataset, len(train_indices) + len(val_indices) , samples=config['evaluation_recursive_samples'])
+
+        # evaluator.individual_images_performance(net_g, test_loader)
+        # evaluator.recusive_application_performance(net_g, dataset, len(train_indices) + len(val_indices) , samples=config['evaluation_recursive_samples'])
 
         print('===> Evaluating with train set:')
         evaluator.set_output_name('train')
         evaluator.snapshots(net_g, train_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
-        evaluator.individual_images_performance(net_g, train_loader)
-        evaluator.recusive_application_performance(net_g, dataset, 5, samples=config['evaluation_recursive_samples'])
+
+        # evaluator.individual_images_performance(net_g, train_loader)
+        # evaluator.recusive_application_performance(net_g, dataset, 5, samples=config['evaluation_recursive_samples'])
 
         if args.model_type == 'c':
             print('===> Running simulations:')
 
             evaluator.set_output_name('simulations')
             evaluator.run_full_simulation(net_g, dataset, 20, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(20))
-
             evaluator.run_full_simulation(net_g, dataset, 100, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(100))
             evaluator.run_full_simulation(net_g, dataset, 200, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(200))
             evaluator.run_full_simulation(net_g, dataset, 300, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(300))
@@ -414,6 +415,9 @@ if args.evaluate:
             print('===> Evaluating recursively:')
 
             evaluator.set_output_name('recursive_i20')
+            evaluator.recusive_application_performance(net_g, dataset, 20, samples=config['evaluation_recursive_samples'])
+
+            evaluator.set_output_name('recursive_i100')
             evaluator.recusive_application_performance(net_g, dataset, 20, samples=config['evaluation_recursive_samples'])
 
             evaluator.set_output_name('recursive_i200')

### 2019-12-04 project/train.py
Fixing train a little bit

@@ -392,16 +392,12 @@ if args.evaluate:
         print('===> Evaluating with test set:')
         evaluator.set_output_name('test')
         evaluator.snapshots(net_g, test_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
-
-        # evaluator.individual_images_performance(net_g, test_loader)
-        # evaluator.recusive_application_performance(net_g, dataset, len(train_indices) + len(val_indices) , samples=config['evaluation_recursive_samples'])
+        evaluator.individual_images_performance(net_g, test_loader)
 
         print('===> Evaluating with train set:')
         evaluator.set_output_name('train')
         evaluator.snapshots(net_g, train_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
-
-        # evaluator.individual_images_performance(net_g, train_loader)
-        # evaluator.recusive_application_performance(net_g, dataset, 5, samples=config['evaluation_recursive_samples'])
+        evaluator.individual_images_performance(net_g, train_loader)
 
         if args.model_type == 'c':
             print('===> Running simulations:')

### 2019-12-05 project/generate_simulations.sh
Adding the scripts for the sikulations

@@ -1,0 +1,26 @@
+#!/usr/bin/env sh
+
+
+
+for res_dir in $(ls -1v -d1 results_c/plain_results_*); do
+
+    if [ ! -d "${res_dir}"/simulations/full_simulation ]; then
+        continue
+    fi
+
+    
+    for rec_dir in $(ls -1v -d1 "${res_dir}"/recursive_i*) ; do
+        ./make_anim.py "$rec_dir/x_recursive.gif" $(ls -1v $rec_dir/recursive/x_*)
+        ./make_anim.py "$rec_dir/y_recursive.gif" $(ls -1v $rec_dir/recursive/y_*)
+    done
+
+    
+    
+    for sim_dir in $(ls -1v -d1 "${res_dir}"/simulations/full_simulation/simulation_*) ; do
+        ./make_anim.py "$sim_dir/x_simulation.gif" $( ls -1v $sim_dir/x_step_*)
+        ./make_anim.py "$sim_dir/y_simulation.gif" $( ls -1v $sim_dir/y_step_*)
+        [ -f "$sim_dir/p_step_1.png" ] &&  ./make_anim.py "$sim_dir/p_simulation.gif" $( ls -1v $sim_dir/p_step_*)
+    done    
+
+done
+

### 2019-12-05 project/make_anim.py

@@ -1,0 +1,21 @@
+#!/usr/bin/env python
+
+
+import sys
+import os
+
+import imageio
+from pygifsicle import optimize
+
+
+def main():
+    
+    with imageio.get_writer(sys.argv[1], mode='I') as writer:
+        for filename in sys.argv[2:]:
+            image = imageio.imread(filename)
+            writer.append_data(image)
+            
+    optimize(sys.argv[1])
+
+if __name__ == '__main__':
+    main()

### 2019-12-06 project/plotter.py
Fixes in the plotter

@@ -229,12 +229,15 @@ class PlotProcessor():
             with suppress(FileExistsError):
                 os.mkdir(os.path.join(mod, 'vis'))
 
+
     def get_model_dirs(self):
         return [os.path.join(self.root_dir, model_dir) for model_dir in os.listdir(self.root_dir)
                 if os.path.isdir(os.path.join(self.root_dir, model_dir))]
 
+
     def get_vis_dir(self, mod):
         return os.path.join(mod, 'vis')
+
 
     def get_model_name(self, mod):
 
@@ -251,14 +254,17 @@ class PlotProcessor():
             return os.path.basename(l[0])
 
 
-    def get_model_metric(self, mod, metric='psnr', test=True):
+    def get_model_metric(self, mod, metric='psnr', test=True, avrg=True):
         file_loc = os.path.join(mod,
                                 'test' if test else 'train',
                                 'metrics_avrg.txt')
+
+        pref = "Avrg " if avrg else "Var "
         with open(file_loc, 'r') as fh:
             for line in fh.readlines():
-                if metric in line:
+                if (pref + metric) in line:
                     return float(line.split(':')[1].strip())
+
 
     def get_recursive_list(self, mod, metric='psnr'):
       
@@ -278,15 +284,16 @@ class PlotProcessor():
         
         with open(os.path.join(mod, di, 'recursive_application.txt')) as fh:
           for line in fh.readlines():
-            if metric in line:
+            if line.startswith(metric):
               rec_lists[di] = [float(f.strip()) for f in line.split(':')[1].strip().split(',')]
 
       return rec_lists
 
+
     def val_losses(self):
         for mod in self.get_model_dirs():
             model_name = self.get_model_name(mod)
-            print('Generating plot for {}'.format(model_name))
+            print('Generating validation loss plot for {}'.format(model_name))
             if os.path.isfile(os.path.join(mod, 'val_losses_test.txt')):
                 plot_val_res(os.path.join(mod, 'val_losses_test.txt'),
                              model_name,
@@ -299,7 +306,7 @@ class PlotProcessor():
     def train_losses(self):
         for mod in self.get_model_dirs():
             model_name = self.get_model_name(mod)
[…]

### 2019-12-06 progress_update/figs/number_answer/fig.tex
Adding the number answer

\documentclass[border=5mm]{standalone}
\usepackage{tikz}
\usetikzlibrary{shadows}
\usetikzlibrary{shapes}

\begin{document}
\tikzset{
  cascaded/.style = {
    general shadow = {
      shadow scale = 1,
      shadow xshift = -2ex,
      shadow yshift = 2ex,
      draw,
      thick,
      fill = white},
    general shadow = {
      shadow scale = 1,
      shadow xshift = -1ex,
      shadow yshift = 1ex,
      draw,
      thick,
      fill = white},
    fill = white, 
    draw,
    thick,
    minimum width = 2.5cm,
    minimum height = 1.3cm},
  roundnode/.style={circle, draw=green!60, fill=green!5, very thick, minimum width = 0.6cm, minimum height = 0.6cm},
  squarednode/.style={rectangle, draw=green!60, fill=green!5, very thick, minimum width = 2.5cm, minimum height = 1.3cm}
}

\begin{tikzpicture}
  \node[cascaded,label=below:Time $t$] (time_t) at (0,0) {};
  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net) at (4,0) {Network};
  \node[cascaded,label=below:Time $t+1$] (time_t_1) at (8,0) {};

  \draw [->,line width=1pt, shorten >=3pt, shorten <=9pt] (time_t) edge (net);
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net) edge (time_t_1);

  \node[text width=1cm,align=center] (x_y) at (time_t.center) {Input\\ channels};
  \node[text width=1cm,align=center] (x_y_1) at (time_t_1.center) {Otput\\ channels};

  q\node[roundnode] (number) at (-1, -2.3) {$3.14$};
  \node[squarednode] (grid) at (2, -2.3) {Constant channel};

  \draw [->,line width=1pt, shorten >=3pt, shorten <=4pt] (number.east) -- (grid.west);
  \draw [->,line width=1pt, shorten >=3pt, shorten <=4pt] (grid.north) -- (2,0);
\end{tikzpicture}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-12-06 progress_update/figs/number_quest/fig.tex
Adding the number question

--- 2019-12-06 progress_update/figs/number_answer/fig.tex
@@
     minimum height = 1.3cm},
-  roundnode/.style={circle, draw=green!60, fill=green!5, very thick, minimum width = 0.6cm, minimum height = 0.6cm},
-  squarednode/.style={rectangle, draw=green!60, fill=green!5, very thick, minimum width = 2.5cm, minimum height = 1.3cm}
+  roundnode/.style={circle, draw=green!60, fill=green!5, very thick, minimum width = 0.6cm, minimum height = 0.6cm}
 }
+\begin{tikzpicture}
 
-\begin{tikzpicture}
   \node[cascaded,label=below:Time $t$] (time_t) at (0,0) {};
+
   \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net) at (4,0) {Network};
+
   \node[cascaded,label=below:Time $t+1$] (time_t_1) at (8,0) {};
@@
 
-  q\node[roundnode] (number) at (-1, -2.3) {$3.14$};
-  \node[squarednode] (grid) at (2, -2.3) {Constant channel};
+  \node[roundnode] (number) at (0, -2.3) {$3.14$};
 
-  \draw [->,line width=1pt, shorten >=3pt, shorten <=4pt] (number.east) -- (grid.west);
-  \draw [->,line width=1pt, shorten >=3pt, shorten <=4pt] (grid.north) -- (2,0);
+  \node[draw, circle] (quest) at (2, -0.6) {\textbf{\large ?}};
+  \draw [->,line width=1pt, shorten >=3pt, shorten <=4pt] (number.east) -- (2,-2.3) -- (2,-1);
+
 \end{tikzpicture}

### 2019-12-06 progress_update/figs/pressure_optional/fig.tex
Adding the pressure optional

\documentclass[border=5mm]{standalone}
\usepackage{tikz}
\usetikzlibrary{shadows}
\usetikzlibrary{shapes}

\begin{document}
\tikzset{
  cascaded/.style = {
    general shadow = {
      shadow scale = 1,
      shadow xshift = -1ex,
      shadow yshift = 1ex,
      draw,
      thick,
      fill = white},
    fill = white, 
    draw,
    thick,
    minimum width = 2.5cm,
    minimum height = 1.3cm},
  roundnode/.style={circle, draw=green!60, fill=green!5, very thick, minimum width = 2.5cm, minimum height = 1.3cm},
  squarednode/.style={rectangle, draw=red!60, fill=red!2, very thick, minimum width = 2.5cm, minimum height = 1.3cm},
}
\begin{tikzpicture}

  \node[cascaded,label=below:Time $t$] (time_t) at (0,0) {};

  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net) at (4,0) {Network};

  \node[cascaded,label=below:Time $t+1$] (time_t_1) at (8,0) {};

  \draw [->,line width=1pt, shorten >=3pt, shorten <=9pt] (time_t) edge (net);
  \draw [->,line width=1pt, shorten >=6pt, shorten <=6pt] (net) edge (time_t_1);

  \node[squarednode] (pressure_i) at (0, -2.3) {Pressure};
  \node[squarednode] (pressure_o) at (8, -2.3) {Pressure};

  \draw [->,line width=1pt, shorten >=3pt, shorten <=4pt] (pressure_i.east) -- (2,-2.3) -- (2,0);
  \draw [->,line width=1pt, shorten >=3pt, shorten <=4pt] (6,0) -- (6,-2.3) -- (pressure_o.west);

  \draw  [dashed] (-1.5,-1.2) rectangle (9.5,-3.4);

  \node[text width=1cm,align=center] (x_y) at (time_t.center) {$x$\&$y$ \\ Velocities};  
  \node[text width=1cm,align=center] (x_y_1) at (time_t_1.center) {$x$\&$y$ \\ Velocities};

\end{tikzpicture}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-12-06 project/eval_models.sh
Writting some presi

@@ -14,8 +14,9 @@ for model_dir in ${MODEL_DIRS[@]}; do
 
         echo "Evaluating ${model_dir}"
 
-        python train.py --data ./data/generated_data/ --model-type 'c' --model-name "unet" --threads 4 --batch-size 3 --shuffle --epochs 50 --lr_policy step --seed $SEED --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "${model_dir}_new" --evaluate --use-pressure  --no-train --model-path ${model_dir}/c_unet_*/* --no-mask
-
+        echo python train.py --data ./data/generated_data/ --model-type 'c' --model-name "unet" --threads 4 --batch-size 3 --shuffle --epochs 50 --lr_policy step --seed $SEED --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "${model_dir}_new" --evaluate --use-pressure  --no-train --model-path ${model_dir}/c_unet_*/* --no-mask
+        exit
+        
         # fi        
 
         

### 2019-12-06 project/plotter.py

@@ -27,7 +27,11 @@ from torch.utils.data import DataLoader
 from torch.utils.data.sampler import SubsetRandomSampler
 
 import numpy as np
+
+import matplotlib
+if 'DISPLAY' not in os.environ: matplotlib.use('agg')
 from matplotlib import pyplot as plt
+
 
 from torchsummary import summary
 

### 2019-12-08 project/plotter.py
Plotting evrythign now

@@ -501,10 +501,10 @@ def main():
 
     plotter = PlotProcessor(args)
 
-    # plotter.val_losses()
-    # plotter.train_losses()
-    # plotter.matrics_comp()
-    # plotter.recursive_plots()
+    plotter.val_losses()
+    plotter.train_losses()
+    plotter.matrics_comp()
+    plotter.recursive_plots()
     plotter.averge_recursive_plot()
 
     

### 2019-12-09 project/plotter.py
Fixes in the presi; making the font bigger

@@ -178,7 +178,9 @@ def plot_recursive(model_name, mse_test, mse_train, ssim_test, ssim_train, test_
     plt.savefig(train_file)
     plt.clf()
         
-    
+matplotlib.rc('xtick', labelsize=17) 
+matplotlib.rc('ytick', labelsize=17)
+
 def plot_model_comparision(metric, labels, test_metr, test_metr_p, train_metr, train_metr_p, filename):
 
   barWidth = 0.2
@@ -501,11 +503,13 @@ def main():
 
     plotter = PlotProcessor(args)
 
-    plotter.val_losses()
-    plotter.train_losses()
+    # plotter.val_losses()
+    # plotter.train_losses()
+
     plotter.matrics_comp()
-    plotter.recursive_plots()
-    plotter.averge_recursive_plot()
+
+    # plotter.recursive_plots()
+    # plotter.averge_recursive_plot()
 
     
 

### 2019-12-09 project/dataloader.py
Fixing the mask normalization

@@ -88,12 +88,13 @@ class SimulationDataSet(data.Dataset):
         transform_list_b = [transforms.ToTensor()]
 
         if args.mask:
+            
             if args.use_pressure:
-                transform_list_a.append(transforms.Normalize((0.5, 0.5, 0.5, 0.0),(0.5, 0.5, 0.5, 1.0)))
-                transform_list_b.append(transforms.Normalize((0.5, 0.5, 0.5),(0.5, 0.5, 0.5)))
+                transform_list_a.append(transforms.Normalize((0.5, 0.5, 0.5, 0.0), (0.5, 0.5, 0.5, 1.0)))
+                transform_list_b.append(transforms.Normalize((0.5, 0.5, 0.5), (0.5, 0.5, 0.5)))
             else:
                 transform_list_a.append(transforms.Normalize((0.5, 0.5, 0.0),(0.5, 0.5, 1.0)))
-                transform_list_b.append(transforms.Normalize((0.5, 0.5),(0.5, 0.5)))
+                transform_list_b.append(transforms.Normalize((0.5, 0.5), (0.5, 0.5)))
         else:
             if args.use_pressure:
                 transform_list_a.append(transforms.Normalize((0.5, 0.5, 0.5),(0.5, 0.5, 0.5)))
@@ -164,23 +165,29 @@ class SimulationDataSet(data.Dataset):
             a_p = load_img(os.path.join(self.root_dir, a_path[2]), size=self.size)
 
 
-        if self.args.mask:mask = self.mask_img
+        if self.args.mask: mask = self.mask_img
 
         if self.args.use_pressure:
-            if self.args.mask:
-                a = np.concatenate((a_x, a_y, a_p, mask), axis=2)
-            else:
-                a = np.concatenate((a_x, a_y, a_p), axis=2)
+            # if self.args.mask:
+            #     a = np.concatenate((a_x, a_y, a_p), axis=2)
+            # else:
+            a = np.concatenate((a_x, a_y, a_p), axis=2)
+
             b = np.concatenate((b_x, b_y, b_p), axis=2)
         else:
-            if self.args.mask:
-                a = np.concatenate([a_x, a_y, mask], axis=2)
-            else:
-                a = np.concatenate([a_x, a_y], axis=2)                
-            b = np.concatenate([b_x*mask, b_y*mask], axis=2)
+            # if self.args.mask:
+            #     a = np.concatenate([a_x, a_y], axis=2)
+            # else:
[…]

### 2019-12-09 project/evaluate.py

@@ -9,7 +9,9 @@ import itertools
 
 import torch
 import torch.nn as nn
+import torchvision.transforms as transforms
 import numpy as np
+
 
 from utils import mkdir
 from utils import correlation
@@ -28,6 +30,8 @@ except ImportError:
         return 0.3
 
 
+# http://www.wikicfp.com/cfp/servlet/event.showcfp?eventid=95018&copyownerid=127295
+
 
 class Evaluator:
 
@@ -44,16 +48,21 @@ class Evaluator:
         if self.args.mask:
             self.MASK = MASK
 
-        if args.rgb:
+        if self.args.mask:
             if args.use_pressure:
-                self.denormalize = UnNormalize([0.5]*9,[0.5]*9)
+                self.denormalize_input = UnNormalize([0.5, 0.5, 0.5, 0.0], [0.5, 0.5, 0.5, 1.0])
             else:
-                self.denormalize = UnNormalize([0.5]*6,[0.5]*6)
+                self.denormalize_input = UnNormalize([0.5, 0.5, 0.0], [0.5, 0.5, 1.0])
         else:
             if args.use_pressure:
-                self.denormalize = UnNormalize([0.5]*3, [0.5]*3)
+                self.denormalize_input = UnNormalize([0.5, 0.5, 0.5], [0.5, 0.5, 0.5])
             else:
-                self.denormalize = UnNormalize([0.5]*2, [0.5]*2)
+                self.denormalize_input = UnNormalize([0.5, 0.5], [0.5, 0.5])
+
+        if args.use_pressure:
+            self.denormalize_output = UnNormalize([0.5, 0.5, 0.5], [0.5, 0.5, 0.5])
+        else:
+            self.denormalize_output = UnNormalize([0.5, 0.5], [0.5, 0.5])
 
 
     def set_output_name(self, name):
@@ -135,8 +144,8 @@ class Evaluator:
                            os.path.join(path, 'y_recursive_{}.png'.format(index - start_index)))
 
 
-            predicted_img = self.denormalize(predicted).detach().cpu().numpy()
-            target_img = self.denormalize(target).detach().cpu().numpy()
+            predicted_img = self.denormalize_output(predicted).detach().cpu().numpy()
+            target_img = self.denormalize_input(target).detach().cpu().numpy()
 
             
             mse += [cur_mse]
@@ -195,8 +204,8 @@ class Evaluator:
 
             cur_mse = self.criterionMSE(predicted, real_b).item()
 
[…]

### 2019-12-09 progress_update/figs/recursive/fig.tex

--- 2019-12-06 progress_update/figs/number_quest/fig.tex
@@
-\documentclass[border=5mm]{standalone}
+\documentclass[border={7pt 0pt 0pt 4pt}]{standalone}
 \usepackage{tikz}
@@
 
+  \draw [dashed, draw=blue!80, fill=blue!4, opacity=1] (-2, 1.5) rectangle (1.7, -1.3);
+
   \node[cascaded,label=below:Time $t$] (time_t) at (0,0) {};
-
   \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net) at (4,0) {Network};
-
   \node[cascaded,label=below:Time $t+1$] (time_t_1) at (8,0) {};
-
   \draw [->,line width=1pt, shorten >=3pt, shorten <=9pt] (time_t) edge (net);
@@
 
-  \node[text width=1cm,align=center] (x_y) at (time_t.center) {Input\\ channels};
-  \node[text width=1cm,align=center] (x_y_1) at (time_t_1.center) {Otput\\ channels};
+  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net_1) at (4,-3) {Network};
+  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (time_t_1.south) -- (8, -1.5) -- (0, -1.5) -- (0, -3) -- (net_1.west);
+  \node[cascaded,label=below:Time $t+2$] (time_1_t_1) at (8,-3) {};
+  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net_1) edge (time_1_t_1);
 
-  \node[roundnode] (number) at (0, -2.3) {$3.14$};
-
-  \node[draw, circle] (quest) at (2, -0.6) {\textbf{\large ?}};
-  \draw [->,line width=1pt, shorten >=3pt, shorten <=4pt] (number.east) -- (2,-2.3) -- (2,-1);
+  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net_2) at (4,-6) {Network};
+  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (time_1_t_1.south) -- (8, -4.5) -- (0, -4.5) -- (0, -6) -- (net_2.west);
+  \node[cascaded,label=below:Time $t+3$] (time_2_t_1) at (8,-6) {};
+  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net_2) edge (time_2_t_1);
 

### 2019-12-09 progress_update/figs/simple_eval/fig.tex

--- 2019-12-09 progress_update/figs/recursive/fig.tex
@@
 
-  \draw [dashed, draw=blue!80, fill=blue!4, opacity=1] (-2, 1.5) rectangle (1.7, -1.3);
+  \draw [dashed, draw=blue!80, fill=blue!4, opacity=1] (-2, 1.5) rectangle (1.7, -7.6);
 
@@
   \node[cascaded,label=below:Time $t+1$] (time_t_1) at (8,0) {};
+
   \draw [->,line width=1pt, shorten >=3pt, shorten <=9pt] (time_t) edge (net);
@@
 
+  \node[cascaded,label=below:Time $t$] (time_1_t) at (0,-3) {};
   \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net_1) at (4,-3) {Network};
-  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (time_t_1.south) -- (8, -1.5) -- (0, -1.5) -- (0, -3) -- (net_1.west);
-  \node[cascaded,label=below:Time $t+2$] (time_1_t_1) at (8,-3) {};
+  \node[cascaded,label=below:Time $t+1$] (time_1_t_1) at (8,-3) {};
+  \draw [->,line width=1pt, shorten >=3pt, shorten <=9pt] (time_1_t) edge (net_1);
   \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net_1) edge (time_1_t_1);
 
+  \node[cascaded,label=below:Time $t$] (time_2_t) at (0,-6) {};
   \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net_2) at (4,-6) {Network};
-  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (time_1_t_1.south) -- (8, -4.5) -- (0, -4.5) -- (0, -6) -- (net_2.west);
-  \node[cascaded,label=below:Time $t+3$] (time_2_t_1) at (8,-6) {};
+  \node[cascaded,label=below:Time $t+1$] (time_2_t_1) at (8,-6) {};
+  \draw [->,line width=1pt, shorten >=3pt, shorten <=9pt] (time_2_t) edge (net_2);
   \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net_2) edge (time_2_t_1);

### 2019-12-09 project/train_models.sh
updating the train script

@@ -4,8 +4,13 @@
 NGF=32
 LAYERS=5
 MODEL_CNT=${MODEL_CNT:-10}
-
 NETS=()
+
+MASK=${MASK:-"--no-mask"}
+CUDA=${CUDA:-"--cuda"}
+
+EPOCHS=${EPOCHS:-30}
+
 
 while [ "$1" != "" ]; do
     
@@ -65,6 +70,14 @@ while [ "$1" != "" ]; do
 done
 
 
+echo "MASK: " $MASK
+echo "CUDA: " $CUDA
+echo "MODEL_CNT: " $MODEL_CNT
+echo "NETS: " ${NETS[@]}
+echo "EPOCHS: " ${EPOCHS}
+
+
+
 # some_command &
 # P1=$!
 # other_command &
@@ -86,7 +99,7 @@ do
 	if [ ! -z "$PRESSURE" ]; then
             for i in $(seq 1 ${MODEL_CNT}); do
                 
-                python train.py --data ./data/generated_data/ --model-type 'c' --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs 50 --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_c/plain_results_$i_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS} --use-pressure  --no-train
+                python train.py --data ./data/generated_data/ --model-type 'c' ${CUDA} --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs ${EPOCHS} --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_c/plain_results_$i_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS} --use-pressure  ${MASK}
 
 	    done
         fi
@@ -95,7 +108,7 @@ do
         if [ ! -z "$NO_PRESSURE" ]; then
             for i in $(seq 1 ${MODEL_CNT}); do
                 
[…]

### 2019-12-15 project/plotter.py
Wraping up the progress presi

@@ -188,7 +188,7 @@ def plot_model_comparision(metric, labels, test_metr, test_metr_p, train_metr, t
   r1 = np.arange(len(test_metr[0]))
   r2 = [x + barWidth + spacing for x in r1]
   
-  plt.figure(figsize=(11, 10), dpi=100)
+  plt.figure(figsize=(9,12), dpi=100)
   plt.suptitle("Models comparison")
 
   plt.subplot(2,1,1)
@@ -428,7 +428,7 @@ class PlotProcessor():
           
       
       for mod, rec in list(model_met.items()):
-        plt.figure(figsize=(10,13), dpi=100)
+        plt.figure(figsize=(11,10), dpi=100)
 
         cnt = 1
         for metric in metrics:
@@ -509,7 +509,7 @@ def main():
     plotter.matrics_comp()
 
     # plotter.recursive_plots()
-    # plotter.averge_recursive_plot()
+    plotter.averge_recursive_plot()
 
     
 

### 2020-01-06 project/data/render_images.sh
Adding the dumass presentaiton

@@ -5,8 +5,7 @@ set +e
 BASEDIR=$(dirname $0)
 
 SOLUTION_LIST=""
-# PVPYTHON_EXE=${PVPYTHON_EXE:-"/home/arnaud/temp/Snap/ParaView-5.2.0-Qt4-OpenGL2-MPI-Linux-64bit/bin/pvpython"}
-PVPYTHON_EXE=${PVPYTHON_EXE:-"/home/arnaud/Downloads/ParaView-5.2.0-Qt4-OpenGL2-MPI-Linux-64bit/bin/pvpython"}
+PVPYTHON_EXE=${PVPYTHON_EXE:-"/home/arnaudov/code/ParaView-5.2.0-Qt4-OpenGL2-MPI-Linux-64bit/bin/pvpython"}
 
 CROPPER_SCRIPT="${BASEDIR}/cropper.py"
 
@@ -28,12 +27,15 @@ do
     SOLUTION_LIST="'${sol}', ${SOLUTION_LIST}"
 done
 # echo "Solution files: ${SOLUTION_LIST}"
-sed -e "s#'<file_place>'#$SOLUTION_LIST#g" anim.py > anim_temp.py
+# echo $SOLUTION_LIST
+echo "s#'<file_place>'#$SOLUTION_LIST#g" > command.txt
+sed -f command.txt anim.py > anim_temp.py
 
 
-# render the U-Direction of velocity
+
+# render the X-Direction of velocity
 IMAGES_DEST="${ROOT_FOLDER}/${SOLUTION_FOLDER}/images_x"
-# echo "Rendering images in $IMAGES_DEST"
+echo "Rendering images in $IMAGES_DEST"
 mkdir -p ${IMAGES_DEST}
 sed -e "s#<output_place>#${IMAGES_DEST}/flow.png#g
         s#<var>#u#g" anim_temp.py > anim_temp_x.py
@@ -41,7 +43,7 @@ eval "${PVPYTHON_EXE} anim_temp_x.py"
 crop_images ${IMAGES_DEST}
 
 
-# render the U-Direction of velocity
+# render the Y-Direction of velocity
 IMAGES_DEST="${ROOT_FOLDER}/${SOLUTION_FOLDER}/images_y"
 echo "Rendering images in $IMAGES_DEST"
 mkdir -p ${IMAGES_DEST}
@@ -51,9 +53,9 @@ eval "${PVPYTHON_EXE} anim_temp_y.py"
 crop_images ${IMAGES_DEST}
 
 
[…]

### 2020-01-14 cluster/time_table.tex
Adding the cluster cpu time estimates

% Created 2020-01-14 Tue 11:33
% Intended LaTeX compiler: pdflatex
\documentclass{llncs}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{minted}
\usepackage[english]{babel}
\usepackage{cite}
\usepackage{parskip}
\usepackage{pgfgantt}
\usepackage{svg}
\usepackage{color}
\usepackage{tikz}
\institute{Karlsruhe Institute of Technology,\\Kaiserstrasse 12,76131 Karlsruhe, Germany\\ \url{http://www.kit.edu/english/}}
\selectlanguage{english}
\author{Stanislav Arnaudov}
\date{<14-01-2020>}
\title{Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks}
\hypersetup{
 pdfauthor={Stanislav Arnaudov},
 pdftitle={Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.1 (Org mode 9.2.1)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section{Timing experiments}
\label{sec:orgf979350}

In order to justify the requested resources, we've performed some preliminary experiments to see how much time our models need for training. Without getting into too much detail, we have three types of models that are to be evaluated -- constant (C), inflow speed (S) and viscosity-density (VD). Each model type has an estimated training time (ETT) and a certain number of tries because we also want to try different hyper-parameters. All of the models have to be trained on GPU nodes. This means that for one hour of training time, we need 48 hours of CPU time.

The total time for a model type is calculated as SUM=TRIES x ETT x 48. We've also added 20\% overestimate to the expected total time, just to be sure that we can train our models. The following table summarizes our estimations:

\begin{center}
\begin{tabular}{l|lllllr|lll}
Model type &  &  & ETT &  &  & Tries &  &  & Sum\\
\hline
C &  &  & 5 h &  &  & 10 &  &  & 2 400 cpu-h\\
S &  &  & 70h &  &  & 10 &  &  & 33 600 cpu-h\\
VD &  &  & 350h &  &  & 10 &  &  & 168 000 cpu-h\\
\hline
Total: &  &  &  &  &  &  &  &  & 204 000 cpu-h\\
+ 20\% &  &  &  &  &  &  &  &  & \(\approx\) 250 000 cpu-h\\
\hline
\end{tabular}
\end{center}
\end{document}

### 2020-01-14 project/generate_simulations.sh

@@ -8,7 +8,7 @@ for res_dir in $(ls -1v -d1 results_c/plain_results_*); do
         continue
     fi
 
-    
+        
     for rec_dir in $(ls -1v -d1 "${res_dir}"/recursive_i*) ; do
         ./make_anim.py "$rec_dir/x_recursive.gif" $(ls -1v $rec_dir/recursive/x_*)
         ./make_anim.py "$rec_dir/y_recursive.gif" $(ls -1v $rec_dir/recursive/y_*)

### 2020-01-14 project/plotter.py

@@ -37,6 +37,8 @@ from torchsummary import summary
 
 plt.style.use('ggplot')
 plt.rcParams.update({'figure.max_open_warning': 0})
+matplotlib.rc('xtick', labelsize=17) 
+matplotlib.rc('ytick', labelsize=17)
 
 def rchop(thestring, ending):
   if thestring.endswith(ending):
@@ -178,8 +180,7 @@ def plot_recursive(model_name, mse_test, mse_train, ssim_test, ssim_train, test_
     plt.savefig(train_file)
     plt.clf()
         
-matplotlib.rc('xtick', labelsize=17) 
-matplotlib.rc('ytick', labelsize=17)
+
 
 def plot_model_comparision(metric, labels, test_metr, test_metr_p, train_metr, train_metr_p, filename):
 
@@ -188,10 +189,10 @@ def plot_model_comparision(metric, labels, test_metr, test_metr_p, train_metr, t
   r1 = np.arange(len(test_metr[0]))
   r2 = [x + barWidth + spacing for x in r1]
   
-  plt.figure(figsize=(9,12), dpi=100)
+  plt.figure(figsize=(12,8), dpi=100)
   plt.suptitle("Models comparison")
 
-  plt.subplot(2,1,1)
+  # plt.subplot(2,1,1)
   plt.title("Test")
   plt.barh(r1, test_metr[0], barWidth, edgecolor='black', label='Without pressure', alpha=0.5, xerr=test_metr[1])
   plt.barh(r2, test_metr_p[0], barWidth, edgecolor='black', label='With pressure' , alpha=0.5, xerr=test_metr_p[1])
@@ -205,18 +206,18 @@ def plot_model_comparision(metric, labels, test_metr, test_metr_p, train_metr, t
   plt.legend(loc='upper left', bbox_to_anchor=(0.7, 1.1), ncol=3, fancybox=True, shadow=True)
 
 
-  plt.subplot(2,1,2)
-  plt.title("Train")
-  plt.barh(r1, train_metr[0], barWidth, edgecolor='black', label='Without pressure', alpha=0.5, xerr=train_metr[1])
-  plt.barh(r2, train_metr_p[0], barWidth, edgecolor='black', label='With pressure', alpha=0.5, xerr=train_metr_p[1])
-  plt.grid(b=True, which='major', color='#999999', linestyle='-', alpha=0.2)
-  plt.minorticks_on()
[…]

### 2020-01-14 project/train_models.sh

@@ -99,7 +99,7 @@ do
 	if [ ! -z "$PRESSURE" ]; then
             for i in $(seq 1 ${MODEL_CNT}); do
                 
-                python train.py --data ./data/generated_data/ --model-type 'c' ${CUDA} --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs ${EPOCHS} --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_c/plain_results_$i_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS} --use-pressure  ${MASK}
+                echo python train.py --data ./data/generated_data/ --model-type 'c' ${CUDA} --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs ${EPOCHS} --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_c/plain_results_$i_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS} --use-pressure  ${MASK}
 
 	    done
         fi
@@ -108,7 +108,7 @@ do
         if [ ! -z "$NO_PRESSURE" ]; then
             for i in $(seq 1 ${MODEL_CNT}); do
                 
-                python train.py --data ./data/generated_data/ --model-type 'c' ${CUDA} --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs ${EPOCHS} --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_c/plain_results_$i_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS} ${MASK}
+                echo python train.py --data ./data/generated_data/ --model-type 'c' ${CUDA} --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs ${EPOCHS} --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_c/plain_results_$i_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS} ${MASK}
                 
 	    done
         fi

### 2020-01-14 project/data/anim_new.py
Addign the new aniamation script

@@ -1,0 +1,233 @@
+#### import the simple module from the paraview
+from paraview.simple import *
+
+#### disable automatic camera reset on 'Show'
+paraview.simple._DisableFirstRenderCameraReset()
+
+# create a new 'XML Partitioned Unstructured Grid Reader'
+c_1_solution0 = XMLPartitionedUnstructuredGridReader(FileName=['<file_place>'])
+
+c_1_solution0.CellArrayStatus = ['Material Id', '_remote_index_', '_sub_domain_']
+c_1_solution0.PointArrayStatus = ['p', 'u', 'v']
+
+# get animation scene
+animationScene1 = GetAnimationScene()
+
+# update animation scene based on data timesteps
+animationScene1.UpdateAnimationUsingDataTimeSteps()
+
+# set active source
+SetActiveSource(c_1_solution0)
+
+# get active view
+renderView1 = GetActiveViewOrCreate('RenderView')
+# uncomment following to set a specific view size
+renderView1.ViewSize = [1567, 782]
+
+# get color transfer function/color map for 'a_sub_domain_'
+a_sub_domain_LUT = GetColorTransferFunction('a_sub_domain_')
+a_sub_domain_LUT.LockDataRange = 0
+a_sub_domain_LUT.InterpretValuesAsCategories = 0
+a_sub_domain_LUT.ShowCategoricalColorsinDataRangeOnly = 0
+a_sub_domain_LUT.RescaleOnVisibilityChange = 0
+a_sub_domain_LUT.EnableOpacityMapping = 0
+a_sub_domain_LUT.RGBPoints = [0.0, 0.231373, 0.298039, 0.752941, 1.5, 0.865003, 0.865003, 0.865003, 3.0, 0.705882, 0.0156863, 0.14902]
+a_sub_domain_LUT.UseLogScale = 0
+a_sub_domain_LUT.ColorSpace = 'Diverging'
+a_sub_domain_LUT.UseBelowRangeColor = 0
+a_sub_domain_LUT.BelowRangeColor = [0.0, 0.0, 0.0]
+a_sub_domain_LUT.UseAboveRangeColor = 0
+a_sub_domain_LUT.AboveRangeColor = [1.0, 1.0, 1.0]
+a_sub_domain_LUT.NanColor = [1.0, 1.0, 0.0]
+a_sub_domain_LUT.Discretize = 1
+a_sub_domain_LUT.NumberOfTableValues = 256
[…]

### 2020-01-20 cluster/time_table.tex
Updates

@@
-% Created 2020-01-14 Tue 11:33
+% Created 2020-01-15 Wed 12:09
 % Intended LaTeX compiler: pdflatex
@@
 \author{Stanislav Arnaudov}
-\date{<14-01-2020>}
+\date{<15-01-2020>}
 \title{Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks}
@@
 \section{Timing experiments}
-\label{sec:orgf979350}
+\label{sec:orge340138}
 
-In order to justify the requested resources, we've performed some preliminary experiments to see how much time our models need for training.
+In order to justify the requested resources, we have performed some preliminary experiments to see how much time our models need for training.
 Without getting into too much detail, we have three types of models that are to be evaluated -- constant (C), inflow speed (S) and viscosity-density (VD).
-Each model type has an estimated training time (ETT) and a certain number of tries because we also want to try different hyper-parameters.
+Each model type has an estimated training time (ETT) and a certain number of tries because we also want to try different hyperparameters.
 All of the models have to be trained on GPU nodes.
@@
 \hline
-C &  &  & 5 h &  &  & 10 &  &  & 2 400 cpu-h\\
-S &  &  & 70h &  &  & 10 &  &  & 33 600 cpu-h\\
-VD &  &  & 350h &  &  & 10 &  &  & 168 000 cpu-h\\
+C &  &  & 10 h &  &  & 15 &  &  & 7 200 cpu-h\\
+S &  &  & 200h &  &  & 15 &  &  & 144 000 cpu-h\\
+VD &  &  & 1000h &  &  & 15 &  &  & 720 000 cpu-h\\
 \hline
-Total: &  &  &  &  &  &  &  &  & 204 000 cpu-h\\
-+ 20\% &  &  &  &  &  &  &  &  & \(\approx\) 250 000 cpu-h\\
+Total: &  &  &  &  &  &  &  &  & 871 200 cpu-h\\
++ 20\% &  &  &  &  &  &  &  &  & \(\approx\) \textbf{1 050 000 cpu-h}\\
 \hline
@@
 \end{center}
+
+Thus, the final requested time is \textbf{1 050 000} CPU hours.
 \end{document}

### 2020-01-20 project/plots/timings.py

@@ -1,0 +1,66 @@
+import matplotlib
+import matplotlib.pyplot as plt
+import os
+import sys
+import numpy as np
+
+plt.style.use('ggplot')
+plt.rcParams.update({'figure.max_open_warning': 0})
+
+def reject_outliers(data, m=2):
+    return data[abs(data - np.mean(data)) < m * np.std(data)]
+
+def main():
+    
+    predic_single_timings = [1681,1534,1485,1582,1407,1384,1384,1430,1392,1480,1530,1535,1500,1536,1480,1409,1425,1401,1381,1403,1385,1383,1379,1372,1373,1380,1377,1367,1372,1392,1378,1393,1561,1562,1479,1368,1371,1372,1379,1377,1365,1378,1373,1367,1386,1378,1378,1373,1379,1379,1375,1372,1375,1378,1401,1401,1423,1449,1395,1393,1385,1379,1378,1372,1378,1368,1373,1378,1376,1372,1378,1379,1378,1388,1383,1372,1380,1371,1372,1384,1380,1381,1392,1382,1380,1391,1367,1405,1391,1356,1377,1373,1408,1382,1375,1383,1372,1381,1376,1387,1380,1392,1389,1375,1377,1382,1369,1377,1368,1381,1384,1382,1451,1433,1378,1372,1410,1388,1366,1377,1380,1380,1373,1366,1394,1378,1379,1379,1383,1378,1453,1538,1497,1375,1361,1376,1390,1377,1381,1358,1353,1366,1380,1379,1499,1554,1530,1374,1363,1377,1376,1357,1378,1379,1374,1381,1371,1376,1376,1390,1384,1378,1377,1357,1378,1371,1364,1395,1383,1374,1379,1371,1381,1411,1375,1392,1479,1509,1499,1383,1395,1396,1362,1362,1362,1372,1390,1381,1378,1371,1365,1373,1359,1373,1378,1377,1372,1372,1379,1378,1378,1374,1381,1384,1378,1371,1392,1399,1379,1376,1378,1379,1379,1374,1379,1374,1390,1410,1395,1357,1377,1376,1384,1371,1415,1391,1378,1377,1372,1379,1386,1369,1368,1357,1371,1378,1368,1376,1378,1495,1506,1380,1372,1364,1377,1358,1388,1377,1380,1375,1419,1527,1523,1478,1372,1393,1372,1376,1378,1378,1425,1378,1373,1379,1378,1378,1372,
[…]

### 2020-01-20 project/train.py

@@ -400,13 +400,15 @@ if args.evaluate:
         evaluator.individual_images_performance(net_g, train_loader)
 
         if args.model_type == 'c':
-            print('===> Running simulations:')
+            print('===> Running simulations for c:')
 
             evaluator.set_output_name('simulations')
             evaluator.run_full_simulation(net_g, dataset, 20, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(20))
             evaluator.run_full_simulation(net_g, dataset, 100, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(100))
             evaluator.run_full_simulation(net_g, dataset, 200, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(200))
             evaluator.run_full_simulation(net_g, dataset, 300, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(300))
+
+            evaluator.run_full_simulation(net_g, dataset, 100, 300, sim_name = 'simulation_timings', saving_imgs=False)
 
             print('===> Evaluating recursively:')
 
@@ -421,3 +423,38 @@ if args.evaluate:
 
             evaluator.set_output_name('recursive_i300')
             evaluator.recusive_application_performance(net_g, dataset, 300, samples=config['evaluation_recursive_samples'])
+
+        if args.model_type == 's':
+            print('===> Running simulations for s:')
+
+            evaluator.set_output_name('simulations')
+            indices = [(1, 's'), (101, 's'), (1436, 's'), (3106, 's'), (6178, 's'), (9518, 's'), (11188, 's'), (12858, 's')]
+            for start_index in indices:
+                evaluator.run_full_simulation(net_(g, ''), dataset, start_index[0],
+                                              config['full_simulaiton_samples'],
+                                              sim_name = 'simulation_{}_i{}'.format(start_index[1], start_index[0]))
+
+            evaluator.run_full_simulation(net_g, dataset, 100, 300, sim_name = 'simulation_timings', saving_imgs=False)            
+
+            print('===> Evaluating recursively:')
+
+            indices = [(1, 's'), (101, 's'), (1436, 's'), (3106, 's'), (6178, 's'), (9518, 's'), (11188, 's'), (12858, 's')]
+            for start_index in indices:
+                evaluator.set_output_name('recursive_i20')
+                evaluator.recusive_application_performance(net_g, dataset, 20, samples=config['evaluation_recursive_samples'])
+
+                evaluator.set_output_name('recursive_i100')
[…]

### 2020-01-20 project/eval_models.sh
Implementing the error images

@@ -23,3 +23,6 @@ for model_dir in ${MODEL_DIRS[@]}; do
     fi
     
 done
+
+
+python train.py --data ./data/generated_data/ --model-type 'c' --model-name "unet" --threads 4 --batch-size 3 --shuffle --epochs 50 --lr_policy step --seed $RANDOM --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir results_c/res_1 --evaluate --use-pressure --no-train --no-mask

### 2020-01-20 project/evaluate.py

@@ -189,6 +189,14 @@ class Evaluator:
         diff_y = []
 
 
+        change_mse_x  = []
+        change_mse_y  = []
+        change_psnr_x = []
+        change_psnr_y = []
+        change_diff_x = []
+        change_diff_y = []
+        change_psnr = []
+        
         for iteration, batch in enumerate(test_dataloader, 1):
             real_a, real_b = batch[0].to(self.device), batch[1].to(self.device)
 
@@ -205,6 +213,7 @@ class Evaluator:
             cur_mse = self.criterionMSE(predicted, real_b).item()
 
             predicted = self.denormalize_output(predicted).detach().cpu().numpy()
+            real_a = self.denormalize_output(real_a).detach().cpu().numpy()
             real_b = self.denormalize_output(real_b).detach().cpu().numpy()
 
             mse += [cur_mse]
@@ -220,6 +229,54 @@ class Evaluator:
                 diff_x.append(imgs_perc_diff(real_b[i][0], predicted[i][0])[0])
                 diff_y.append(imgs_perc_diff(real_b[i][1], predicted[i][1])[0])
 
+
+            # error images
+
+            batch_change_mse  = []
+            batch_change_mse_x  = []
+            batch_change_mse_y  = []
+            batch_change_psnr_x = []
+            batch_change_psnr_y = []
+            batch_change_diff_x = []
+            batch_change_diff_y = []
+            
+            for ind in range(real_a.shape[0]):
+
+                real_change_img = np.abs(real_a[ind] - real_b[ind])
+                predicted_change_img = np.abs(predicted[ind] - real_b[ind])
+                cur_mse = (np.square(real_change_img - predicted_change_img)).mean(axis=None)
+                cur_psnr = 10 * np.log10(255.0 / np.sqrt(cur_mse))
+                batch_change_mse.append(cur_psnr)
+                
+                real_change_img_x = np.abs(real_a[ind][0] - real_b[ind][0])
+                predicted_change_img_x = np.abs(predicted[ind][0] - real_b[ind][0])
+
+                real_change_img_y = np.abs(real_a[ind][1] - real_b[ind][1])
+                predicted_change_img_y = np.abs(predicted[ind][1] - real_b[ind][1])
+
+                x_cur_mse = (np.square(real_change_img_x - predicted_change_img_x)).mean(axis=None)
[…]

### 2020-01-20 project/train.py

@@ -391,8 +391,9 @@ if args.evaluate:
 
         print('===> Evaluating with test set:')
         evaluator.set_output_name('test')
-        evaluator.snapshots(net_g, test_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
         evaluator.individual_images_performance(net_g, test_loader)
+        exit(1)
+        evaluator.snapshots(net_g, test_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
 
         print('===> Evaluating with train set:')
         evaluator.set_output_name('train')
@@ -428,30 +429,22 @@ if args.evaluate:
             print('===> Running simulations for s:')
 
             evaluator.set_output_name('simulations')
+            evaluator.run_full_simulation(net_g, dataset, 100, 300, sim_name = 'simulation_timings', saving_imgs=False)
             indices = [(1, 's'), (101, 's'), (1436, 's'), (3106, 's'), (6178, 's'), (9518, 's'), (11188, 's'), (12858, 's')]
             for start_index in indices:
                 evaluator.run_full_simulation(net_(g, ''), dataset, start_index[0],
                                               config['full_simulaiton_samples'],
                                               sim_name = 'simulation_{}_i{}'.format(start_index[1], start_index[0]))
 
-            evaluator.run_full_simulation(net_g, dataset, 100, 300, sim_name = 'simulation_timings', saving_imgs=False)            
+
 
             print('===> Evaluating recursively:')
 
             indices = [(1, 's'), (101, 's'), (1436, 's'), (3106, 's'), (6178, 's'), (9518, 's'), (11188, 's'), (12858, 's')]
             for start_index in indices:
-                evaluator.set_output_name('recursive_i20')
-                evaluator.recusive_application_performance(net_g, dataset, 20, samples=config['evaluation_recursive_samples'])
+                evaluator.set_output_name('recursive_{}_i{}'.format(start_index[1], start_index[0]))
+                evaluator.recusive_application_performance(net_g, dataset, start_index[0], samples=config['evaluation_recursive_samples'])
 
-                evaluator.set_output_name('recursive_i100')
-                evaluator.recusive_application_performance(net_g, dataset, 20, samples=config['evaluation_recursive_samples'])
-
-                evaluator.set_output_name('recursive_i200')
-                evaluator.recusive_application_performance(net_g, dataset, 200, samples=config['evaluation_recursive_samples'])
-
-                evaluator.set_output_name('recursive_i300')
[…]

### 2020-01-20 project/train_models.sh

@@ -99,7 +99,7 @@ do
 	if [ ! -z "$PRESSURE" ]; then
             for i in $(seq 1 ${MODEL_CNT}); do
                 
-                echo python train.py --data ./data/generated_data/ --model-type 'c' ${CUDA} --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs ${EPOCHS} --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_c/plain_results_$i_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS} --use-pressure  ${MASK}
+                python train.py --data ./data/generated_data/ --model-type 'c' ${CUDA} --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs ${EPOCHS} --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_c/plain_results_$i_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS} --use-pressure  ${MASK}
 
 	    done
         fi
@@ -108,7 +108,7 @@ do
         if [ ! -z "$NO_PRESSURE" ]; then
             for i in $(seq 1 ${MODEL_CNT}); do
                 
-                echo python train.py --data ./data/generated_data/ --model-type 'c' ${CUDA} --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs ${EPOCHS} --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_c/plain_results_$i_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS} ${MASK}
+                python train.py --data ./data/generated_data/ --model-type 'c' ${CUDA} --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs ${EPOCHS} --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_c/plain_results_$i_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS} ${MASK}
                 
 	    done
         fi

### 2020-01-20 project/evaluate.py
Error images for the simulations

@@ -450,6 +450,8 @@ class Evaluator:
 
         for i, index in enumerate(range(start_index, start_index + cnt), 1):
 
+            pred_output = self._prepare_tensor_img(input_img[0], is_input=True)
+            
             if self.parameterized:
                 t0 = time.time()
                 predicted = net((input_img, params))
@@ -463,6 +465,8 @@ class Evaluator:
                 for l,j in itertools.product(range(predicted.shape[0]), range(predicted.shape[1])):
                     predicted[l][j] = self.MASK * predicted[l][j]
 
+
+            
             if self.args.mask:
                 input_img = torch.cat((torch.tensor(predicted.clone().detach()[0][0:3]).expand(1,-1,-1,-1), self.MASK.expand(1,-1,-1,-1)), 1)
             else:
@@ -483,6 +487,28 @@ class Evaluator:
             if self.args.use_pressure:
                 save_img(predicted_p, 'p_step_{}'.format(i), '{}/p_step_{}.png'.format(path, i))
 
+
+            real_input = self._prepare_tensor_img(dataset[index][0], True)
+            real_output = self._prepare_tensor_img(dataset[index][1])
+
+            
+            
+
+            diff_x_real = np.abs(      real_output[0] - real_input[0])
+            diff_x_predicted = np.abs( pred_output[0] - predicted_x)
+
+            diff_y_predicted = np.abs( pred_output[1] - predicted_y)
+            diff_y_real = np.abs(      real_output[1] - real_input[1])
+
+            
+
+            merge_and_save(diff_x_real, diff_x_predicted,
+                           'Real difference_x {}'.format(i), 'Predicted difference_x {}'.format(i),
+                           os.path.join(path, 'diff_x_step_{}.png'.format(i)), txt_color=(255, 255,255,255))
+
+            merge_and_save(diff_y_real, diff_y_predicted,
+                           'Real difference_y {}'.format(i), 'Predicted difference_y {}'.format(i),
+                           os.path.join(path, 'diff_y_step_{}.png'.format(i)), txt_color=(255, 255,255,255))
             
 
         times = np.array(times)

### 2020-01-20 project/train.py

@@ -389,22 +389,22 @@ if args.evaluate:
     net_g.eval()
     with torch.no_grad():
 
-        print('===> Evaluating with test set:')
-        evaluator.set_output_name('test')
-        evaluator.individual_images_performance(net_g, test_loader)
-        exit(1)
-        evaluator.snapshots(net_g, test_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
+        # print('===> Evaluating with test set:')
+        # evaluator.set_output_name('test')
+        # evaluator.individual_images_performance(net_g, test_loader)
+        # evaluator.snapshots(net_g, test_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
 
-        print('===> Evaluating with train set:')
-        evaluator.set_output_name('train')
-        evaluator.snapshots(net_g, train_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
-        evaluator.individual_images_performance(net_g, train_loader)
+        # print('===> Evaluating with train set:')
+        # evaluator.set_output_name('train')
+        # evaluator.snapshots(net_g, train_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
+        # evaluator.individual_images_performance(net_g, train_loader)
 
         if args.model_type == 'c':
             print('===> Running simulations for c:')
 
             evaluator.set_output_name('simulations')
             evaluator.run_full_simulation(net_g, dataset, 20, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(20))
+            exit(1)
             evaluator.run_full_simulation(net_g, dataset, 100, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(100))
             evaluator.run_full_simulation(net_g, dataset, 200, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(200))
             evaluator.run_full_simulation(net_g, dataset, 300, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(300))

### 2020-01-20 project/utils.py

@@ -83,7 +83,7 @@ def correlation(img1, img2):
     return c
 
 
-def merge_and_save(img1, img2, text1, text2, dest, mode='L'):
+def merge_and_save(img1, img2, text1, text2, dest, mode='L', txt_color=(0,0,0,255)):
     image_1 = Image.fromarray(np.uint8(np.squeeze(img1)))
     image_2 = Image.fromarray(np.uint8(np.squeeze(img2)))
 
@@ -96,8 +96,8 @@ def merge_and_save(img1, img2, text1, text2, dest, mode='L'):
 
     draw = ImageDraw.Draw(new_im) 
     draw.line((0,height_1,width_1,height_2), fill=0, width=2)
-    draw.text((10,10), text1, (0,0,0), font=VERDANA_FONT)
-    draw.text((10,10 + height_1), text2, (0,0,0), font=VERDANA_FONT)
+    draw.text((10,10), text1,font=VERDANA_FONT, fill=txt_color)
+    draw.text((10,10 + height_1), text2, font=VERDANA_FONT, fill=txt_color)
     
     new_im.save(dest)
 

### 2020-01-20 project/evaluate.py
Error images for the  recursive eval

@@ -102,12 +102,19 @@ class Evaluator:
         diff_x = []
         diff_y = []
 
+        change_psnr_x = []
+        change_psnr_y = []
+        change_diff_x = []
+        change_diff_y = []
+        
         input_img = dataset[start_index][0].expand(1,-1,-1,-1).to(self.device)
 
         if self.parameterized:
             params = dataset[start_index][2].expand(1,-1,-1,-1).to(self.device)
 
         for index in range(start_index, end_index):
+
+            pred_input = self._prepare_tensor_img(input_img[0], is_input=True)
             
             if self.parameterized:
                 predicted = net((input_img, params))
@@ -161,6 +168,30 @@ class Evaluator:
             diff_y.append(imgs_perc_diff(target_img[0][1], predicted_img[0][1])[0])
 
 
+            real_input = self._prepare_tensor_img(dataset[index][0], True)
+
+            change_x_real = np.abs(      target_x - real_input[0])
+            change_x_predicted = np.abs( pred_input[0] - predicted_x)
+            change_y_real = np.abs(      target_y - real_input[1])
+            change_y_predicted = np.abs( pred_input[1] - predicted_y)
+            
+            change_mse_x = (np.square(change_x_real - change_x_predicted)).mean(axis=None)
+            change_mse_y = (np.square(change_y_real - change_y_predicted)).mean(axis=None)
+
+            change_psnr_x += [10.0 * np.log10(255.0 / np.sqrt(change_mse_x))]
+            change_psnr_y += [10.0 * np.log10(255.0 / np.sqrt(change_mse_y))]
+            change_diff_x += [imgs_perc_diff(change_x_real, change_x_predicted)[0]]
+            change_diff_y += [imgs_perc_diff(change_y_real, change_y_predicted)[0]]
+
+            merge_and_save(change_x_real, change_x_predicted,
+                           'Real', 'Predicted',
+                           os.path.join(path, 'x_diff_{}.png'.format(index - start_index)))
+
+            merge_and_save(change_y_real, change_y_predicted,
+                           'Real', 'Predicted',
+                           os.path.join(path, 'y_diff_{}.png'.format(index - start_index)))
+        
+
             print('> Recursive application {} completed'.format(index - start_index))
 
 
@@ -174,6 +205,12 @@ class Evaluator:
[…]

### 2020-01-20 project/train.py

@@ -389,22 +389,21 @@ if args.evaluate:
     net_g.eval()
     with torch.no_grad():
 
-        # print('===> Evaluating with test set:')
-        # evaluator.set_output_name('test')
-        # evaluator.individual_images_performance(net_g, test_loader)
-        # evaluator.snapshots(net_g, test_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
+        print('===> Evaluating with test set:')
+        evaluator.set_output_name('test')
+        evaluator.individual_images_performance(net_g, test_loader)
+        evaluator.snapshots(net_g, test_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
 
-        # print('===> Evaluating with train set:')
-        # evaluator.set_output_name('train')
-        # evaluator.snapshots(net_g, train_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
-        # evaluator.individual_images_performance(net_g, train_loader)
+        print('===> Evaluating with train set:')
+        evaluator.set_output_name('train')
+        evaluator.snapshots(net_g, train_sampler, dataset, samples=config['evaluation_snapshots_cnt'])
+        evaluator.individual_images_performance(net_g, train_loader)
 
         if args.model_type == 'c':
             print('===> Running simulations for c:')
 
             evaluator.set_output_name('simulations')
             evaluator.run_full_simulation(net_g, dataset, 20, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(20))
-            exit(1)
             evaluator.run_full_simulation(net_g, dataset, 100, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(100))
             evaluator.run_full_simulation(net_g, dataset, 200, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(200))
             evaluator.run_full_simulation(net_g, dataset, 300, config['full_simulaiton_samples'], sim_name = 'simulation_i{}'.format(300))
@@ -415,7 +414,7 @@ if args.evaluate:
 
             evaluator.set_output_name('recursive_i20')
             evaluator.recusive_application_performance(net_g, dataset, 20, samples=config['evaluation_recursive_samples'])
-
+            
             evaluator.set_output_name('recursive_i100')
             evaluator.recusive_application_performance(net_g, dataset, 20, samples=config['evaluation_recursive_samples'])
 

### 2020-01-23 project/eval_models.sh
Fixing a nasty bug

@@ -7,14 +7,27 @@ MODEL_DIRS="$@"
 for model_dir in ${MODEL_DIRS[@]}; do
 
     SEED=$(grep "seed" "${model_dir}/log.txt" | grep "[0-9]*" -o)
+    MASK_VAR=$(grep "mask" "${model_dir}/log.txt" | grep "True\|False" -o)
+    PRESSURE_VAR=$(grep "use_pressure" "${model_dir}/log.txt" | grep "True\|False" -o)
+
+    if [ $MASK_VAR == "True" ] ; then
+        $MASK_VAR=" "
+    else
+        $MASK_VAR="--no-mask"
+    fi
+
+    
+    if [ $PRESSURE_VAR == "True" ] ; then
+        $PRESSURE_VAR="--use-pressure"
+    else
+        $PRESSURE_VAR=" "
+    fi
 
     if [ $SEED ] ; then
 
-        # if [ ! -d ${model_dir}/test ] ; then
-
         echo "Evaluating ${model_dir}"
 
-        echo python train.py --data ./data/generated_data/ --model-type 'c' --model-name "unet" --threads 4 --batch-size 3 --shuffle --epochs 50 --lr_policy step --seed $SEED --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "${model_dir}_new" --evaluate --use-pressure  --no-train --model-path ${model_dir}/c_unet_*/* --no-mask
+        echo python train.py --data ./data/generated_data/ --model-type 'c' --model-name "unet" --threads 4 --batch-size 3 --shuffle --epochs 50 --lr_policy step --seed ${SEED} --test-train-split 0.8 --val-train-split 0.1 --output-dir "${model_dir}_new" --evaluate ${PRESSURE_VAR}  --no-train --model-path ${model_dir}/c_unet_*/*_epoch_45.pth ${MASK_VAR}
         exit
         
         # fi        
@@ -23,6 +36,3 @@ for model_dir in ${MODEL_DIRS[@]}; do
     fi
     
 done
-
-
-python train.py --data ./data/generated_data/ --model-type 'c' --model-name "unet" --threads 4 --batch-size 3 --shuffle --epochs 50 --lr_policy step --seed $RANDOM --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir results_c/res_1 --evaluate --use-pressure --no-train --no-mask

### 2020-01-23 project/evaluate.py

@@ -212,7 +212,6 @@ class Evaluator:
             list_hand.write('{} {}\n'.format('change_diff_y: ',  ','.join(str(i) for i in change_diff_y )))
             
 
-
     def individual_images_performance(self, net, test_dataloader):
         print('===> Evaluating performance on individual images')
 
@@ -279,7 +278,7 @@ class Evaluator:
             
             for ind in range(real_a.shape[0]):
 
-                real_change_img = np.abs(real_a[ind] - real_b[ind])
+                real_change_img = np.abs(real_a[ind][0:3] - real_b[ind])
                 predicted_change_img = np.abs(predicted[ind] - real_b[ind])
                 cur_mse = (np.square(real_change_img - predicted_change_img)).mean(axis=None)
                 cur_psnr = 10 * np.log10(255.0 / np.sqrt(cur_mse))
@@ -472,7 +471,7 @@ class Evaluator:
                                os.path.join(config['output_dir'], self.output_name, 'snapshots', 'p_timestep_{}_{}.png'.format(index, random.randint(0, 10000))))
 
 
-    def run_full_simulation(self, net, dataset, start_index, cnt, sim_name='simulation'):
+    def run_full_simulation(self, net, dataset, start_index, cnt, sim_name='simulation', saving_imgs=False):
         print('===> Running simulation with the generator network')
 
         path = os.path.join(self.path_full_sim, sim_name)

### 2020-01-23 project/plots/timings.py

@@ -14,12 +14,13 @@ def main():
     
     predic_single_timings = [1681,1534,1485,1582,1407,1384,1384,1430,1392,1480,1530,1535,1500,1536,1480,1409,1425,1401,1381,1403,1385,1383,1379,1372,1373,1380,1377,1367,1372,1392,1378,1393,1561,1562,1479,1368,1371,1372,1379,1377,1365,1378,1373,1367,1386,1378,1378,1373,1379,1379,1375,1372,1375,1378,1401,1401,1423,1449,1395,1393,1385,1379,1378,1372,1378,1368,1373,1378,1376,1372,1378,1379,1378,1388,1383,1372,1380,1371,1372,1384,1380,1381,1392,1382,1380,1391,1367,1405,1391,1356,1377,1373,1408,1382,1375,1383,1372,1381,1376,1387,1380,1392,1389,1375,1377,1382,1369,1377,1368,1381,1384,1382,1451,1433,1378,1372,1410,1388,1366,1377,1380,1380,1373,1366,1394,1378,1379,1379,1383,1378,1453,1538,1497,1375,1361,1376,1390,1377,1381,1358,1353,1366,1380,1379,1499,1554,1530,1374,1363,1377,1376,1357,1378,1379,1374,1381,1371,1376,1376,1390,1384,1378,1377,1357,1378,1371,1364,1395,1383,1374,1379,1371,1381,1411,1375,1392,1479,1509,1499,1383,1395,1396,1362,1362,1362,1372,1390,1381,1378,1371,1365,1373,1359,1373,1378,1377,1372,1372,1379,1378,1378,1374,1381,1384,1378,1371,1392,1399,1379,1376,1378,1379,1379,1374,1379,1374,1390,1410,1395,1357,1377,1376,1384,1371,1415,1391,1378,1377,1372,1379,1386,1369,1368,1357,1371,1378,1368,1376,1378,1495,1506,1380,1372,1364,1377,1358,1388,1377,1380,1375,1419,1527,1523,1478,1372,1393,1372,1376,1378,1378,1425,1378,1373,1379,1378,1378,1372,1378,1376,1373,1372,1373,1385,1376,1361,1498,1434,1370,1371,1362,1375,1375,1357,1376,1371,1368,1378,1362,1381,1370,1377,1377,1379,1380,1394,1384,1451,1414,1375,1371,1616,1414,1449,1417,1421,1419,1382,1481,1425,1432,1419,1
[…]

### 2020-02-18 paper/eccv2020submission.tex
Adding the paper

\documentclass{llncs}
\usepackage[pagebackref]{hyperref}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{color}

\newcommand{\reffig}[1]{\hyperref[#1]{Figure \ref*{#1}}}
\newcommand{\refsec}[1]{\hyperref[#1]{Section \ref*{#1}}}
\newcommand{\reftab}[1]{\hyperref[#1]{Table \ref*{#1}}}
\newcommand{\refapp}[1]{\hyperref[#1]{Appendix \ref*{#1}}}

% INITIAL SUBMISSION - The following two lines are NOT commented
% CAMERA READY - Comment OUT the following two lines
% \usepackage{ruler}
% \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCVSubNumber{100}  % Insert your submission number here

\title{Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks} % Replace with your title

% INITIAL SUBMISSION 
\begin{comment}
\titlerunning{Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks} 
\authorrunning{Stanislav Arnaudov, Markus Hoffmann} 
\author{Stanislav Arnaudov, Markus Hoffmann}
\institute{Karlsruhe Institute of Technology,\\Kaiserstrasse 12,76131 Karlsruhe, Germany\\ \url{http://www.kit.edu/english/}}
\end{comment}
%******************

% CAMERA READY SUBMISSION
% \begin{comment}
\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Stanislav Arnaudoc, Markus Hoffmann }
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Karlsruhe Institute of Technology,\\Kaiserstrasse 12,76131 Karlsruhe, Germany\\ \url{http://www.kit.edu/english/}}
% \end{comment}
%******************
\maketitle

\begin{abstract}
A central problem in the field of Computational Fluid Dynamics (CFD) is to efficiently perform a simulation of fluid flow while keeping the processing time low. Classical methods that provide accurate results, work based on partial differential equation solvers. They, however, require a considerable amount of processing time which is a problem when there are different simulation-parameter sets. We propose an alternative method for performing a simulation of fluid flow around an object based on convolutional neural networks (CNNs). We investigate a novel approach that uses simulation images as input for the CNN.\@ Several models are built, each trying to generalize a different subset of the parameters of the simulation. All models are based on the U-Net architecture and generate an image for the next time-step of the simulation. On average, the models perform an order of magnitude faster than the classical solvers at the cost of reduced accuracy. The generated images, however, are close enough to the real ones, so that a human observer can perceive them as the same. We also evaluate the results with appropriate error metrics.
\keywords{Computational Fluid Dynamics, Convolutional Neural Networks, U-Net, Image processing}
\end{abstract}

\section{Introduction}\label{introduction}
Computational Fluid Dynamics (CFD) is a field that deals with performing simulations of fluid flows. The task usually consists of setting certain initial conditions in a defined space and solving a large mathematical problem for each timestep of the simulation. Two central points of interest in CFD is the processing time needed for a simulation as well as the accuracy of the results. It is clear that low processing time and high accuracy are desired but often e certain trade off has to be made. With our research we want to propose an innovative method for quickly inspecting the results of a simulation while keeping the accuracy high enough for them to make sense.

We've concentrated our study on 2D simulations of a incompressible fluid flow around an object in a channel according to the Navier-Stokes equations. This setup has three adjustable parameters --- the inflow speed, the viscosity and the density of the fluid. The solutions of the simulation are three separate fields over the input space --- two velocity fields in x and y directions and a pressure field. These can be conveniently visualized as images over the input space. We are mainly interested in those image representations of the timeteps of the simulation.

Classical methods for performing such simulations are based on partial differential equations (PDEs) solvers. The simulation setup is first formalized and a mathematical model in form of a time dependent differential equation is given. In itself this equation is then transformed and brought into a suitable form. A common technique is the finite difference method (FDM). This can provide accurate results at the cost of large computational time. The generated results are in form of raw numbers representing the velocities and pressure fields which has to be visualized separately. Our method aims to generate straight the visualizations while needing much lower computational time.

In recent years there has been a large interest in neural networks and their capabilities. Convolutional Neural Networks (CNNs) in particular have been successfully applied in a wide variety of contexts and having proven to be a valuable tools. On of the major fields where the performance of CNNs is recognized is image processing. A lot of research has shown how CNNs can achieve state-of-the-art performance in tasks like image classification, image segmentation of image-to-image mapping. With our research we try to tie CFD and CNNs together and show how image processing approaches can be applied to performing numerical simulations.

In our research we want to investigate how a CNN can be used in order generate an image of the simulation in interest. We build models that take an image from the previous timestep as an input and transform it into an image for the next timestep. The built CNNs can also take certain parameters of the simulation and transform the image in accordance with these parameters. With this approach we are trying to transform the numerical task of calculating a timestep of a simulation into an image processing task.

The goal of our research is to see to what extend the described approach is viable. We achieve that by investigating how a CNN generalizes the different parameters of the investigated simulation. Two subsets of the parameters are defined --- fluid parameters (viscosity and density) and inflow speed of the fluid. For each of these two subsets we train a separate model and evaluate its performance in different use cases. A baseline model that does not take parameters into account is also built. We give more details on the models in section \refsec{methodology}.

The built models are evaluated from two points of view. Firstly, as the output of the network is meant for a human observer, we evaluate the generated images based on their perceived fidelity. Secondly, as the networks tries to model a numerical task, we also compare the real and generated images in a objective manner by measuring the actual differences between them.

Because of the nature of our task, two evaluation cases are given. On the one side, we want to see how the networks perform while predicting individual images. That is, a network performs a single simulation timestep and the results of that are evaluated. On the other side, we also want to see how the inaccuracies in the predicted images can accumulate over time. Hence also evaluate the models by recursive application where the output of the network is used again as an input for certain amount of timesteps.

Lastly, we briefly want to motivate why we propose exactly this approach.

\section{Related Work}\label{related_work}

\section{Methodology}\label{methodology}

The models were trained with real simulation data. We first descibe the process of generating said data, then we give details on the training procedure and the architecture of the models. We then descibe the three types of models that we build and evaluated.

\subsection{Simulation Setup}
\begin{itemize}
\item first describe the simulation setup in details
\item initial conditions and boundary conditions --- inflow condition, no slip conditions, outflow condition
\item schematic of the channel with the object in it
\item the simulations were preformed by a FEM solver --- HiFlow. The final images were rendered by ParaView. The images were cropped in order to contain only the relevant region of the simulation.
\item Gray scale images because [\ldots]
\item Example images
\item The parameters of the simulation were appropriately chosen. Argumentation with the Reynold's number. We want interesting effects but not a turbulent flow.
\item Simulations according to the Navier-Stokes equations are appropriate only if the flow is laminar. 
\item Concrete parameter numbers [\ldots]
\item Details on how HiFlow runs the simulation --- method, parameters, timestep time.
\end{itemize}

\subsection{Networks Details}

\subsection{Model types}

\subsection{Evaluation}

\section{Results}\label{results}

\section{Conclusion}\label{conclusion}

\clearpage
\bibliographystyle{splncs04}
\bibliography{egbib}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

% LocalWords:  Convolutional timestep timesteps

### 2020-02-18 project/eval_models.sh
Fixing things here and there

@@ -2,8 +2,6 @@
 
 MODEL_DIRS="$@"
 
-
-
 for model_dir in ${MODEL_DIRS[@]}; do
 
     SEED=$(grep "seed" "${model_dir}/log.txt" | grep "[0-9]*" -o)
@@ -16,7 +14,6 @@ for model_dir in ${MODEL_DIRS[@]}; do
         $MASK_VAR="--no-mask"
     fi
 
-    
     if [ $PRESSURE_VAR == "True" ] ; then
         $PRESSURE_VAR="--use-pressure"
     else
@@ -25,9 +22,11 @@ for model_dir in ${MODEL_DIRS[@]}; do
 
     if [ $SEED ] ; then
 
+        CHECKPOINT=$(ls ${model_dir}/c_unet_*/ | sort -r | head -n1)
+
         echo "Evaluating ${model_dir}"
 
-        python train.py --data ./data/generated_data/ --model-type 'c' --model-name "unet" --threads 4 --batch-size 3 --shuffle --epochs 50 --lr_policy step --seed ${SEED} --test-train-split 0.8 --val-train-split 0.1 --output-dir "${model_dir}_new" --evaluate ${PRESSURE_VAR}  --no-train --model-path ${model_dir}/c_unet_*/*_epoch_45.pth ${MASK_VAR}
+        python train.py --data ./data/generated_data/ --model-type 'c' --model-name "unet" --threads 4 --batch-size 3 --shuffle --seed ${SEED} --test-train-split 0.8 --val-train-split 0.1 --output-dir "${model_dir}_new" --evaluate ${PRESSURE_VAR}  --no-train --model-path "${model_dir}/${CHECKPOINT}"  ${MASK_VAR}
         
 
     fi

### 2020-02-18 project/evaluate.py

@@ -476,7 +476,7 @@ class Evaluator:
                                os.path.join(config['output_dir'], self.output_name, 'snapshots', 'p_timestep_{}_{}.png'.format(index, random.randint(0, 10000))))
 
 
-    def run_full_simulation(self, net, dataset, start_index, cnt, sim_name='simulation', saving_imgs=False):
+    def run_full_simulation(self, net, dataset, start_index, cnt, sim_name='simulation', saving_imgs=True):
         print('===> Running simulation with the generator network')
 
         path = os.path.join(self.path_full_sim, sim_name)
@@ -522,12 +522,13 @@ class Evaluator:
                 predicted_x, predicted_y, predicted_p = self._prepare_tensor_img(predicted[0])
 
 
-            
-            save_img(predicted_x, 'x_step_{}'.format(i), '{}/x_step_{}.png'.format(path, i))
-            save_img(predicted_y, 'y_step_{}'.format(i), '{}/y_step_{}.png'.format(path, i))        
 
-            if self.args.use_pressure:
-                save_img(predicted_p, 'p_step_{}'.format(i), '{}/p_step_{}.png'.format(path, i))
+            if saving_imgs:
+                save_img(predicted_x, 'x_step_{}'.format(i), '{}/x_step_{}.png'.format(path, i))
+                save_img(predicted_y, 'y_step_{}'.format(i), '{}/y_step_{}.png'.format(path, i))        
+
+                if self.args.use_pressure:
+                    save_img(predicted_p, 'p_step_{}'.format(i), '{}/p_step_{}.png'.format(path, i))
 
 
             real_input = self._prepare_tensor_img(dataset[index][0], True)
@@ -541,14 +542,14 @@ class Evaluator:
             diff_y_predicted = np.abs( pred_output[1] - predicted_y)
 
             
+            if saving_imgs:
+                merge_and_save(diff_x_real, diff_x_predicted,
+                               'Real difference_x {}'.format(i), 'Predicted difference_x {}'.format(i),
+                               os.path.join(path, 'diff_x_step_{}.png'.format(i)), txt_color=(255, 255,255,255))
 
-            merge_and_save(diff_x_real, diff_x_predicted,
-                           'Real difference_x {}'.format(i), 'Predicted difference_x {}'.format(i),
-                           os.path.join(path, 'diff_x_step_{}.png'.format(i)), txt_color=(255, 255,255,255))
-
-            merge_and_save(diff_y_real, diff_y_predicted,
[…]

### 2020-02-18 project/models.py

@@ -81,12 +81,14 @@ def define_G(input_nc, output_nc, ngf, norm='batch', use_dropout=True, init_gain
         else:
             raise Exception("Unknowns model: {}:".format(args.model_name))
 
+        net.device = gpu_id
         return init_net(net, init_gain, gpu_id=gpu_id)
 
 
 def define_D(input_nc, ndf, n_layers_D=3, norm='batch', use_sigmoid=False, init_gain=0.02, gpu_id='cuda:0'):
     norm_layer = get_norm_layer(norm_type=norm)
     net = NLayerDiscriminator(input_nc, ndf=ndf, n_layers=n_layers_D, norm_layer=norm_layer, use_sigmoid=use_sigmoid)
+    net.device = gpu_id
     return init_net(net, init_gain, gpu_id=gpu_id)
 
 
@@ -342,7 +344,7 @@ class UnetGenerator(nn.Module):
                 for j in range(params.size(3)):
                     t.append(torch.ones(1, 1, input.shape[2], input.shape[3]) * params[i][0][0][j])                    
                 tens.append(torch.torch.cat(t, 1))
-            input = torch.cat((torch.torch.cat(tens, 0).to('cuda'), input), 1).to('cuda')
+            input = torch.cat((torch.torch.cat(tens, 0).to(self.device), input), 1).to(self.device)
 
 
         return self.model(input)

### 2020-02-18 project/plotter.py

@@ -194,8 +194,8 @@ def plot_model_comparision(metric, labels, test_metr, test_metr_p, train_metr, t
 
   # plt.subplot(2,1,1)
   plt.title("Test")
-  plt.barh(r1, test_metr[0], barWidth, edgecolor='black', label='Without pressure', alpha=0.5 )
-  plt.barh(r2, test_metr_p[0], barWidth, edgecolor='black', label='With pressure' , alpha=0.5)
+  plt.barh(r1, test_metr[0], barWidth, edgecolor='black', label='Without pressure', alpha=0.5, xerr=test_metr[1] )
+  plt.barh(r2, test_metr_p[0], barWidth, edgecolor='black', label='With pressure' , alpha=0.5, xerr=test_metr_p[1])
   plt.grid(b=True, which='major', color='#999999', linestyle='-', alpha=0.2)
   plt.minorticks_on()
   plt.grid(b=True, which='minor', color='#999999', linestyle='-', alpha=0.2)
@@ -214,8 +214,8 @@ def plot_model_comparision(metric, labels, test_metr, test_metr_p, train_metr, t
   # plt.minorticks_on()
   # plt.grid(b=True, which='minor', color='#999999', linestyle='-', alpha=0.2)
 
-  # plt.xlabel(metric.upper(), fontweight='bold')
-  # plt.ylabel('Model', fontweight='bold')
+  plt.xlabel(metric.upper(), fontweight='bold')
+  plt.ylabel('Model', fontweight='bold')
 
   # plt.yticks([r + barWidth - spacing/2 for r in range(len(train_metr[0]))], labels)
 
@@ -328,14 +328,14 @@ class PlotProcessor():
         for mod in self.get_model_dirs():
 
           model_name = self.get_model_name(mod)
-          met = hel_d.setdefault(rchop(model_name, '_p'), {})
+          met = hel_d.setdefault(model_name.replace('_p', ''), {})
 
           met.setdefault('train_with_p', [])
           met.setdefault('train_without_p', [])
           met.setdefault('test_with_p', [])
           met.setdefault('test_without_p', [])
-          
-          if model_name.endswith('_p'):
+
+          if '_p' in model_name:
             met['test_with_p'].append(self.get_model_metric(mod, metric=metric, test=True))
             met['train_with_p'].append(self.get_model_metric(mod, metric=metric, test=False))
           else:
@@ -507,9 +507,9 @@ def main():
 
     # plotter.val_losses()
[…]

### 2020-02-18 project/train.py

@@ -58,9 +58,10 @@ def get_dataconf_file(args):
     return args.model_type + '_dataconf.txt'
 
 
-def test_validation_test_split(dataset, test_train_split=0.8, val_train_split=0.1, shuffle=False, model_type = 'c'):
+def test_validation_test_split(dataset, test_train_split=0.8, val_train_split=0.1, shuffle=False, model = 'c'):
 
-    if model_type is 'c':
+    if model == 'c':
+        print('Splitting for c')
         dataset_size = len(dataset)
         indices = list(range(dataset_size))
         test_split = int(np.floor(test_train_split * dataset_size))
@@ -72,7 +73,8 @@ def test_validation_test_split(dataset, test_train_split=0.8, val_train_split=0.
         train_indices, val_indices = train_indices[ : validation_split], train_indices[validation_split:]
         return train_indices, val_indices, test_indices
 
-    if model_type is 's':
+    if model == 's':
+        print('Splitting for s')
         dataset_size = len(dataset)
         indices = list(range(dataset_size))
         
@@ -85,7 +87,8 @@ def test_validation_test_split(dataset, test_train_split=0.8, val_train_split=0.
         train_indices, val_indices = train_indices[ : validation_split], train_indices[validation_split:]
         return train_indices, val_indices, test_indices
 
-    if model_type is 'vd':
+    if model == 'vd':
+        print('Splitting for vd')
         dataset_size = len(dataset)
         indices = list(range(dataset_size))
         
@@ -97,7 +100,6 @@ def test_validation_test_split(dataset, test_train_split=0.8, val_train_split=0.
         validation_split = int(np.floor((1 - val_train_split) * train_size))
         train_indices, val_indices = train_indices[ : validation_split], train_indices[validation_split:]
         return train_indices, val_indices, test_indices
-        
 
 
 def save_models(net_g, net_d, args, epoch):
@@ -239,10 +241,11 @@ print('===> Loading datasets')
 dataconf_file = get_dataconf_file(args)
 dataset = SimulationDataSet(args.data_dir, dataconf_file, args)
 
-train_indices, val_indices, test_indices = test_validation_test_split(dataset, shuffle=shuffle_dataset,
+train_indices, val_indices, test_indices = test_validation_test_split(dataset,
                                                                       test_train_split=args.test_train_split,
                                                                       val_train_split=args.val_train_split,
[…]

### 2020-02-18 project/train_models.sh

@@ -142,11 +142,13 @@ do
 	    done
         fi
 
-	for i in $(seq 1 ${MODEL_CNT}); do
+        if [ ! -z "$NO_PRESSURE" ]; then
+	    for i in $(seq 1 ${MODEL_CNT}); do
 
-	    python train.py --data ./data/generated_data/ --model-type 's' ${CUDA} --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs ${EPOCHS} --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_s/plain_results_${i}_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS} ${MASK}
+	        python train.py --data ./data/generated_data/ --model-type 's' ${CUDA} --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs ${EPOCHS} --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_s/plain_results_${i}_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS} ${MASK}
 
-	done
+	    done
+        fi
     fi
 
     #################################################################
@@ -172,11 +174,13 @@ do
 	    done
 	fi
 
-	for i in $(seq 1 ${MODEL_CNT}); do
+        if [ ! -z "$NO_PRESSURE" ]; then
+	    for i in $(seq 1 ${MODEL_CNT}); do
 
-	    python train.py --data ./data/generated_data/ --model-type 'vd' ${CUDA} --model-name "${net}" --threads 4 --batch-size 3 --shuffle --epochs ${EPOCHS} --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_vd/plain_results_$i_${RANDOM}/" --evaluate --g_nfg ${NGF} --g_layers ${LAYERS}  ${MASK}
[…]

### 2020-02-18 project/train_multi_gpu.sh

@@ -16,20 +16,17 @@ module load devel/cuda/10.1
 echo "Job ID: " ${SLURM_JOB_ID}
 
 
-MASK=" "          EPOCHS=40 CUDA_VISIBLE_DEVICES=0 ./train_models.sh --unet -c -n 32 -l 5 -p -np -m 2 &
-MASK=" "          EPOCHS=40 CUDA_VISIBLE_DEVICES=1 ./train_models.sh --unet -c -n 32 -l 5 -p -np -m 2 & 
-MASK=" "          EPOCHS=40 CUDA_VISIBLE_DEVICES=1 ./train_models.sh --unet -c -n 32 -l 5 -p -np -m 2 &
-MASK=" "          EPOCHS=40 CUDA_VISIBLE_DEVICES=1 ./train_models.sh --unet -c -n 32 -l 5 -p -np -m 2
+# MASK=" "          EPOCHS=40 CUDA_VISIBLE_DEVICES=0 ./train_models.sh --unet -c -n 32 -l 5 -p -np -m 2 &
+# MASK=" "          EPOCHS=40 CUDA_VISIBLE_DEVICES=1 ./train_models.sh --unet -c -n 32 -l 5 -p -np -m 2 & 
+# MASK=" "          EPOCHS=40 CUDA_VISIBLE_DEVICES=1 ./train_models.sh --unet -c -n 32 -l 5 -p -np -m 2 &
+# MASK=" "          EPOCHS=40 CUDA_VISIBLE_DEVICES=1 ./train_models.sh --unet -c -n 32 -l 5 -p -np -m 2
 
 # MASK="--no-mask"  EPOCHS=40 CUDA_VISIBLE_DEVICES=2 ./train_models.sh --unet -c -n 32 -l 5 -p -np -m 2 &
 # MASK="--no-mask"  EPOCHS=40 CUDA_VISIBLE_DEVICES=3 ./train_models.sh --unet -c -n 32 -l 5 -p -np -m 2
-
-
 # MASK="--no-mask"  EPOCHS=45 CUDA_VISIBLE_DEVICES=2 ./train_models.sh --unet -c -n 32 -l 5 -p -np -m 5 & 
 # MASK="--no-mask"  EPOCHS=45 CUDA_VISIBLE_DEVICES=3 ./train_models.sh --unet -c -n 32 -l 5 -p -np -m 5
 
-
[…]

### 2020-02-18 project/eval_multi_gpu.sh
Adding the multi eval

@@ -1,0 +1,22 @@
+#!/bin/bash
+#SBATCH --ntasks=1
+#SBATCH --nodes=1
+#SBATCH --cpus-per-task=8
+#SBATCH --time=24:00:00
+#SBATCH --mem=16gb
+#SBATCH --partition=visu
+#SBATCH --output=speed_model
+
+cd $(ws_find arnaud)
+. setenv.sh
+cd code/flow_pred/
+
+module load devel/cuda/10.1
+
+echo "Job ID: " ${SLURM_JOB_ID}
+
+CUDA_VISIBLE_DEVICES=0 ./eval_models.sh results_c/* &
+
+CUDA_VISIBLE_DEVICES=1 ./eval_models.sh results_s/* & 
+
+CUDA_VISIBLE_DEVICES=2 ./eval_models.sh results_vd/*

### 2020-03-03 paper/eccv2020submission.tex
Writing out a part of the methodology section of the paper

@@
 
-The models were trained with real simulation data.
-We first descibe the process of generating said data, then we give details on the training procedure and the architecture of the models.
-We then descibe the three types of models that we build and evaluated.
+\emph{The models were trained with real simulation data.
+We first describe the process of generating said data, then we give details on the training procedure and the architecture of the models.
+We then descibe the three types of models that we build and evaluated.}
 
 \subsection{Simulation Setup}
+The training data was generated by performing numerous simulations of an incompressible fluid flow around a rectangular object in a channel.
+The simulations were modeled according to the Navier-Stokes equations for incompressible flow.
+Because we are interested in the image representations of the simulations, we are dealing only with the 2D case.
+There are several boundary conditions that describe the simulation setup:
 \begin{itemize}
-\item first describe the simulation setup in details
-\item initial conditions and boundary conditions --- inflow condition, no slip conditions, outflow condition
-\item schematic of the channel with the object in it
-\item the simulations were preformed by a FEM solver --- HiFlow. The final images were rendered by ParaView. The images were cropped in order to contain only the relevant region of the simulation.
-\item Gray scale images because [\ldots]
-\item Example images
-\item The parameters of the simulation were appropriately chosen. Argumentation with the Reynold's number. We want interesting effects but not a turbulent flow.
-\item Simulations according to the Navier-Stokes equations are appropriate only if the flow is laminar. 
-\item Concrete parameter numbers [\ldots]
-\item Details on how HiFlow runs the simulation --- method, parameters, timestep time.
+\item Inflow condition on the left side of the channel
+\item Outflow condition on the right side of the channel
+\item No slip condition on bottom and top side of the channel as well as the sides of the object.
+\end{itemize}
+The simulation setup has three separate adjustable parameters --- inflow speed, fluid density and fluid viscosity.
+\\
+We generated three sets of simulations for training the three kinds of models.
+\begin{itemize}
+\item plain: a single simulation with \ldots.
+\item varying inflow speed: \ldots simulations with different inflow speed. The inflow speeds are in the range of \ldots with a step of \ldots.
+\item varying viscosity and density of the fluid: \ldots simulations all with different fluid viscosity and density.
+The viscosity was in the range of \ldots with a step of \ldots and the density was in the range of \ldots with a step of \ldots.
+We used the product of the two parameter ranges to perform simulations with all of the possible combinations between the two parameters.
 \end{itemize}
 
-\subsection{Networks Details}
+The choice of the concrete values for the parameters was deliberate.
+All of the values are chosen so that the Reynolds number of the simulations in the range of \ldots.
+This keeps the flow laminar while still making it interesting enough.
+We were interested whether the built models can predict the emerging Kármán vortex street behind the object in the channel.
+Thus the Reynolds numbers were chosen so that the effect can occur.
+
+The simulations were performed numerically by solving the differential equation describing the flow --- the Navier-Stokes equation.
+This was done with a numerical solver --- HiFlow ---  that works on base of Finite element method.
+The solver supports parallelization with MPI and OpenMP and we used 12 MPI processes to run each simulation.
+For all of the simulations the timestep for of solver was set to $0.035$ seconds.
+This means the a single timestep of the simulations corresponds to a $0.035$ seconds of physical time.
+
+The numerical solver on itself cannot be used to render the simulation results to images.
+For this reason we used ParaView to load the simulation data and exported it as a sequence of images in PNG format.
+We opted out for using grayscale images as early experiments with RGB-images did not deliver satisfying results.
+We used the default ``Grayscale'' color preset of ParaView to visualize the results.
+
+\subsection{Network Details}
+\emph{In this subsection we turn our attention to the details around the architecture of the used network.}
+
+The architecture of the used network and the training approach are entirely based on pix2pix.
 
@@
 
-% LocalWords:  Convolutional timestep timesteps
+% LocalWords:  Convolutional timestep timesteps grayscale

### 2020-03-04 paper/eccv2020submission.tex
Adding some sentences to the paper.

@@
 
-\subsection{Network Details}
+The images are finally cropped.
+
+\subsection{Network and Training Details}
 \emph{In this subsection we turn our attention to the details around the architecture of the used network.}
 
-The architecture of the used network and the training approach are entirely based on pix2pix.
+Our task is an image generation task we used the conditional GAN method introduced in pix2pix.
+
+Some of the experiments in pix2pix suggest that keeping the noise vector can be reasonable but we decided to use only a single multichannel image as an input for the generator network.
+
+The generator is trained to produced the next frame of the simulation based on the previous one.
+A single frame contains the two velocity fields as well as optional pressure field.
+We experimented with using and leaving out the pressure field.
+
+Some of the models, however, also take some simulation parameters into account.
+For those models, the generator also receives one or two constant channels with a value equal to the value of the parameter.
+
+The training approach is almost entirely based on pix2pix.
+We used the conditional GAN (Generative adversarial network) method to build a minimal image translation framework.
+In contrast to classical GANs, conditional GANs present both the original and the generated image to the discriminator network.
+The discriminator network is also used as part of the loss function for the generator network.
+
+In our case, the generator network is presented a single timestep of the simulation in an image form.
+For the inflow-speed and fluid viscosity-density models the corresponding parameters of the simulation are also given to the network.
+The parameters are represented as separate constant channels with a value equal to the one of the parameter.
 

### 2020-03-05 paper/eccv2020submission.tex
Doing some good work on the paper

--- 2020-03-03 paper/eccv2020submission.tex
@@
 
+Our contributions are \ldots.
+
 \section{Related Work}\label{related_work}
@@
 \section{Methodology}\label{methodology}
-
-\emph{The models were trained with real simulation data.
+% \emph{The models were trained with real simulation data.
 We first describe the process of generating said data, then we give details on the training procedure and the architecture of the models.
@@
 
-\subsection{Simulation Setup}
+The task is to build a network that can predict the next frame of the simulation based on the previous one.
+Each frame represents a timestep of the simulation and consists of a three channel image.
+Two of the channels encode the velocity fields in both directions and the third channel is the pressure field of the fluid.
+We were interested in how the usage of the pressure field affects the performance of the built models.
+Therefore, for each model be trained two variants --- one that uses the pressure field and one that does not.
+
+We did not construct a single holistic model that can handle all of the simulation's parameters.
+Our efforts were concentrated on building a couple of smaller ones that take into account subsets of the parameters.
+The studied models are:
+\begin{itemize}
+\item A Constant model --- does not take into any of the parameters and it is trained with data from a single simulation.
+It is conceived as a baseline and proof of concept model that is there to show how a neural network can learn to generate simulation timesteps in from of images.
+\item A fluid inflow speed model --- the model receives the inflow speed of the fluid as an extra input. It is trained with data from several simulations with different inflow speeds.
+\item A viscosity and density model --- the model receives the viscosity and density of the fluid as extra inputs.
+\end{itemize}
+By evaluating each models we want to see how a network can generalize each of the parameter subsets and to what extent
+
+To study the performance of conditional GANs on generating frames of the concrete simulation we generated the training data ourselves. In what follows we give details about the process.
+
+\subsection{Simulation Setup and Data generation}
 The training data was generated by performing numerous simulations of an incompressible fluid flow around a rectangular object in a channel.
@@
 The simulations were performed numerically by solving the differential equation describing the flow --- the Navier-Stokes equation.
-This was done with a numerical solver --- HiFlow ---  that works on base of Finite element method.
+This was done with a numerical solver library --- HiFlow ---  that works on the base of Finite element method.
 The solver supports parallelization with MPI and OpenMP and we used 12 MPI processes to run each simulation.
@@
 We used the default ``Grayscale'' color preset of ParaView to visualize the results.
+Each frame of the simulation was exported as three separate grayscale images.
+The images were finally cropped to select a subset of the space that contains the object and the space behind it.
 
-\subsection{Network Details}
+\subsection{Training approach and networks details}
 \emph{In this subsection we turn our attention to the details around the architecture of the used network.}
 
-The architecture of the used network and the training approach are entirely based on pix2pix.
+We base our generative models almost entirely on pix2pix.
+We use the conditional GAN approach to train a generator network that can perform image-to-image translation.
+As explained in [], the traditional GAN method uses a random vector $z$ as in input to the generator network $G$ to generate output $y$, $G:z \rightarrow y$.
+Conditional GANs also feed an input image $x$ to the generator, $G: x,z \rightarrow y$.
+Pix2Pix suggests that in certain cases the usage of $z$ can be usefully but we decided not to include for out generator as we want a deterministic network.
+
+We adopt the objective for the discriminator network as we modify it slightly by leaving out the random vector $z$.
+\begin{equation}
+\mathcal{L}_{cGAN} (G, D) = (\mathbb{E}[\log D (x,y)] + \mathbb{E}[\log D (x, G(x))])/2
+\end{equation}
+where $x$ is the input image and $y$ is the target image.
+In contrast to unconditional GANs, both the generator and the discriminator network have access to the input image.
+The objective is divided by 2 to slow down the training of the discriminator relative to the generator as suggested by [].
+
+The objective for the generator network is comprised of two parts --- the value of the discriminator as well as
+
+% In contrast to pix2pix we also disable the dropout and batch normalization layers during testing.
+
+% Our task is an image generation task we used the conditional GAN method introduced in pix2pix.
+
+% Some of the experiments in pix2pix suggest that keeping the noise vector can be reasonable but we decided to use only a single multichannel image as an input for the generator network.
+
+% The generator is trained to produced the next frame of the simulation based on the previous one.
+A single frame contains the two velocity fields as well as optional pressure field.
+We experimented with using and leaving out the pressure field.
+
+% Some of the models, however, also take some simulation parameters into account.
+For those models, the generator also receives one or two constant channels with a value equal to the value of the parameter.
+
+% The training approach is almost entirely based on pix2pix.
+We used the conditional GAN (Generative adversarial network) method to build a minimal image translation framework.
+In contrast to classical GANs, conditional GANs present both the original and the generated image to the discriminator network.
+The discriminator network is also used as part of the loss function for the generator network.
+
+% In our case, the generator network is presented a single timestep of the simulation in an image form.
+For the inflow-speed and fluid viscosity-density models the corresponding parameters of the simulation are also given to the network.
+The parameters are represented as separate constant channels with a value equal to the one of the parameter.
 

### 2020-03-05 paper/eccv2020submission.tex
Doing some more work on the paper

@@
 \newcommand{\refapp}[1]{\hyperref[#1]{Appendix \ref*{#1}}}
+\DeclareMathOperator*{\argminA}{arg\,min} % Jan Hlavacek
 
@@
 \subsection{Training approach and networks details}
-\emph{In this subsection we turn our attention to the details around the architecture of the used network.}
-
 We base our generative models almost entirely on pix2pix.
@@
 
-The objective for the generator network is comprised of two parts --- the value of the discriminator as well as
+The objective for the generator network is comprised of two parts --- the value of the discriminator as well as a L1 distance loss between the target and the predicted images.
+According to [] the L1 loss promotes less blurring and captures the low frequency details of the images.
+The L1 loss is given by:
+\begin{equation}
+\mathcal{L}_{L1} (G) = \mathbb{E}[\left\lVert y - G(x)\right\rVert_1]
+\end{equation}
+The final object for the generator is thus:
+\begin{equation}
+G^* = \argminA_G \max_D \mathcal{L}_{cGAN}  + \lambda \mathcal{L}_{L1} (G)
+\end{equation}
+For all of the models we used $\lambda = 100$.
+\\
+\noindent\textbf{Networks Architectures:} For our generator we use the U-Net variant proposed in pix2pix.
+It is a standard encoder-decoder model that skip connections between parts of the encoder and the decoder.
+We also experimented with ResNet based generator but the results were not satisfactory.
+The network uses blocks of layers of the from convolution-normalization-ReLu.
+The encoder-decoder first downsamples the input till a bottleneck layer is reached and what follows is a upsampling to the original size of the input image.
 
-% In contrast to pix2pix we also disable the dropout and batch normalization layers during testing.
+For the discriminator we follow the method of pix2pix and we use their PatchGAN.\@ This is a convolutional network that examines only patches of the input.
+It tires to guess if each patch is from real or generated image.
+We use patches of size $70\times 70$  pixels.
 
-% Our task is an image generation task we used the conditional GAN method introduced in pix2pix.
+\noindent\textbf{Training details: } We train the described three models with the generated datasets.
+When loading the images in memory, we first resize them to $1024\times 256$.
+We then apply random crops as well as add random noise to each channel of the images.
+We do this to force the generator to learn actual features of the simulation and make over-fitting harder.
+Before the input images are fed into the networks, we also multiply them with a mask of the object in the channel.
+This is an image that has zero value in the area where the object is located and one for every other location.
+The multiplication with the mask results in an input image with values of zero in the are of the object.
+The object mask itself is also given as an input to the generator network.
 
-% Some of the experiments in pix2pix suggest that keeping the noise vector can be reasonable but we decided to use only a single multichannel image as an input for the generator network.
+Two of the models also take certain simulation parameters as inputs.
+In all cases the parameters are real values.
+These are first transformed in a constant single channel images with a value equal to the one of the parameter.
+This means that for each simulation parameter
 
-% The generator is trained to produced the next frame of the simulation based on the previous one.
-A single frame contains the two velocity fields as well as optional pressure field.
-We experimented with using and leaving out the pressure field.
+% how does the generator handles parameters
 
-% Some of the models, however, also take some simulation parameters into account.
-For those models, the generator also receives one or two constant channels with a value equal to the value of the parameter.
-
-% The training approach is almost entirely based on pix2pix.
-We used the conditional GAN (Generative adversarial network) method to build a minimal image translation framework.
-In contrast to classical GANs, conditional GANs present both the original and the generated image to the discriminator network.
-The discriminator network is also used as part of the loss function for the generator network.
-
-% In our case, the generator network is presented a single timestep of the simulation in an image form.
-For the inflow-speed and fluid viscosity-density models the corresponding parameters of the simulation are also given to the network.
-The parameters are represented as separate constant channels with a value equal to the one of the parameter.
-
-\subsection{Model types}
-
-\subsection{Evaluation}
-
-\section{Results}\label{results}
+\section{Evaluation}\label{eval}
 

### 2020-03-05 paper/eccv2020submission.tex
Adding some more text to the paper

@@
 
-\noindent\textbf{Training details: } We train the described three models with the generated datasets.
+\noindent\textbf{Training details:} We train the described three models with the generated datasets.
 When loading the images in memory, we first resize them to $1024\times 256$.
@@
 In all cases the parameters are real values.
-These are first transformed in a constant single channel images with a value equal to the one of the parameter.
-This means that for each simulation parameter
+In order for the network to be able to use them as part of the input, we transform these values in a constant single channel images with a value equal to the one of the parameter.
+This means that for each simulation parameter there is an extra channel in the for the generator network.
+Thus, depending on the model being trained, the network can take anywhere between 3 (velocity fields and object mask) and 6 (velocity and pressure fields, object mask and two parameter channels) channel input.
 
-% how does the generator handles parameters
+The output of the generator, however, is limited to either 2 or 3 channel image depending on whether the pressure field is used or not.
 

### 2020-03-10 paper/eccv2020submission.tex
Adding some small parts to the paper

@@
 
+Because the number of simulations in each set is different, we also generated different number of images per simulation based on the corresponding set.
+For the plain dataset, we rendered 1904 frames of the simulation (66 seconds of simulated physical time).
+For the inflow speed dataset --- overall 10050 frames coming from the 40 simulations (335 frames per simulation for 12 seconds of simulated physical time).
+For the viscosity-density model --- overall 104328 frames from 334 simulation (322 frames per simulation for 11 seconds of simulated physical time).
+Even though the simulation in the different datasets represent different time intervals, they are all long enough to develop the flow patterns that we are interested in.
+
 \subsection{Training approach and networks details}
@@
 Thus, depending on the model being trained, the network can take anywhere between 3 (velocity fields and object mask) and 6 (velocity and pressure fields, object mask and two parameter channels) channel input.
+The output of the generator, however, can either be 2 or 3 channel image depending on whether the pressure field is used or not.
 
-The output of the generator, however, is limited to either 2 or 3 channel image depending on whether the pressure field is used or not.
+For the training procedure we follow the standard approach proposed by [].
+With each mini-batch we first optimize the discriminator and then the generator with the discussed objectives.
+We use Stochastic Gradient Descent [] with the Adam optimizer with a learning rate of $0.0002$ and momentum parameters $\beta_1=0.9$ and $\beta_2=0.999$.
+
+The used batch size for the constant and inflow speed models was set to 3 and for the viscosity-density models to 4.
+Those are relatively small numbers for batch sizes but [] suggests that the UNet architecture benefits from small batches in image-to-image translation problems.
+Our experiments confirmed this.
+
+Because of the differences in the amount of data available for training each model type, suitable epoch numbers were chosen for each of them.
+The constant models were trained for 45 epochs, the inflow speed models for 30 epochs and the viscosity-density models for 10 epochs.
+
+All of the models were trained and evaluated on a single Nvidia GTX 980Ti GPU.\@
 

### 2020-03-10 paper/eccv2020submission.tex
Cleaning up some of the introducion of the paper

@@
 The task usually consists of setting certain initial conditions in a defined space and solving a large mathematical problem for each timestep of the simulation.
-Two central points of interest in CFD is the processing time needed for a simulation as well as the accuracy of the results.
-It is clear that low processing time and high accuracy are desired but often e certain trade off has to be made.
+Two central points of interest in CFD are the processing time needed for a simulation and the accuracy of the results.
+It is clear that low processing time and high accuracy are desired but often a certain trade off has to be made.
 With our research we want to propose an innovative method for quickly inspecting the results of a simulation while keeping the accuracy high enough for them to make sense.
 
-We've concentrated our study on 2D simulations of a incompressible fluid flow around an object in a channel according to the Navier-Stokes equations.
+We've concentrated our study on 2D simulations of an incompressible fluid flow around an object in a channel according to the Navier-Stokes equations.
 This setup has three adjustable parameters --- the inflow speed, the viscosity and the density of the fluid.
-The solutions of the simulation are three separate fields over the input space --- two velocity fields in x and y directions and a pressure field.
+The solutions of the simulation are three separate fields over the input space --- two velocity fields in $x$ and $y$ directions and a pressure field.
 These can be conveniently visualized as images over the input space.
 We are mainly interested in those image representations of the timeteps of the simulation.
+We call the image representations of the timesteps ``frames'' of the simulation.
+The sequence of this frames show how the flow develops over the course of the simulation.
 
 Classical methods for performing such simulations are based on partial differential equations (PDEs) solvers.
-The simulation setup is first formalized and a mathematical model in form of a time dependent differential equation is given.
-In itself this equation is then transformed and brought into a suitable form.
+The simulation setup is first formalized as a mathematical model in the form of a time dependent differential equation.
+In itself this equation is then transformed and brought into a suitable for solving form.
 A common technique is the finite difference method (FDM).
 This can provide accurate results at the cost of large computational time.
-The generated results are in form of raw numbers representing the velocities and pressure fields which has to be visualized separately.
+The generated results are in form of raw numbers representing the velocities and pressure fields which have to be visualized separately.
 Our method aims to generate straight the visualizations while needing much lower computational time.
@@
 Convolutional Neural Networks (CNNs) in particular have been successfully applied in a wide variety of contexts and having proven to be a valuable tools.
-On of the major fields where the performance of CNNs is recognized is image processing.
+One of the major fields where the performance of CNNs is clearly recognized is image processing.
 A lot of research has shown how CNNs can achieve state-of-the-art performance in tasks like image classification, image segmentation of image-to-image mapping.
@@
 
+We try to apply the approach of [pix2pix] in our work.
+In recent years GAN show impressive results in image generation.
+Conditional GANs (cGANs) extend this capabilities of the generator network and allow it to learn image-to-image translation tasks.
+We wanted to show that conditional GANs can be used in the context of numerical simulations.
+In this case, the generation of a frame of a simulation is conditioned on the previous frame of the same simulation.
+
 The goal of our research is to see to what extend the described approach is viable.
-We achieve that by investigating how a CNN generalizes the different parameters of the investigated simulation.
+We achieve that by investigating how a cGANs generalizes the different parameters of the investigated simulation.
 Two subsets of the parameters are defined --- fluid parameters (viscosity and density) and inflow speed of the fluid.
-For each of these two subsets we train a separate model and evaluate its performance in different use cases.
+For each of these two subsets we train a separate models and evaluate their performance in different use cases.
 A baseline model that does not take parameters into account is also built.
@@
 Firstly, as the output of the network is meant for a human observer, we evaluate the generated images based on their perceived fidelity.
-Secondly, as the networks tries to model a numerical task, we also compare the real and generated images in a objective manner by measuring the actual differences between them.
+Secondly, as the networks tries to model a numerical task, we also compare the real and generated images in an objective manner by measuring the actual differences between them.
 
@@
 Hence also evaluate the models by recursive application where the output of the network is used again as an input for certain amount of timesteps.
+More details about the evaluations are given in \refsec{eval}.
 
 Lastly, we briefly want to motivate why we propose exactly this approach.
-
-Our contributions are \ldots.
+Images represent a well defined input space as every pixel can take limited range of values --- $[0, 255]$.
+This makes the handling of data in image form convenient.
+Our assumption was that a neural network can process the information in this from more easily.
+Furthermore, convolutional neural networks are well established models for preforming image processing tasks.
+We were interested how a numerical task can be turn into an image processing task as in certain situations, the image result has the priority.
+We also think that the image processing can be done much quicker in a more optimal way.
+Those considerations urged us to conduct the research presented in this paper.
 
@@
 \section{Methodology}\label{methodology}
-% \emph{The models were trained with real simulation data.
-We first describe the process of generating said data, then we give details on the training procedure and the architecture of the models.
-We then descibe the three types of models that we build and evaluated.}
-
 The task is to build a network that can predict the next frame of the simulation based on the previous one.
@@
 We were interested in how the usage of the pressure field affects the performance of the built models.
-Therefore, for each model be trained two variants --- one that uses the pressure field and one that does not.
+Therefore, for each model two variants are trained --- one that uses the pressure field and one that does not.
 
@@
 The studied models are:
-\begin{itemize}
-\item A Constant model --- does not take into any of the parameters and it is trained with data from a single simulation.
+\begin{list}{$\circ$}{}
+\item a constant model --- does not take into any of the parameters and it is trained with data from a single simulation.
 It is conceived as a baseline and proof of concept model that is there to show how a neural network can learn to generate simulation timesteps in from of images.
@@
 \item A viscosity and density model --- the model receives the viscosity and density of the fluid as extra inputs.
-\end{itemize}
+\end{list}
 By evaluating each models we want to see how a network can generalize each of the parameter subsets and to what extent
 
-To study the performance of conditional GANs on generating frames of the concrete simulation we generated the training data ourselves. In what follows we give details about the process.
-
 \subsection{Simulation Setup and Data generation}
-The training data was generated by performing numerous simulations of an incompressible fluid flow around a rectangular object in a channel.
+\emph{To study the performance of conditional GANs on generating frames of the concrete simulation we generated the training data ourselves.
+In what follows we give details about the process.} The training data was generated by performing numerous simulations of an incompressible fluid flow around a rectangular object in a channel.
 The simulations were modeled according to the Navier-Stokes equations for incompressible flow.
@@
 There are several boundary conditions that describe the simulation setup:
-\begin{itemize}
+\begin{list}{$\circ$}{}
 \item Inflow condition on the left side of the channel
@@
 \item No slip condition on bottom and top side of the channel as well as the sides of the object.
-\end{itemize}
-The simulation setup has three separate adjustable parameters --- inflow speed, fluid density and fluid viscosity.
+\end{list}
+The simulation setup has three separate adjustable parameters --- inflow speed $g$, fluid density $\rho$ and fluid viscosity $\vu$.
 \\
 We generated three sets of simulations for training the three kinds of models.
-\begin{itemize}
+\begin{list}{$\circ$}{}
 \item plain: a single simulation with \ldots.
@@
 We used the product of the two parameter ranges to perform simulations with all of the possible combinations between the two parameters.
-\end{itemize}
+\end{list}
 
-The choice of the concrete values for the parameters was deliberate.
-All of the values are chosen so that the Reynolds number of the simulations in the range of \ldots.
+The choice of the concrete values for the parameters is deliberate.
+All of the values are chosen so that the Reynolds number of the simulations in the range of [90, 450].
 This keeps the flow laminar while still making it interesting enough.
@@
 The simulations were performed numerically by solving the differential equation describing the flow --- the Navier-Stokes equation.
-This was done with a numerical solver library --- HiFlow ---  that works on the base of Finite element method.
+This was done with a numerical solver library --- \emph{HiFlow} [] ---  that works on the base of Finite element method.
 The solver supports parallelization with MPI and OpenMP and we used 12 MPI processes to run each simulation.
@@
 The numerical solver on itself cannot be used to render the simulation results to images.
-For this reason we used ParaView to load the simulation data and exported it as a sequence of images in PNG format.
+For this reason we used \emph{ParaView} to load the simulation data and exported it as a sequence of images in PNG format.
 We opted out for using grayscale images as early experiments with RGB-images did not deliver satisfying results.
@@
 \subsection{Training approach and networks details}
-We base our generative models almost entirely on pix2pix.
+We base our generative models almost entirely on [pix2pix].
 We use the conditional GAN approach to train a generator network that can perform image-to-image translation.
@@
 For all of the models we used $\lambda = 100$.
-\\
+
 \noindent\textbf{Networks Architectures:} For our generator we use the U-Net variant proposed in pix2pix.
@@
 
-% LocalWords:  Convolutional timestep timesteps grayscale
+% LocalWords:  Convolutional timestep timesteps grayscale cGANs

### 2020-03-16 paper/eccv2020submission.tex
Adding small paragraph to the evaluation

@@
 In contrast to unconditional GANs, both the generator and the discriminator network have access to the input image.
-The objective is divided by 2 to slow down the training of the discriminator relative to the generator as suggested by [].
+The objective is divided by two to slow down the training of the discriminator relative to the generator as suggested by [].
 
@@
 
-All of the models were trained and evaluated on a single Nvidia GTX 980Ti GPU.\@
+All of the models were trained and evaluated on a single Nvidia GTX 980Ti GPU.\@ The implementation of the models was done in the PyTorch python library for machine leaning.
 
 \section{Evaluation}\label{eval}
+
+When it comes to the evaluation, we have two separate views of the results generated by the models.
+
+On one hand, we are dealing with image data that is meant to be perceived by human observer.
+This implies that full accuracy is not essential and therefore we place the importance on the perceived qualities of the results.
+This makes sense as in our case a human is concerned with the general development of the simulation over time.
+Under those consideration have chose appropriate metrics to compare the predicted simulation frames with the real ones.
+In this aspect, the first of the metrics that we have chose is Peak Signal to Noise Ratio (PSNR).
+It is related top the mean secured error (MSE) and it's given by
+\begin{equation}
+PSNR = 10 \cdot \log_{10}\left(\frac{255^2}{MSE}\right)
+\end{equation}
+PSNR is measured in decibel (dB) and it is a common metric used to evaluate lossy compression algorithms.
+It measures the difference between original and reconstructed image and considers the fidelity of the reconstruction.
+This makes the metric suitable in our case.
+Typical PSNR values of lossy image and video compression  algorithms are between 30 and 50 dB.
 

### 2020-03-16 paper/eccv2020submission.tex
Adding paragraph about correlation

@@
 This makes the metric suitable in our case.
-Typical PSNR values of lossy image and video compression  algorithms are between 30 and 50 dB.
+Typical PSNR values of lossy image and video compression  algorithms are between $30$ and $50$ dB.
+
+When considering the perceived image quality, we also have decided to use correlation to compare the predicted and the real simulation frames.
+We think that if the predicted images differ only in a factor from the real ones, the models can accurately capture the relative difference between the pixels of the target image.
+For this reason we opted for also evaluating the results through correlation.
 

### 2020-03-23 paper/eccv2020submission.tex
Adding a good portion of the paper

@@
 \end{list}
-The simulation setup has three separate adjustable parameters --- inflow speed $g$, fluid density $\rho$ and fluid viscosity $\vu$.
+The simulation setup has three separate adjustable parameters --- inflow speed $g$, fluid density $\rho$ and fluid viscosity $\nu$.
 \\
@@
 
-When it comes to the evaluation, we have two separate views of the results generated by the models.
+\noindent\textbf{Evaluation Metrics:} When it comes to the evaluation, we have two separate views of the results generated by the models.
 
@@
 
+On the other hand, as we are dealing with a numerical task, we also wanted to evaluate the results in a more object manner.
+Classical solvers are evaluated in terms of the actual differences between the real and generated result and not the perceived differences.
+For those reasons, we have chosen two more metrics --- average difference and maximal differences.
+We calculated them based on differences between the corresponding pixels of the predicted and the real simulation frame.
+Both metrics are then averaged across the test set and are given in absolute values.
+The evaluation with these metrics should represent how well our models perform the simulation in the context of a CFD system.
+
+\noindent\textbf{Details Evaluation:}
+\emph{In this subsection we want to give several details on the training and evaluating approach}
+\begin{itemize}
+\item All models were trained from scratch and no pretraining or transfer-learning was undertaken.
+\item For each model, the whole training and evaluating procedure was done ten times with different seeds for the random number generators of our python scripts.
+We report the results of each run and give them in a form of error plots or explicitly give the variance of all runs.
+\item All of the reported results of for the individual runs are averaged across the simulation frames in the training sets.
+\item While performing the experiments, we did not tweak the hyper parameters of the models excessively.
+We did, however, tried several sets of hyper parameters until the models achieved satisfactory results.
+The exact hyper parameters are given in []
+\end{itemize}
+
+\noindent\textbf{Single Image Performance:}
+As mentioned before, we have two evaluation strategies for the models.
+The first of them is to see how well a single frame of the simulation is predicted.
+In this case, we pass all of the simulation frames in the test set to the network and evaluate the predicted frames.
+The models use only real simulation data for their predictions.
+
+[Fig] shows the results of the different model types with respect to PSNR.\@ Examples of the predicted images are given in [fig].
+We can clearly see that the predicted images are almost identical to the real ones.
+In all cases, we measured a correlation of about $0.9998$ so we will not give it explicitly here.
+We think that the images themselves illustrate the high correlation.
+
+[Table] summarizes the results of the evaluation with the average and maximal difference metrics.
+
+\\
+
+\begin{center}
+  \begin{tabular}{l|c|c}
+    Model type & Max difference &  Average difference\\
+    \hline
+    Constant & 0.5 &  0.5 \\
+    Inflow speed &  0.5 &  0.5 \\
+    Viscosity-density &  0.5  &  0.5 \\
+  \end{tabular}
+\end{center}
+
+The effects of the usage of the pressure field can be seen in the variance of the results.
+The pressure field has the potential to make the models better but in some runs it can also make them worse.
+We believe this is the case because the pressure fields increases the complexity of the data but it also carries information about the simulation that can be useful for the networks.
+
+\\
+
+Based on our experiments, we can say that achieving good performance was the hardest for the constant model.
+We attribute that to the limited data with which it was trained --- only a single simulation.
+Contrary to the intuition, the more varied data is easier to predict, as it can be seen in the results for the inflow speed and viscosity-density models.
+We also believe, that a bigger test set can better estimate the performance of our models.
+This probably also contributes to the worse results for the constant models.
+
+\noindent\textbf{Recursive Application Performance:}
+
 \section{Conclusion}\label{conclusion}

### 2020-03-24 paper/eccv2020submission.tex
Addin the recursive aplication portion and the split methodoogy

@@
 \documentclass{llncs}
+\usepackage[title]{appendix}
 \usepackage[pagebackref]{hyperref}
+\usepackage{subcaption}
 \usepackage{graphicx}
@@
 \begin{list}{$\circ$}{}
-\item plain: a single simulation with \ldots.
+\item constant: a single simulation with \ldots.
 \item varying inflow speed: \ldots simulations with different inflow speed. The inflow speeds are in the range of \ldots with a step of \ldots.
@@
 Because the number of simulations in each set is different, we also generated different number of images per simulation based on the corresponding set.
-For the plain dataset, we rendered 1904 frames of the simulation (66 seconds of simulated physical time).
+For the constant dataset, we rendered 1904 frames of the simulation (66 seconds of simulated physical time).
 For the inflow speed dataset --- overall 10050 frames coming from the 40 simulations (335 frames per simulation for 12 seconds of simulated physical time).
@@
 Even though the simulation in the different datasets represent different time intervals, they are all long enough to develop the flow patterns that we are interested in.
+
+After all images were generated, a test-train split was created for each of the datasets The split for the inflow speed and viscosity-density sets were done manually.
+For the inflow speed set, we selected every fourth simulation to be part of the test set and for the viscosity-density set --- every 25th.
+All other simulations are used for training.
+The split for the constant dataset was done at random.
+All of the splits result in a 80\% of the data being used for training and the rest for testing.
+It is important to note that all of the images in the test sets come from simulations with parameters that are not found for the simulations in the training sets.
+This means that the datasets are designed in a way to see if the models can generalize the parameters of the simulations and predict simulations with parameters that are unseen during the training.
 
@@
 
-\\
-
+\begin{table}
   \begin{center}
@@
   \end{center}
+  \caption{\label{tab:table-name} Your caption.}
+\end{table}
+
+\begin{figure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/pred}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/pred.png}  
+  \end{subfigure}
+\end{figure}
 
@@
 We believe this is the case because the pressure fields increases the complexity of the data but it also carries information about the simulation that can be useful for the networks.
-
-\\
 
@@
 \noindent\textbf{Recursive Application Performance:}
+With this evaluation case we want to see how our models handle recursive application. That is, the output of the network is used again as an input for the prediction of the next simulation frame.
+
+For each recursive evaluation we generate 40 frames of the corresponding simulation.
+We did not in any was post-processed the output of the networks before feeding it as an input.
+We calculate the discussed metrics for each of the predicted frames while comparing them to the corresponding real one.
+
+In our experiments, we performed several recursive evaluation for each simulation while starting at frames with different index.
+We wanted to see how a different starting point in the simulation can affect the frames predicted by the models.
+
+The viscosity-density and inflow speed models are evaluated with several simulations with different parameters.
+As it is unpracticed to give the results of the evaluation of each simulation, here we present only several of them.
+The showed results, however, are representative of the general performance of our models.
+For this section, We also limit ourselves only to models that do use the pressure field of the simulations.
+
+The constant model is evaluated with a single simulation --- the one it was trained with.
+[fig] presents the results of the recursive application.
+During the evaluation we noticed that the models can more accurately predict a simulation when the starting frame is further in the simulation.
+That is, its index relative to the first frame is higher.
+The plots for the constant model in [fig] illustrate this.
+
+For the inflow speed model we present the results from three different simulations in [fig].
+We can see the same trend that predicting frames with smaller index is harder.
+We, however, like to note that the networks appear to be handling the parameters properly and adjust the predicted frames accordingly.
+[fig] presents the results of the viscosity-density model.
+
+We again do not explicitly give the correlation between the predicted and real frames.
+In all cases the correlation stayed very close to $1$ and varied in the range $[0.98, 0.99998]$.
+The CFD-metrics are summarized in [table].
 
@@
 \bibliography{egbib}
+
+\begin{subappendices}
+\renewcommand{\thesection}{\Alph{section}}%
+
+\section{Networks architectures and hyperparameters}
+\emph{Here we give the exact details on the architectures of the used networks.}
+
+\end{subappendices}
+
 \end{document}

### 2020-03-24 project/train.py

@@ -501,9 +501,18 @@ if args.evaluate:
         if args.model_type == 'vd':
             print('===> Running simulations for vd:')
             
-            indices = [(7705 + 50, 'vd_50'), (17335 + 150, 'vd_150'), (23755 + 10, 'vd_10'), (31780 + 250, 'vd_250'), (39805 + 2, 'vd_2'),
-                       (55855 + 150, 'vd'), (63880 + 150, 'vd'), (71807 + 150, 'vd'), (79832 + 150, 'vd'), (87857 + 150, 'vd'),
-                       (95882 + 150, 'vd'), (99092 + 150, 'vd')]
+            indices = [(7705 + 50, 'vd_50'),
+                       (17335 + 150, 'vd_150'),
+                       (23755 + 10, 'vd_10'),
+                       (31780 + 250, 'vd_250'),
+                       (39805 + 2, 'vd_2'),
+                       (55855 + 150, 'vd'),
+                       (63880 + 150, 'vd'),
+                       (71807 + 150, 'vd'),
+                       (79832 + 150, 'vd'),
+                       (87857 + 150, 'vd'),
+                       (95882 + 150, 'vd'),
+                       (99092 + 150, 'vd')]
             
             evaluator.set_output_name('simulations')
 

### 2020-03-24 paper/eccv2020submission.tex
Adding some text to the appendix

@@
 \emph{Here we give the exact details on the architectures of the used networks.}
+The code for all of the models and experiments can be found at \url{https://github.com/palikar/flow_predict}.
+
+The architectures are almost entirely based on [pix2pix, 44].
+Both the generator and the discriminator networks are comprised of two types of blocks of layers.
+We will denote a Convolution-BatchNorm-ReLU block with $k$ filters with $Ck$ and Convolution-BatchNorm-Dropout-ReLU with $k$ filters $CDk$.
+The dropout rate for each dropout layers is 50\%.
+All convolutions use $4\times4$ filters applied with a stride of $2$.
+
+\noindent\textbf{Generator Architecture:}
+The generator is an follows the encoder-decoder principle.
+All model types use 6 layer encoder and decoder.
+The model types differ only in the amount of filters that they have in the blocks.
+As we use the U-Net architecture, the there are also skip connections between each block $i$ in the encoder and the block $n-i$ in the decoder where $n$ is the total number of blocks in the network.
+The skip connections concatenate the results the both blocks $i$ and $i-i$.
+
+The concrete encoder-decoders for each model type are as follows:
+\begin{itemize}
+\item[\cdot] Constant model:\newline
+  \emph{Encoder}: \texttt{C32-C64-C128-C256-C256-C256}\newline
+  \emph{Decoder}: \texttt{CD256-C512-C512-C256-C128-C64}
+\item[\cdot] Inflow speed model:\newline
+  \emph{Encoder}: \texttt{C48-C96-C192-C384-C384-C384}\newline
+  \emph{Decoder}: \texttt{CD384-C768-C768-C384-C192-C96}
+\item[\cdot] Viscosity-Density model:\newline
+  \emph{Encoder}: \texttt{C64-C128-C256-C512-C512-C512} \newline
+  \emph{Decoder}: \texttt{CD512-C1024-C1024-C512-C256-C128}
+\end{itemize}
+
+The ReLUs in the encoders are leaky (slope of $0.2$) and those in the decoders are not.
+At the end of each decoder there is also a convolution layer that maps to the final channel count of the output.
+This final convolution is followed by a $\tanh$-function.
+
+\noindent\textbf{Discriminator Architecture:}
+We adopt the $70\times70$ variant of the decoder form [pix2pix]. The architecture is:\newline
+\texttt{C64-C128-C256-C512}
 

### 2020-03-25 paper/eccv2020submission.tex
Adding basic chart generation scripts

@@
 
+This configuration results in a receptive field of $70\times70$.
+This means that for each $70\times70$ region of the input, the discriminator tries to guess if the region is from a real image or from a generated one.
+
+All of the ReLUs are leaky (slope of $0.2$).
+Also, a final convolution is applied after the last layers that produced the a dimensional output of the discriminator.
+A sigmoid function is applied after the convolution.
+
 \end{subappendices}

### 2020-03-25 charts/recursive.py

@@ -1,0 +1,33 @@
+#!/usr/bin/env python
+import matplotlib
+import matplotlib.pyplot as plt
+import os
+import sys
+
+import numpy as np
+
+plt.style.use('ggplot')
+plt.rcParams.update({'figure.max_open_warning': 0})
+
+
+def main():
+
+    matplotlib.rc('xtick', labelsize=17)
+    matplotlib.rc('ytick', labelsize=17)
+
+    x = np.array([0, 5, 10, 15, 20, 25, 30, 35, 40])
+    y = np.linspace(44.6, 33.3, len(x))
+
+    yerr = np.linspace(1, 5, len(x))
+    
+    plt.figure()
+    plt.errorbar(x, y, yerr=yerr, fmt='-o', ecolor='black', mfc='white', mec='black', color='black')
+    plt.gca().spines['top'].set_visible(False)
+    plt.gca().spines['right'].set_visible(False)
+    plt.xlabel('Frame index', fontsize=16)
+    plt.ylabel('PSNR', fontsize=16)
+    plt.title('Constant model (recursive application performance)', fontsize=17)
+    plt.show()
+
+if __name__ == '__main__':
+    main()

### 2020-03-25 charts/single.py

@@ -1,0 +1,130 @@
+import matplotlib
+import matplotlib.pyplot as plt
+import os
+import sys
+
+plt.style.use('ggplot')
+plt.rcParams.update({'figure.max_open_warning': 0})
+
+
+def constant_models():
+
+    data = {}
+    labels = []
+    box_data = []
+
+    data['with'] = [1,1.3,1.5,0.9,1.23,1.32]
+    data['without'] = [1,1.3,1.5,0.9,1.23,1.32]
+
+    box_data.append([1,1.3,1.5,0.9,1.23,1.32])
+    box_data.append([1,1.3,1.5,0.9,1.23,1.32])
+
+    labels.append('with pressure')
+    labels.append('without pressure')
+
+    matplotlib.rc('xtick', labelsize=13)
+    matplotlib.rc('ytick', labelsize=17)
+
+    plt.figure(figsize=(17, 10))
+
+    x = [i for i in range(1, len(data.keys())+1)]
+
+    plt.boxplot(box_data, labels=labels)
+
+    for (_, times), i  in zip(data.items(), x):
+        plt.scatter([i]*len(times), times, alpha=0.5, linewidths=None)
+
+
+    plt.gca().spines['top'].set_visible(False)
+    plt.gca().spines['right'].set_visible(False)
+
+    plt.ylabel('PSNR')
+    plt.title('Constant model (single image performance)', fontsize=17)
+
+    plt.show()
+
+
+def speed_models():
+
+    data = {}
+    labels = []
+    box_data = []
+
+    data['with'] = [1,1.3,1.5,0.9,1.23,1.32]
+    data['without'] = [1,1.3,1.5,0.9,1.23,1.32]
+
+    box_data.append([1,1.3,1.5,0.9,1.23,1.32])
+    box_data.append([1,1.3,1.5,0.9,1.23,1.32])
+
+    labels.append('with pressure')
+    labels.append('without pressure')
+
+    matplotlib.rc('xtick', labelsize=13)
+    matplotlib.rc('ytick', labelsize=17)
+
+    plt.figure(figsize=(17, 10))
+
+    x = [i for i in range(1, len(data.keys())+1)]
+
+    plt.boxplot(box_data, labels=labels)
+
+    for (_, times), i  in zip(data.items(), x):
+        plt.scatter([i]*len(times), times, alpha=0.5, linewidths=None)
+
+
+    plt.gca().spines['top'].set_visible(False)
[…]

### 2020-03-25 paper/eccv2020submission.tex
Adding the conclusion

@@
 \usepackage{comment}
-\usepackage{amsmath,amssymb} % define this before the line numbering.
+\usepackage{amsmath,amssymb}
 \usepackage{color}
@@
 \newcommand{\refapp}[1]{\hyperref[#1]{Appendix \ref*{#1}}}
-\DeclareMathOperator*{\argminA}{arg\,min} % Jan Hlavacek
+\DeclareMathOperator*{\argminA}{arg\,min}
 
@@
 \mainmatter
-\def\ECCVSubNumber{100}  % Insert your submission number here
+\def\ECCVSubNumber{100}
 
-\title{Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks} % Replace with your title
+\title{Towards Bringing Together Numerical Methods for Partial Differential Equation and Image Processing}
 
@@
 \begin{list}{$\circ$}{}
-\item a constant model --- does not take into any of the parameters and it is trained with data from a single simulation.
+\item[$\cdot$] a constant model --- does not take into any of the parameters and it is trained with data from a single simulation.
 It is conceived as a baseline and proof of concept model that is there to show how a neural network can learn to generate simulation timesteps in from of images.
-\item A fluid inflow speed model --- the model receives the inflow speed of the fluid as an extra input. It is trained with data from several simulations with different inflow speeds.
-\item A viscosity and density model --- the model receives the viscosity and density of the fluid as extra inputs.
+\item[$\cdot$] A fluid inflow speed model --- the model receives the inflow speed of the fluid as an extra input. It is trained with data from several simulations with different inflow speeds.
+\item[$\cdot$] A viscosity and density model --- the model receives the viscosity and density of the fluid as extra inputs.
 \end{list}
@@
 \begin{list}{$\circ$}{}
-\item Inflow condition on the left side of the channel
-\item Outflow condition on the right side of the channel
-\item No slip condition on bottom and top side of the channel as well as the sides of the object.
+\item[$\cdot$] Inflow condition on the left side of the channel
+\item[$\cdot$] Outflow condition on the right side of the channel
+\item[$\cdot$] No slip condition on bottom and top side of the channel as well as the sides of the object.
 \end{list}
@@
 \begin{list}{$\circ$}{}
-\item constant: a single simulation with \ldots.
-\item varying inflow speed: \ldots simulations with different inflow speed. The inflow speeds are in the range of \ldots with a step of \ldots.
-\item varying viscosity and density of the fluid: \ldots simulations all with different fluid viscosity and density.
+\item[$\cdot$] constant: a single simulation with \ldots.
+\item[$\cdot$] varying inflow speed: \ldots simulations with different inflow speed. The inflow speeds are in the range of \ldots with a step of \ldots.
+\item[$\cdot$] varying viscosity and density of the fluid: \ldots simulations all with different fluid viscosity and density.
 The viscosity was in the range of \ldots with a step of \ldots and the density was in the range of \ldots with a step of \ldots.
@@
 \begin{itemize}
-\item All models were trained from scratch and no pretraining or transfer-learning was undertaken.
-\item For each model, the whole training and evaluating procedure was done ten times with different seeds for the random number generators of our python scripts.
+\item[$\cdot$] All models were trained from scratch and no pretraining or transfer-learning was undertaken.
+\item[$\cdot$] For each model, the whole training and evaluating procedure was done ten times with different seeds for the random number generators of our python scripts.
 We report the results of each run and give them in a form of error plots or explicitly give the variance of all runs.
-\item All of the reported results of for the individual runs are averaged across the simulation frames in the training sets.
-\item While performing the experiments, we did not tweak the hyper parameters of the models excessively.
+\item[$\cdot$] All of the reported results of for the individual runs are averaged across the simulation frames in the training sets.
+\item[$\cdot$] While performing the experiments, we did not tweak the hyper parameters of the models excessively.
 We did, however, tried several sets of hyper parameters until the models achieved satisfactory results.
@@
 
+The results presented in this paper suggest that solving a numerical task trough image-to-image translation is can be a viable approach.
+We showed how conditional GANs can be used to learn the image representations of the solutions of a fluid simulation according to the Navier-Stokes equations.
+We built several models that can generalize different parts of the parameters of the simulations and gave concrete numbers that quantify the results.
+
+We see our work as a preliminary research and we believe that the approach can be further developed and investigated.
+Strategies for improving the models that were considered but not implemented include:
+\begin{itemize}
+\item[$\cdot$] using a LSTM layer in the networks --- our models have the limitation that during training they don't know about the artifact on the images caused by themselves.
+We think a LSTM layer can mitigate this problem.
+\item[$\cdot$] preprocessing the input for and postprocessing the output of the networks --- morphological operations like opening and closing can also be used to minimize the artifacts in the predicted frames.
+\item[$\cdot$] further investigation of the effects of using RGB-images instead of grayscale ones.
+\end{itemize}
+
 \clearpage
@@
 \begin{itemize}
-\item[\cdot] Constant model:\newline
+\item[$\cdot$] Constant model:\newline
   \emph{Encoder}: \texttt{C32-C64-C128-C256-C256-C256}\newline
   \emph{Decoder}: \texttt{CD256-C512-C512-C256-C128-C64}
-\item[\cdot] Inflow speed model:\newline
+\item[$\cdot$] Inflow speed model:\newline
   \emph{Encoder}: \texttt{C48-C96-C192-C384-C384-C384}\newline
   \emph{Decoder}: \texttt{CD384-C768-C768-C384-C192-C96}
-\item[\cdot] Viscosity-Density model:\newline
+\item[$\cdot$] Viscosity-Density model:\newline
   \emph{Encoder}: \texttt{C64-C128-C256-C512-C512-C512} \newline
@@
 % LocalWords:  Convolutional timestep timesteps grayscale cGANs
+% LocalWords:  preprocessing postprocessing

### 2020-03-25 charts/recursive.py

@@ -10,7 +10,108 @@ plt.style.use('ggplot')
 plt.rcParams.update({'figure.max_open_warning': 0})
 
 
-def main():
+def consant_i20():
+    
+    matplotlib.rc('xtick', labelsize=17)
+    matplotlib.rc('ytick', labelsize=17)
+
+    x = np.array([0, 5, 10, 15, 20, 25, 30, 35, 40])
+    y = np.linspace(44.6, 33.3, len(x))
+
+    yerr = np.linspace(1, 5, len(x))
+    
+    plt.figure()
+    plt.errorbar(x, y, yerr=yerr, fmt='-o', ecolor='black', mfc='white', mec='black', color='black')
+    plt.gca().spines['top'].setc_visible(False)
+    plt.gca().spines['right'].set_visible(False)
+    plt.xlabel('Frame index', fontsize=16)
+    plt.ylabel('PSNR', fontsize=16)
+    plt.title('Constant model (recursive application performance)', fontsize=17)
+    plt.show()
+
+
+
+def consant_i200():
+    
+    matplotlib.rc('xtick', labelsize=17)
+    matplotlib.rc('ytick', labelsize=17)
+
+    x = np.array([0, 5, 10, 15, 20, 25, 30, 35, 40])
+    y = np.linspace(44.6, 33.3, len(x))
+
+    yerr = np.linspace(1, 5, len(x))
+    
+    plt.figure()
+    plt.errorbar(x, y, yerr=yerr, fmt='-o', ecolor='black', mfc='white', mec='black', color='black')
+    plt.gca().spines['top'].setc_visible(False)
+    plt.gca().spines['right'].set_visible(False)
+    plt.xlabel('Frame index', fontsize=16)
+    plt.ylabel('PSNR', fontsize=16)
+    plt.title('Constant model (recursive application performance)', fontsize=17)
+    plt.show()
+
+
+def speed_i2():
+    
+    matplotlib.rc('xtick', labelsize=17)
+    matplotlib.rc('ytick', labelsize=17)
+
+    x = np.array([0, 5, 10, 15, 20, 25, 30, 35, 40])
+    y = np.linspace(44.6, 33.3, len(x))
+
+    yerr = np.linspace(1, 5, len(x))
+    
+    plt.figure()
+    plt.errorbar(x, y, yerr=yerr, fmt='-o', ecolor='black', mfc='white', mec='black', color='black')
+    plt.gca().spines['top'].setc_visible(False)
[…]

### 2020-03-25 paper/eccv2020submission.tex
Adding some exmaple images

@@
 \begin{figure}
+
   \begin{subfigure}{.5\textwidth}
     \centering
-    \includegraphics[width=1\linewidth]{imgs/pred}
+    \includegraphics[width=1\linewidth]{imgs/single_constant_x}
+
   \end{subfigure}  
@@
     \centering
-    \includegraphics[width=1\linewidth]{imgs/pred.png}  
+    \includegraphics[width=1\linewidth]{imgs/single_constant_y}
+
   \end{subfigure}
+  \begin{center}
+    Constant model
+  \end{center}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/single_speed_x_1}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/single_speed_y_1}  
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/single_speed_x_2}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/single_speed_y_2}  
+  \end{subfigure}
+
+  \begin{center}
+    Images form the inflow speed model. The upper two are from simulation with $g=1.3$ and the lower ones form simulation with $g=0.1$
+  \end{center}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    % \caption{Fluid model, x-velocity fields}
+      \includegraphics[width=1\linewidth]{imgs/single_fluid_x_1}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    % \caption{Fluid model, y-velocity fields}
+    \includegraphics[width=1\linewidth]{imgs/single_fluid_y_1}  
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    % \caption{Fluid model, x-velocity fields}
+    \includegraphics[width=1\linewidth]{imgs/single_fluid_x_2}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    % \caption{Fluid model, y-velocity fields}
+    \includegraphics[width=1\linewidth]{imgs/single_fluid_y_2}
+  \end{subfigure}
+
+  \begin{center}
+  Images form the viscosity-density model. The upper two are from simulation with $\nu=1.3, \rho=2.3$ and the lower ones form simulation with $\nu=1.3, \rho=2.3$
+  \end{center}
+
+  \caption{Each image haw tow halves and the upper one shows the ground truth simulation frame.
+The lower half is the prediction of the model.
+In the left column, the images are from the x-velocity fie4ld of the simulation and in the right --- form the y-velocity field.}
 \end{figure}
@@
 \end{itemize}
+
+\begin{figure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_1}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_1}  
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_5}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_5}  
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_10}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_10}  
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_15}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_15}  
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_20}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_20}  
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_25}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_25}  
+  \end{subfigure}
+
+  \caption{These frames are generated by the constant model. The artifacts become apparent after the 10.\@ one.}
+\end{figure}
 

### 2020-03-25 paper/eccv2020submission.tex
adding fluid sim images

@@
 \usepackage{color}
-
+\usepackage{float}
 \newcommand{\reffig}[1]{\hyperref[#1]{Figure \ref*{#1}}}
@@
 
-\begin{table}
-  \begin{center}
-    \begin{tabular}{l|c|c}
-      Model type & Max difference &  Average difference\\
-      \hline
-      Constant & 0.5 &  0.5 \\
-      Inflow speed &  0.5 &  0.5 \\
-      Viscosity-density &  0.5  &  0.5 \\
-    \end{tabular}
-  \end{center}
-  \caption{\label{tab:table-name} Your caption.}
-\end{table}
+The effects of the usage of the pressure field can be seen in the variance of the results.
+The pressure field has the potential to make the models better but in some runs it can also make them worse.
+We believe this is the case because the pressure fields increases the complexity of the data but it also carries information about the simulation that can be useful for the networks.
+
+Based on our experiments, we can say that achieving good performance was the hardest for the constant model.
+We attribute that to the limited data with which it was trained --- only a single simulation.
+Contrary to the intuition, the more varied data is easier to predict, as it can be seen in the results for the inflow speed and viscosity-density models.
+We also believe, that a bigger test set can better estimate the performance of our models.
+This probably also contributes to the worse results for the constant models.
 
@@
 
-The effects of the usage of the pressure field can be seen in the variance of the results.
-The pressure field has the potential to make the models better but in some runs it can also make them worse.
-We believe this is the case because the pressure fields increases the complexity of the data but it also carries information about the simulation that can be useful for the networks.
-
-Based on our experiments, we can say that achieving good performance was the hardest for the constant model.
-We attribute that to the limited data with which it was trained --- only a single simulation.
-Contrary to the intuition, the more varied data is easier to predict, as it can be seen in the results for the inflow speed and viscosity-density models.
-We also believe, that a bigger test set can better estimate the performance of our models.
-This probably also contributes to the worse results for the constant models.
+\begin{table}
+  \begin{center}
+    \begin{tabular}{l|c|c}
+      Model type & Max difference &  Average difference\\
+      \hline
+      Constant & 0.5 &  0.5 \\
+      Inflow speed &  0.5 &  0.5 \\
+      Viscosity-density &  0.5  &  0.5 \\
+    \end{tabular}
+  \end{center}
+  \caption{\label{tab:table-name} Your caption.}
+\end{table}
 
@@
 
+We noticed that across all model types, for some of the predicted frames, certain visual artifacts can occur.
+In some cases those are in the form of a pattern that spans across the image.
+This pattern seem to be recognized by the models as not part of the flow and does not disrupt the structure of the flow.
+Other artifacts, however, can look much more like features of the fluid flow.
+In this case, the network will develop them as it develops the real flow.
+These artifacts accumulate with each predicted frame and become apparent after around the 10.\@ frame.
+In our experiments we managed to minimize the artifacts by making the networks bigger but we never could mitigate them completely.
+
 We again do not explicitly give the correlation between the predicted and real frames.
@@
 
-\section{Conclusion}\label{conclusion}
-
-The results presented in this paper suggest that solving a numerical task trough image-to-image translation is can be a viable approach.
-We showed how conditional GANs can be used to learn the image representations of the solutions of a fluid simulation according to the Navier-Stokes equations.
-We built several models that can generalize different parts of the parameters of the simulations and gave concrete numbers that quantify the results.
-
-We see our work as a preliminary research and we believe that the approach can be further developed and investigated.
-Strategies for improving the models that were considered but not implemented include:
-\begin{itemize}
-\item[$\cdot$] using a LSTM layer in the networks --- our models have the limitation that during training they don't know about the artifact on the images caused by themselves.
-We think a LSTM layer can mitigate this problem.
-\item[$\cdot$] preprocessing the input for and postprocessing the output of the networks --- morphological operations like opening and closing can also be used to minimize the artifacts in the predicted frames.
-\item[$\cdot$] further investigation of the effects of using RGB-images instead of grayscale ones.
-\end{itemize}
-
-\begin{figure}
+\begin{figure}[H]
   \begin{subfigure}{.5\textwidth}
@@
 \end{figure}
+
+\begin{figure}[H]
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_1}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_1}  
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_5}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_5}  
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_10}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_10}  
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_15}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_15}  
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_20}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_20}  
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_25}  
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_25}  
+  \end{subfigure}
+
+  \caption{Example frames generated by the viscosity-density model. The parameters for this particular simulation are $\nu=4.17647, \rho = 0.001, g=1.4$}
+\end{figure}
+
+\section{Conclusion}\label{conclusion}
+
+The results presented in this paper suggest that solving a numerical task trough image-to-image translation is can be a viable approach.
+We showed how conditional GANs can be used to learn the image representations of the solutions of a fluid simulation according to the Navier-Stokes equations.
+We built several models that can generalize different parts of the parameters of the simulations and gave concrete numbers that quantify the results.
+
+We see our work as a preliminary research and we believe that the approach can be further developed and investigated.
+Strategies for improving the models that were considered but not implemented include:
+\begin{itemize}
+\item[$\cdot$] using a LSTM layer in the networks --- our models have the limitation that during training they don't know about the artifact on the images caused by themselves.
+We think a LSTM layer can mitigate this problem.
+\item[$\cdot$] preprocessing the input for and postprocessing the output of the networks --- morphological operations like opening and closing can also be used to minimize the artifacts in the predicted frames.
+\item[$\cdot$] further investigation of the effects of using RGB-images instead of grayscale ones.
+\end{itemize}
 

### 2020-03-26 paper/eccv2020submission.tex
Cleaning up the things a little bit

@@
 
-% INITIAL SUBMISSION - The following two lines are NOT commented
-% CAMERA READY - Comment OUT the following two lines
-% \usepackage{ruler}
-% \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
+\begin{document}
 
-\begin{document}
-% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
-% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
-% \linenumbers
 \pagestyle{headings}
@@
 \def\ECCVSubNumber{100}
-
 \title{Towards Bringing Together Numerical Methods for Partial Differential Equation and Image Processing}
-
-% INITIAL SUBMISSION
-\begin{comment}
+\author{Stanislav Arnaudov, Markus Hoffmann}
 \titlerunning{Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks}
 \authorrunning{Stanislav Arnaudov, Markus Hoffmann}
-\author{Stanislav Arnaudov, Markus Hoffmann}
 \institute{Karlsruhe Institute of Technology,\\Kaiserstrasse 12,76131 Karlsruhe, Germany\\ \url{http://www.kit.edu/english/}}
-\end{comment}
-%******************
 
-% CAMERA READY SUBMISSION
-% \begin{comment}
-\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\author{Stanislav Arnaudoc, Markus Hoffmann }
-%
-\authorrunning{F. Author et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{Karlsruhe Institute of Technology,\\Kaiserstrasse 12,76131 Karlsruhe, Germany\\ \url{http://www.kit.edu/english/}}
-% \end{comment}
-%******************
 \maketitle
@@
 The task usually consists of setting certain initial conditions in a defined space and solving a large mathematical problem for each timestep of the simulation.
-Two central points of interest in CFD are the processing time needed for a simulation and the accuracy of the results.
-It is clear that low processing time and high accuracy are desired but often a certain trade off has to be made.
-With our research we want to propose an innovative method for quickly inspecting the results of a simulation while keeping the accuracy high enough for them to make sense.
+Two central points of interest in CFD are the processing time needed for simulation and the accuracy of the results.
+It is clear that low processing time and high accuracy are desired but often a certain trade-off has to be made.
+With our research, we want to propose an innovative method for quickly inspecting the results of a simulation while keeping the accuracy high enough for them to make sense.
 
-We've concentrated our study on 2D simulations of an incompressible fluid flow around an object in a channel according to the Navier-Stokes equations.
+We've concentrated our study on 2D simulations of incompressible fluid flow around an object in a channel according to the Navier-Stokes equations.
 This setup has three adjustable parameters --- the inflow speed, the viscosity and the density of the fluid.
@@
 These can be conveniently visualized as images over the input space.
-We are mainly interested in those image representations of the timeteps of the simulation.
+We are mainly interested in those image representations of the timesteps of the simulation.
 We call the image representations of the timesteps ``frames'' of the simulation.
-The sequence of this frames show how the flow develops over the course of the simulation.
+The sequence of these frames shows how the flow develops throughout the simulation.
 
 Classical methods for performing such simulations are based on partial differential equations (PDEs) solvers.
-The simulation setup is first formalized as a mathematical model in the form of a time dependent differential equation.
-In itself this equation is then transformed and brought into a suitable for solving form.
+The simulation setup is first formalized as a mathematical model in the form of a time-dependent differential equation.
+In itself, this equation is then transformed and brought into a suitable for solving form.
 A common technique is the finite difference method (FDM).
 This can provide accurate results at the cost of large computational time.
-The generated results are in form of raw numbers representing the velocities and pressure fields which have to be visualized separately.
+The generated results are in the form of raw numbers representing the velocities and pressure fields which have to be visualized separately.
 Our method aims to generate straight the visualizations while needing much lower computational time.
@@
 In recent years there has been a large interest in neural networks and their capabilities.
-Convolutional Neural Networks (CNNs) in particular have been successfully applied in a wide variety of contexts and having proven to be a valuable tools.
-One of the major fields where the performance of CNNs is clearly recognized is image processing.
+Convolutional Neural Networks (CNNs) in particular have been successfully applied in a wide variety of contexts and have proven to be a valuable tool.
+One of the major fields where the performance of CNNs is recognized is image processing.
 A lot of research has shown how CNNs can achieve state-of-the-art performance in tasks like image classification, image segmentation of image-to-image mapping.
-With our research we try to tie CFD and CNNs together and show how image processing approaches can be applied to performing numerical simulations.
+With our research, we try to tie CFD and CNNs together and show how image processing approaches can be applied to performing numerical simulations.
 
-In our research we want to investigate how a CNN can be used in order generate an image of the simulation in interest.
+In our work, we want to investigate how CNN can be used to generate an image of the simulation in interest.
 We build models that take an image from the previous timestep as an input and transform it into an image for the next timestep.
 The built CNNs can also take certain parameters of the simulation and transform the image in accordance with these parameters.
-With this approach we are trying to transform the numerical task of calculating a timestep of a simulation into an image processing task.
+With this approach, we are trying to transform the numerical task of calculating a timestep of simulation into an image processing task.
 
 We try to apply the approach of [pix2pix] in our work.
-In recent years GAN show impressive results in image generation.
-Conditional GANs (cGANs) extend this capabilities of the generator network and allow it to learn image-to-image translation tasks.
+In recent years GANs show impressive results in image generation.
+Conditional GANs (cGANs) extend these capabilities of the generator network and allow it to learn image-to-image translation tasks.
 We wanted to show that conditional GANs can be used in the context of numerical simulations.
@@
 
-The goal of our research is to see to what extend the described approach is viable.
+The goal of our research is to see to what extent the described approach is viable.
 We achieve that by investigating how a cGANs generalizes the different parameters of the investigated simulation.
-Two subsets of the parameters are defined --- fluid parameters (viscosity and density) and inflow speed of the fluid.
-For each of these two subsets we train a separate models and evaluate their performance in different use cases.
+Two subsets of the parameters are defined --- fluid parameters (viscosity and density) and the inflow speed of the fluid.
+For each of these two subsets, we train separate models and evaluate their performance in different use cases.
 A baseline model that does not take parameters into account is also built.
@@
 Firstly, as the output of the network is meant for a human observer, we evaluate the generated images based on their perceived fidelity.
-Secondly, as the networks tries to model a numerical task, we also compare the real and generated images in an objective manner by measuring the actual differences between them.
+Secondly, as the networks try to model a numerical task, we also compare the real and generated images objectively by measuring the actual differences between them.
 
@@
 On the other side, we also want to see how the inaccuracies in the predicted images can accumulate over time.
-Hence also evaluate the models by recursive application where the output of the network is used again as an input for certain amount of timesteps.
+Hence also evaluate the models by recursive application where the output of the network is used again as an input for a certain amount of timesteps.
 More details about the evaluations are given in \refsec{eval}.
@@
 Lastly, we briefly want to motivate why we propose exactly this approach.
-Images represent a well defined input space as every pixel can take limited range of values --- $[0, 255]$.
+Images represent a well-defined input space as every pixel can take a limited range of values --- $[0, 255]$.
 This makes the handling of data in image form convenient.
-Our assumption was that a neural network can process the information in this from more easily.
-Furthermore, convolutional neural networks are well established models for preforming image processing tasks.
-We were interested how a numerical task can be turn into an image processing task as in certain situations, the image result has the priority.
+We assumed that a neural network can process the information in this form more easily.
+Furthermore, convolutional neural networks are well-established models for performing image processing tasks.
+We were interested in how a numerical task can be turned into an image processing task as in certain situations, the image result has the priority.
 We also think that the image processing can be done much quicker in a more optimal way.
@@
 The task is to build a network that can predict the next frame of the simulation based on the previous one.
-Each frame represents a timestep of the simulation and consists of a three channel image.
+Each frame represents a time step of the simulation and consists of a three-channel image.
 Two of the channels encode the velocity fields in both directions and the third channel is the pressure field of the fluid.
@@
 \end{list}
-By evaluating each models we want to see how a network can generalize each of the parameter subsets and to what extent
+By evaluating each model we want to see how a network can generalize each of the parameter subsets and to what extent
 
@@
 \emph{To study the performance of conditional GANs on generating frames of the concrete simulation we generated the training data ourselves.
-In what follows we give details about the process.} The training data was generated by performing numerous simulations of an incompressible fluid flow around a rectangular object in a channel.
+In what follows we give details about the process.} The training data was generated by performing numerous simulations of incompressible fluid flow around a rectangular object in a channel.
 The simulations were modeled according to the Navier-Stokes equations for incompressible flow.
 Because we are interested in the image representations of the simulations, we are dealing only with the 2D case.
-There are several boundary conditions that describe the simulation setup:
+Several boundary conditions describe the simulation setup:
 \begin{list}{$\circ$}{}
@@
 \item[$\cdot$] Outflow condition on the right side of the channel
-\item[$\cdot$] No slip condition on bottom and top side of the channel as well as the sides of the object.
+\item[$\cdot$] No-slip condition on the bottom and top side of the channel as well as the sides of the object.
 \end{list}
@@
 The viscosity was in the range of \ldots with a step of \ldots and the density was in the range of \ldots with a step of \ldots.
-We used the product of the two parameter ranges to perform simulations with all of the possible combinations between the two parameters.
+We used the product of the two-parameter ranges to perform simulations with all of the possible combinations between the two parameters.
 \end{list}
 
-The choice of the concrete values for the parameters is deliberate.
+The choice of concrete values for the parameters is deliberate.
 All of the values are chosen so that the Reynolds number of the simulations in the range of [90, 450].
@@
 The simulations were performed numerically by solving the differential equation describing the flow --- the Navier-Stokes equation.
-This was done with a numerical solver library --- \emph{HiFlow} [] ---  that works on the base of Finite element method.
+This was done with a numerical solver library --- \emph{HiFlow} [] ---  that works on the base of the Finite element method.
 The solver supports parallelization with MPI and OpenMP and we used 12 MPI processes to run each simulation.
-For all of the simulations the timestep for of solver was set to $0.035$ seconds.
-This means the a single timestep of the simulations corresponds to a $0.035$ seconds of physical time.
+For all of the simulations, the timestep for of solver was set to $0.035$ seconds.
+This means a single time step of the simulations corresponds to a $0.035$ seconds of physical time.
 
 The numerical solver on itself cannot be used to render the simulation results to images.
-For this reason we used \emph{ParaView} to load the simulation data and exported it as a sequence of images in PNG format.
+For this reason, we used \emph{ParaView} to load the simulation data and exported it as a sequence of images in PNG format.
 We opted out for using grayscale images as early experiments with RGB-images did not deliver satisfying results.
@@
 Each frame of the simulation was exported as three separate grayscale images.
-The images were finally cropped to select a subset of the space that contains the object and the space behind it.
+The images were finally cropped to select a subset of the space that contains the object and space behind it.
 
-Because the number of simulations in each set is different, we also generated different number of images per simulation based on the corresponding set.
+Because the number of simulations in each set is different, we also generated a different number of images per simulation based on the corresponding set.
 For the constant dataset, we rendered 1904 frames of the simulation (66 seconds of simulated physical time).
 For the inflow speed dataset --- overall 10050 frames coming from the 40 simulations (335 frames per simulation for 12 seconds of simulated physical time).
-For the viscosity-density model --- overall 104328 frames from 334 simulation (322 frames per simulation for 11 seconds of simulated physical time).
-Even though the simulation in the different datasets represent different time intervals, they are all long enough to develop the flow patterns that we are interested in.
+For the viscosity-density model --- overall 104328 frames from 334 simulations (322 frames per simulation for 11 seconds of simulated physical time).
+Even though the simulations in the different datasets represent different time intervals, they are all long enough to develop the flow patterns that we are interested in.
 
-After all images were generated, a test-train split was created for each of the datasets The split for the inflow speed and viscosity-density sets were done manually.
+After all of the images were generated, a test-train split was created for each of the datasets The split for the inflow speed and viscosity-density sets were done manually.
 For the inflow speed set, we selected every fourth simulation to be part of the test set and for the viscosity-density set --- every 25th.
@@
 The split for the constant dataset was done at random.
-All of the splits result in a 80\% of the data being used for training and the rest for testing.
+All of the splits result in  80\% of the data being used for training and the rest for testing.
 It is important to note that all of the images in the test sets come from simulations with parameters that are not found for the simulations in the training sets.
@@
 Conditional GANs also feed an input image $x$ to the generator, $G: x,z \rightarrow y$.
-Pix2Pix suggests that in certain cases the usage of $z$ can be usefully but we decided not to include for out generator as we want a deterministic network.
+Pix2Pix suggests that in certain cases the usage of $z$ can be usefully but we decided not to include for our generator as we want a deterministic network.
 
@@
 The network uses blocks of layers of the from convolution-normalization-ReLu.
-The encoder-decoder first downsamples the input till a bottleneck layer is reached and what follows is a upsampling to the original size of the input image.
+The encoder-decoder first downsamples the input till a bottleneck layer is reached and what follows is an upsampling to the original size of the input image.
 
-For the discriminator we follow the method of pix2pix and we use their PatchGAN.\@ This is a convolutional network that examines only patches of the input.
-It tires to guess if each patch is from real or generated image.
-We use patches of size $70\times 70$ pixels.
+For the discriminator, we follow the method of pix2pix and we use their PatchGAN.\@ This is a convolutional network that examines only patches of the input.
+It tries to guess if each patch is from a real or generated image.
+We use patches of size $256\times 256$ pixels.
 
@@
 We then apply random crops as well as add random noise to each channel of the images.
-We do this to force the generator to learn actual features of the simulation and make over-fitting harder.
+We do this to force the generator to learn the actual features of the simulation and make over-fitting harder.
 Before the input images are fed into the networks, we also multiply them with a mask of the object in the channel.
 This is an image that has zero value in the area where the object is located and one for every other location.
-The multiplication with the mask results in an input image with values of zero in the are of the object.
+The multiplication with the mask results in an input image with values of zero in the area of the object.
 The object mask itself is also given as an input to the generator network.
@@
 Two of the models also take certain simulation parameters as inputs.
-In all cases the parameters are real values.
-In order for the network to be able to use them as part of the input, we transform these values in a constant single channel images with a value equal to the one of the parameter.
+In all cases, the parameters are real values.
+In order for the network to be able to use them as part of the input, we transform these values in constant single-channel images with a value equal to one of the parameters.
 This means that for each simulation parameter there is an extra channel in the for the generator network.
@@
 
-For the training procedure we follow the standard approach proposed by [].
-With each mini-batch we first optimize the discriminator and then the generator with the discussed objectives.
+For the training procedure, we follow the standard approach proposed by [].
+With each mini-batch, we first optimize the discriminator and then the generator with the discussed objectives.
 We use Stochastic Gradient Descent [] with the Adam optimizer with a learning rate of $0.0002$ and momentum parameters $\beta_1=0.9$ and $\beta_2=0.999$.
@@
 
-All of the models were trained and evaluated on a single Nvidia GTX 980Ti GPU.\@ The implementation of the models was done in the PyTorch python library for machine leaning.
+All of the models were trained and evaluated on a single Nvidia GTX 980Ti GPU.\@ The implementation of the models was done in the PyTorch python library for machine learning.
 
 \section{Evaluation}\label{eval}
-
 \noindent\textbf{Evaluation Metrics:} When it comes to the evaluation, we have two separate views of the results generated by the models.
 
-On one hand, we are dealing with image data that is meant to be perceived by human observer.
+On one hand, we are dealing with image data that is meant to be perceived by a human observer.
 This implies that full accuracy is not essential and therefore we place the importance on the perceived qualities of the results.
 This makes sense as in our case a human is concerned with the general development of the simulation over time.
-Under those consideration have chose appropriate metrics to compare the predicted simulation frames with the real ones.
-In this aspect, the first of the metrics that we have chose is Peak Signal to Noise Ratio (PSNR).
-It is related top the mean secured error (MSE) and it's given by
+Under those considerations have chosen appropriate metrics to compare the predicted simulation frames with the real ones.
+In this aspect, the first of the metrics is Peak Signal to Noise Ratio (PSNR).
+It is related to the mean secured error (MSE) and it's given by
 \begin{equation}
@@
 PSNR is measured in decibel (dB) and it is a common metric used to evaluate lossy compression algorithms.
-It measures the difference between original and reconstructed image and considers the fidelity of the reconstruction.
+It measures the difference between the original and reconstructed images and considers the fidelity of the reconstruction.
 This makes the metric suitable in our case.
@@
 We think that if the predicted images differ only in a factor from the real ones, the models can accurately capture the relative difference between the pixels of the target image.
-For this reason we opted for also evaluating the results through correlation.
+For this reason, we opted for also evaluating the results through correlation.
 
-On the other hand, as we are dealing with a numerical task, we also wanted to evaluate the results in a more object manner.
+On the other hand, as we are dealing with a numerical task, we also wanted to evaluate the results more objectively.
 Classical solvers are evaluated in terms of the actual differences between the real and generated result and not the perceived differences.
@@
 We calculated them based on differences between the corresponding pixels of the predicted and the real simulation frame.
-Both metrics are then averaged across the test set and are given in absolute values.
+Both metrics are then averaged across the test set and are given in perceptual values.
 The evaluation with these metrics should represent how well our models perform the simulation in the context of a CFD system.
@@
 \noindent\textbf{Details Evaluation:}
-\emph{In this subsection we want to give several details on the training and evaluating approach}
+\emph{In this subsection, we want to give several details on the training and evaluating approach}
 \begin{itemize}
@@
 We report the results of each run and give them in a form of error plots or explicitly give the variance of all runs.
-\item[$\cdot$] All of the reported results of for the individual runs are averaged across the simulation frames in the training sets.
-\item[$\cdot$] While performing the experiments, we did not tweak the hyper parameters of the models excessively.
-We did, however, tried several sets of hyper parameters until the models achieved satisfactory results.
-The exact hyper parameters are given in []
+\item[$\cdot$] All of the reported results for the individual runs are averaged across the simulation frames in the training sets.
+\item[$\cdot$] While performing the experiments, we did not tweak the hyperparameters of the models excessively.
+We did, however, tried several sets of hyperparameters until the models achieved satisfactory results.
+The exact hyperparameters are given in \refapp{app1}.
 \end{itemize}
@@
 The effects of the usage of the pressure field can be seen in the variance of the results.
-The pressure field has the potential to make the models better but in some runs it can also make them worse.
-We believe this is the case because the pressure fields increases the complexity of the data but it also carries information about the simulation that can be useful for the networks.
+The pressure field has the potential to make the models better but in some runs, it can also make them worse.
+We believe this is the case because the pressure fields increase the complexity of the data but it also carries information about the simulation that can be useful for the networks.
 
@@
 Contrary to the intuition, the more varied data is easier to predict, as it can be seen in the results for the inflow speed and viscosity-density models.
-We also believe, that a bigger test set can better estimate the performance of our models.
+We also believe that a bigger test set can better estimate the performance of our models.
 This probably also contributes to the worse results for the constant models.
@@
   \begin{center}
-    \begin{tabular}{l|c|c}
-      Model type & Max difference &  Average difference\\
+    \begin{tabular}{lcc|cc}
       \hline
-      Constant & 0.5 &  0.5 \\
-      Inflow speed &  0.5 &  0.5 \\
-      Viscosity-density &  0.5  &  0.5 \\
+      \hline
+      Model type & \multicolumn{2}{c|}{\underline{Max difference}}  &  \multicolumn{2}{c}{\underline{Average difference}}\\
+      \multicolumn{3}{c|}{}&&\\
+                 & With pr. & without pr.  &  With pr.& without pr.\\
+      \hline
+      Constant          &  14.6(3.89)&44.0(3.1e+02)&0.599(0.0818)&0.721(0.294)  \\
+
+      Inflow speed      &  32.2(0.297)&45.7(1.47)&0.546(0.00217)&0.929(0.00533) \\
+
+      Viscosity-density &  57.0(1.8e+03)&14.7(7.04)&13.8(1.8e+02)&0.374(0.00824) \\
     \end{tabular}
@@
 \noindent\textbf{Recursive Application Performance:}
-With this evaluation case we want to see how our models handle recursive application. That is, the output of the network is used again as an input for the prediction of the next simulation frame.
+With this evaluation case, we want to see how our models handle recursive application. That is, the output of the network is used again as an input for the prediction of the next simulation frame.
 
-For each recursive evaluation we generate 40 frames of the corresponding simulation.
+For each recursive evaluation, we generate 40 frames of the corresponding simulation.
 We did not in any was post-processed the output of the networks before feeding it as an input.
@@
 
-In our experiments, we performed several recursive evaluation for each simulation while starting at frames with different index.
+In our experiments, we performed several recursive evaluations for each simulation while starting at frames with different indexes.
 We wanted to see how a different starting point in the simulation can affect the frames predicted by the models.
@@
 [fig] presents the results of the recursive application.
-During the evaluation we noticed that the models can more accurately predict a simulation when the starting frame is further in the simulation.
+During the evaluation, we noticed that the models can more accurately predict a simulation when the starting frame is further in the simulation.
 That is, its index relative to the first frame is higher.
@@
 
-For the inflow speed model we present the results from three different simulations in [fig].
+For the inflow speed model, we present the results from three different simulations in [fig].
 We can see the same trend that predicting frames with smaller index is harder.
@@
 We noticed that across all model types, for some of the predicted frames, certain visual artifacts can occur.
-In some cases those are in the form of a pattern that spans across the image.
-This pattern seem to be recognized by the models as not part of the flow and does not disrupt the structure of the flow.
+In some cases, those are in the form of a pattern that spans across the image.
+This pattern seems to be recognized by the models as not part of the flow and does not disrupt the structure of the flow.
 Other artifacts, however, can look much more like features of the fluid flow.
@@
 These artifacts accumulate with each predicted frame and become apparent after around the 10.\@ frame.
-In our experiments we managed to minimize the artifacts by making the networks bigger but we never could mitigate them completely.
+In our experiments, we managed to minimize the artifacts by making the networks bigger but we never could mitigate them completely.
 
 We again do not explicitly give the correlation between the predicted and real frames.
-In all cases the correlation stayed very close to $1$ and varied in the range $[0.98, 0.99998]$.
+In all cases, the correlation stayed very close to $1$ and varied in the range $[0.98, 0.99998]$.
 The CFD-metrics are summarized in [table].
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{lcc|cc}
+      \hline
+      \hline
+      Model type & \multicolumn{2}{c|}{\underline{Max difference}}  &  \multicolumn{2}{c}{\underline{Average difference}}\\
+      \multicolumn{3}{c|}{}&&\\
+                 & With pr. & without pr.  &  With pr.& without pr.\\
+      \hline
+      Constant          &  14.6(3.89)&44.0(3.1e+02)&0.599(0.0818)&0.721(0.294)  \\
+
+      Inflow speed      &  32.2(0.297)&45.7(1.47)&0.546(0.00217)&0.929(0.00533) \\
+
+      Viscosity-density &  57.0(1.8e+03)&14.7(7.04)&13.8(1.8e+02)&0.374(0.00824) \\
+    \end{tabular}
+  \end{center}
+  \caption{\label{tab:table-name} Your caption.}
+\end{table}
 
@@
 \section{Conclusion}\label{conclusion}
-
 The results presented in this paper suggest that solving a numerical task trough image-to-image translation is can be a viable approach.
@@
 
-We see our work as a preliminary research and we believe that the approach can be further developed and investigated.
+We see our work as preliminary research and we believe that the approach can be further developed and investigated.
 Strategies for improving the models that were considered but not implemented include:
 \begin{itemize}
-\item[$\cdot$] using a LSTM layer in the networks --- our models have the limitation that during training they don't know about the artifact on the images caused by themselves.
-We think a LSTM layer can mitigate this problem.
+\item[$\cdot$] using an LSTM [] layer in the networks --- our models have the limitation that during training they don't know about the artifact on the images caused by themselves.
+We think an LSTM layer can mitigate this problem.
 \item[$\cdot$] preprocessing the input for and postprocessing the output of the networks --- morphological operations like opening and closing can also be used to minimize the artifacts in the predicted frames.
@@
 \section{Networks architectures and hyperparameters}
-\emph{Here we give the exact details on the architectures of the used networks.}
-The code for all of the models and experiments can be found at \url{https://github.com/palikar/flow_predict}.
+\label{app1}
+\emph{Here we give the exact details on the architectures of the used networks.} The code for all of the models and experiments can be found at \url{https://github.com/palikar/flow_predict}.
 
@@
 We will denote a Convolution-BatchNorm-ReLU block with $k$ filters with $Ck$ and Convolution-BatchNorm-Dropout-ReLU with $k$ filters $CDk$.
-The dropout rate for each dropout layers is 50\%.
+The dropout rate for each dropout layer is 50\%.
 All convolutions use $4\times4$ filters applied with a stride of $2$.
@@
 All model types use 6 layer encoder and decoder.
-The model types differ only in the amount of filters that they have in the blocks.
-As we use the U-Net architecture, the there are also skip connections between each block $i$ in the encoder and the block $n-i$ in the decoder where $n$ is the total number of blocks in the network.
-The skip connections concatenate the results the both blocks $i$ and $i-i$.
+The model types differ only in the number of filters that they have in the blocks.
+As we use the U-Net architecture, there are also skip connections between each block $i$ in the encoder and the block $n-i$ in the decoder where $n$ is the total number of blocks in the network.
+The skip connections concatenate the results both blocks $i$ and $i-i$.
 
@@
 The ReLUs in the encoders are leaky (slope of $0.2$) and those in the decoders are not.
-At the end of each decoder there is also a convolution layer that maps to the final channel count of the output.
+At the end of each decoder, there is also a convolution layer that maps to the final channel count of the output.
 This final convolution is followed by a $\tanh$-function.
@@
 All of the ReLUs are leaky (slope of $0.2$).
-Also, a final convolution is applied after the last layers that produced the a dimensional output of the discriminator.
+Also, a final convolution is applied after the last layers that produced the one-dimensional output of the discriminator.
 A sigmoid function is applied after the convolution.
-
 \end{subappendices}

### 2020-03-26 charts/single.py

@@ -13,11 +13,11 @@ def constant_models():
     labels = []
     box_data = []
 
-    data['with'] = [1,1.3,1.5,0.9,1.23,1.32]
-    data['without'] = [1,1.3,1.5,0.9,1.23,1.32]
+    data['with'] = [42.4267183875451 , 43.78148944993617]
+    data['without'] = [37.73239422055144 , 42.99703106930973 , 43.02076006161946]
 
-    box_data.append([1,1.3,1.5,0.9,1.23,1.32])
-    box_data.append([1,1.3,1.5,0.9,1.23,1.32])
+    box_data.append(data['with'])
+    box_data.append(data['without'])
 
     labels.append('with pressure')
     labels.append('without pressure')
@@ -38,10 +38,11 @@ def constant_models():
     plt.gca().spines['top'].set_visible(False)
     plt.gca().spines['right'].set_visible(False)
 
-    plt.ylabel('PSNR')
+    plt.ylabel('PSNR', fontsize=16)
     plt.title('Constant model (single image performance)', fontsize=17)
 
-    plt.show()
+    # plt.show()
+    plt.savefig('single_const_psnr.png')
 
 
 def speed_models():
@@ -50,11 +51,11 @@ def speed_models():
     labels = []
     box_data = []
 
-    data['with'] = [1,1.3,1.5,0.9,1.23,1.32]
-    data['without'] = [1,1.3,1.5,0.9,1.23,1.32]
+    data['with'] = [32.70363132431171 , 32.37544378610233 , 33.22313390003679, 33.80816838419148 , 33.1802077172184 , 33.873630834872216 , 33.95285390084521 ,33.67447951182013 , 33.179886956867975 , 34.17147778053133]
+    data['without'] = [32.038006486935075 , 32.192804717704554 , 32.184300070511554, 32.48270450488618 , 32.311327037629844 , 32.19408204987984 , 32.35434794736937 , 32.15279210676768 , 32.04192581940871 , 32.10279251816919]
 
-    box_data.append([1,1.3,1.5,0.9,1.23,1.32])
-    box_data.append([1,1.3,1.5,0.9,1.23,1.32])
+    box_data.append(data['with'])
+    box_data.append(data['without'])
 
     labels.append('with pressure')
     labels.append('without pressure')
@@ -75,11 +76,12 @@ def speed_models():
     plt.gca().spines['top'].set_visible(False)
     plt.gca().spines['right'].set_visible(False)
 
[…]

### 2020-03-27 paper/eccv2020submission.tex
Adding some of the charts

@@
 A baseline model that does not take parameters into account is also built.
-We give more details on the models in section \refsec{methodology}.
+We give more details on the models in \refsec{methodology}.
 
@@
 The simulation setup has three separate adjustable parameters --- inflow speed $g$, fluid density $\rho$ and fluid viscosity $\nu$.
-\\
+
 We generated three sets of simulations for training the three kinds of models.
@@
 The showed results, however, are representative of the general performance of our models.
-For this section, We also limit ourselves only to models that do use the pressure field of the simulations.
+For this section, we also limit ourselves only to models that do use the pressure field of the simulations.
 
@@
 \begin{itemize}
-\item[$\cdot$] using an LSTM [] layer in the networks --- our models have the limitation that during training they don't know about the artifact on the images caused by themselves.
+\item[$\cdot$] using an LSTM~\cite{lstm} layer in the networks --- our models have the limitation that during training they don't know about the artifact on the images caused by themselves.
 We think an LSTM layer can mitigate this problem.
@@
 
-The architectures are almost entirely based on [pix2pix, 44].
+The architectures are almost entirely based on~\cite{pix2pix} and [44].
 Both the generator and the discriminator networks are comprised of two types of blocks of layers.
@@
 
-This configuration results in a receptive field of $70\times70$.
-This means that for each $70\times70$ region of the input, the discriminator tries to guess if the region is from a real image or from a generated one.
+This configuration results in a receptive field of $256\times256$.
+This means that for each $256\times256$ region of the input, the discriminator tries to guess if the region is from a real image or from a generated one.
 

### 2020-03-27 charts/recursive.py

@@ -11,6 +11,16 @@ plt.rcParams.update({'figure.max_open_warning': 0})
 
 
 def consant_i20():
+
+    data = [
+        [],
+        [],
+        [],
+        [],
+        [],
+        [],
+        [],
+        []]
     
     matplotlib.rc('xtick', labelsize=17)
     matplotlib.rc('ytick', labelsize=17)
@@ -22,7 +32,7 @@ def consant_i20():
     
     plt.figure()
     plt.errorbar(x, y, yerr=yerr, fmt='-o', ecolor='black', mfc='white', mec='black', color='black')
-    plt.gca().spines['top'].setc_visible(False)
+    plt.gca().spines['top'].set_visible(False)
     plt.gca().spines['right'].set_visible(False)
     plt.xlabel('Frame index', fontsize=16)
     plt.ylabel('PSNR', fontsize=16)
@@ -30,20 +40,35 @@ def consant_i20():
     plt.show()
 
 
-
 def consant_i200():
+
     
+    data = [
+        [31.21371553240797,25.774796584766285,22.518287453450174,20.176077597725644,18.325811971986347,16.76595465976897,15.401841299073011,14.162732235021815,13.00164222870023,11.891585384370114,10.823932866015706,9.813458643379192,8.878976175202727,8.033006657415863,7.267624015850677,6.572893473810777,5.943467942891073,5.378433567276048,4.882449089961279,4.454255319783532,4.086808386026957,3.773749000760382,3.50673634754454,3.2804985599423864,3.0872746590487443,2.9225815569964704,2.7797752676214116,2.655375955303315,2.5453923657128064,2.4460625938551948,2.354388451416122,2.26764364660264,2.1822257705234667,2.0965649249374563,2.012240937524123,1.933634289359347,1.864423379003213,1.8060589789138428,1.7578192837848823,1.7186392200410952],
[…]

### 2020-03-27 charts/single_table.py

@@ -1,0 +1,65 @@
+#!/usr/bin/env python
+import matplotlib
+import matplotlib.pyplot as plt
+import os
+import sys
+
+import numpy as np
+
+
+
+
+
+
+def main():
+
+    
+    p_const_avrg = np.array([1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102 ,])
+    p_const_max = np.array([16.123661417322836 , 16.308669291338582 , 11.390377952755905 , 14.41744881889764 ])
+    np_const_avrg = np.array([0.32077165354330706 , 0.5521338582677168 , 0.3627007874015747 , 1.6469842519685036])
+    np_const_max = np.array([30.49359055118111 , 29.123480314960634 , 75.47813385826771 , 41.04614173228347])
+    
+    p_speed_avrg = np.array([0.5161387225548902 , 0.5086556886227545 , 0.534815369261477 , 0.6252145708582835])
+    p_speed_max = np.array([31.709387225548905 , 32.00352095808383 , 31.838751497005987 , 33.08689720558882])
+    np_speed_avrg = np.array([0.8764880239520958 , 0.8413493013972057 , 1.0208942115768462 , 0.97850499001996 ])
+    np_speed_max = np.array([46.87356187624751 , 43.75898702594811 , 46.5552864271457 , 45.54569660678643])
+
+    p_fluid_avrg = np.array([0.41133193702152243 , 27.280076848998455])
+    p_fluid_max = np.array([14.537741441571573 , 99.45428139445299])
+    np_fluid_avrg = np.array([0.42235304314329736 , 0.5787415254237288 , 0.33393451463790447 , 0.30568432203389834 , 0.3313731041456016 , 0.3340954788386537 , 0.31267950693374424 ])
+    np_fluid_max = np.array([16.124258474576273 , 14.990394260400619 , 13.283522534668721 , 19.36700442989214 , 11.396986710963457 , 11.501868842987145 , 16.20593278120185 ])
+
+    print("{:.3}({:.3})&{:.3}({:.3})&{:.3}({:.3})&{:.3}({:.3})".format(
+        np.mean(p_const_max),
+        np.var(p_const_max),
+        np.mean(np_const_max),
+        np.var(np_const_max),
+        np.mean(p_const_avrg),
+        np.var(p_const_avrg),
+        np.mean(np_const_avrg),
[…]

### 2020-03-27 project/evaluate.py

@@ -79,7 +79,7 @@ class Evaluator:
 
     def recusive_application_performance(self, net, dataset, split_point, samples=20):
         print('===> Evaluating performance of recursive application')
-
+        
         path = os.path.join(config['output_dir'], self.output_name, 'recursive')
         mkdir(path)
 

### 2020-03-29 paper/eccv2020submission.tex
Adding a whole bunch of charts

@@
 \usepackage{float}
-\newcommand{\reffig}[1]{\hyperref[#1]{Figure \ref*{#1}}}
-\newcommand{\refsec}[1]{\hyperref[#1]{Section \ref*{#1}}}
-\newcommand{\reftab}[1]{\hyperref[#1]{Table \ref*{#1}}}
-\newcommand{\refapp}[1]{\hyperref[#1]{Appendix \ref*{#1}}}
+\newcommand{\reffig}[1]{\hyperref[#1]{Figure~\ref*{#1}}}
+\newcommand{\refsec}[1]{\hyperref[#1]{Section~\ref*{#1}}}
+\newcommand{\reftab}[1]{\hyperref[#1]{Table~\ref*{#1}}}
+\newcommand{\refapp}[1]{\hyperref[#1]{Appendix~\ref*{#1}}}
+\newcommand{\thickhline}{%
+    \noalign {\ifnum 0=`}\fi \hrule height 1pt
+    \futurelet \reserved@a \@xhline
+}
 \DeclareMathOperator*{\argminA}{arg\,min}
@@
 \pagestyle{headings}
-\mainmatter
-\def\ECCVSubNumber{100}
+\mainmatter\def\ECCVSubNumber{100}
 \title{Towards Bringing Together Numerical Methods for Partial Differential Equation and Image Processing}
@@
 The simulations were performed numerically by solving the differential equation describing the flow --- the Navier-Stokes equation.
-This was done with a numerical solver library --- \emph{HiFlow} [] ---  that works on the base of the Finite element method.
+This was done with a numerical solver library --- \emph{HiFlow}~\cite{gawlok2017} ---  that works on the base of the Finite element method.
 The solver supports parallelization with MPI and OpenMP and we used 12 MPI processes to run each simulation.
@@
 \subsection{Training approach and networks details}
-We base our generative models almost entirely on [pix2pix].
+We base our generative models almost entirely on~\cite{pix2pix}.
 We use the conditional GAN approach to train a generator network that can perform image-to-image translation.
-As explained in [], the traditional GAN method uses a random vector $z$ as in input to the generator network $G$ to generate output $y$, $G:z \rightarrow y$.
-Conditional GANs also feed an input image $x$ to the generator, $G: x,z \rightarrow y$.
-Pix2Pix suggests that in certain cases the usage of $z$ can be usefully but we decided not to include for our generator as we want a deterministic network.
+As explained in~\cite{pix2pix}, the traditional GAN method uses a random vector $z$ as in input to the generator network $G$ to generate output $y$, $G:z \rightarrow y$.
+Conditional GANs also feed an input image $x$ to the generator, $G: x,z \rightarrow y$.~\cite{pix2pix} and~\cite{wang2016} suggest that in certain cases the usage of $z$ can be usefully but we decided not to include for our generator as we want a deterministic network.
 
@@
 In contrast to unconditional GANs, both the generator and the discriminator network have access to the input image.
-The objective is divided by two to slow down the training of the discriminator relative to the generator as suggested by [].
+The objective is divided by two to slow down the training of the discriminator relative to the generator as suggested by~\cite{pix2pix}.
 
 The objective for the generator network is comprised of two parts --- the value of the discriminator as well as a L1 distance loss between the target and the predicted images.
-According to [] the L1 loss promotes less blurring and captures the low frequency details of the images.
+According to~\cite{pix2pix} the L1 loss promotes less blurring and captures the low frequency details of the images.
 The L1 loss is given by:
@@
 
-\noindent\textbf{Networks Architectures:} For our generator we use the U-Net variant proposed in pix2pix.
-It is a standard encoder-decoder model that skip connections between parts of the encoder and the decoder.
+\noindent\textbf{Networks Architectures:} For our generator we use the U-Net~\cite{ronneberger2015} variant proposed in~\cite{pix2pix}.
+It is a standard encoder-decoder~\cite{hinton2006} model that skip connections between parts of the encoder and the decoder.
 We also experimented with ResNet based generator but the results were not satisfactory.
@@
 
-For the training procedure, we follow the standard approach proposed by [].
+For the training procedure, we follow the standard approach proposed by~\cite{goodfellow2014}.
 With each mini-batch, we first optimize the discriminator and then the generator with the discussed objectives.
-We use Stochastic Gradient Descent [] with the Adam optimizer with a learning rate of $0.0002$ and momentum parameters $\beta_1=0.9$ and $\beta_2=0.999$.
-
+We use Stochastic Gradient Descent~\cite{kiefer1952} with the Adam optimizer~\cite{kingma2014} with a learning rate of $0.0002$ and momentum parameters $\beta_1=0.9$ and $\beta_2=0.999$.
 The used batch size for the constant and inflow speed models was set to 3 and for the viscosity-density models to 4.
-Those are relatively small numbers for batch sizes but [] suggests that the UNet architecture benefits from small batches in image-to-image translation problems.
+Those are relatively small numbers for batch sizes but~\cite{pix2pix} suggests that the U-Net architecture benefits from small batches in image-to-image translation problems.
 Our experiments confirmed this.
@@
 
-[Fig] shows the results of the different model types with respect to PSNR.\@ Examples of the predicted images are given in [fig].
+\reffig{fig:single_psnr} shows the results of the different model types with respect to PSNR.\@ Examples of the predicted images are given in \reffig{fig:single_images}.
 We can clearly see that the predicted images are almost identical to the real ones.
@@
 
-[Table] summarizes the results of the evaluation with the average and maximal difference metrics.
+\reftab{tab:single} summarizes the results of the evaluation with the average and maximal difference metrics.
 
@@
     \includegraphics[width=1\linewidth]{imgs/single_constant_x}
-
   \end{subfigure}
@@
 The lower half is the prediction of the model.
-In the left column, the images are from the x-velocity fie4ld of the simulation and in the right --- form the y-velocity field.}
+In the left column, the images are from the x-velocity fie4ld of the simulation and in the right --- form the y-velocity field.}\label{fig:single_images}
+\end{figure}
+
+\begin{figure}
+  \begin{subfigure}{.3\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/single_const_psnr}
+  \end{subfigure}
+  \begin{subfigure}{.3\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/single_fluid_psnr}
+  \end{subfigure}
+  \begin{subfigure}{.3\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/single_speed_psnr}
+  \end{subfigure}
+
+  \caption{}\label{fig:single_psnr}
 \end{figure}
@@
     \begin{tabular}{lcc|cc}
+
+      \textbf{Model type} & \multicolumn{2}{c|}{\textbf{Max difference}}  &  \multicolumn{2}{c}{\textbf{Average difference}}\\
       \hline 
-      \hline
-      Model type & \multicolumn{2}{c|}{\underline{Max difference}}  &  \multicolumn{2}{c}{\underline{Average difference}}\\
       \multicolumn{3}{c|}{}&&\\
-                 & With pr. & without pr.  &  With pr.& without pr.\\
-      \hline
+                 & \underline{With pr.} & \underline{without pr.}  &  \underline{With pr}.& \underline{without pr.}\\
+
       Constant          &  14.6(3.89)&44.0(3.1e+02)&0.599(0.0818)&0.721(0.294)  \\
@@
   \end{center}
-  \caption{\label{tab:table-name} Your caption.}
+  \caption{Your caption.}\label{tab:single}
 \end{table}
@@
 The constant model is evaluated with a single simulation --- the one it was trained with.
-[fig] presents the results of the recursive application.
+\reffig{fig:rec_const_psnr} presents the results of the recursive application.
 During the evaluation, we noticed that the models can more accurately predict a simulation when the starting frame is further in the simulation.
 That is, its index relative to the first frame is higher.
-The plots for the constant model in [fig] illustrate this.
+The plots for the constant model in \reffig{fig:rec_const_psnr} illustrate this.
 
-For the inflow speed model, we present the results from three different simulations in [fig].
+For the inflow speed model, we present the results from two different simulations in \reffig{fig:rec_speed_psnr}.
 We can see the same trend that predicting frames with smaller index is harder.
-We, however, like to note that the networks appear to be handling the parameters properly and adjust the predicted frames accordingly.
-[fig] presents the results of the viscosity-density model.
+We, however, like to note that the networks appear to be handling the parameters properly and adjust the predicted frames accordingly.\reffig{fig:rec_fluid_psnr} presents two simulations of the viscosity-density model.
 
@@
 In all cases, the correlation stayed very close to $1$ and varied in the range $[0.98, 0.99998]$.
-The CFD-metrics are summarized in [table].
-
-\begin{table}
-  \begin{center}
-    \begin{tabular}{lcc|cc}
-      \hline
-      \hline
-      Model type & \multicolumn{2}{c|}{\underline{Max difference}}  &  \multicolumn{2}{c}{\underline{Average difference}}\\
-      \multicolumn{3}{c|}{}&&\\
-                 & With pr. & without pr.  &  With pr.& without pr.\\
-      \hline
-      Constant          &  14.6(3.89)&44.0(3.1e+02)&0.599(0.0818)&0.721(0.294)  \\
-
-      Inflow speed      &  32.2(0.297)&45.7(1.47)&0.546(0.00217)&0.929(0.00533) \\
-
-      Viscosity-density &  57.0(1.8e+03)&14.7(7.04)&13.8(1.8e+02)&0.374(0.00824) \\
-    \end{tabular}
-  \end{center}
-  \caption{\label{tab:table-name} Your caption.}
-\end{table}
+The CFD-metrics are summarized in [].
 
@@
 
-  \caption{These frames are generated by the constant model. The artifacts become apparent after the 10.\@ one.}
+  \caption{These frames are generated by the constant model. The artifacts become apparent after the 10.\@ one.}\label{fig:const_sim}
 \end{figure}
@@
 
-  \caption{Example frames generated by the viscosity-density model. The parameters for this particular simulation are $\nu=4.17647, \rho = 0.001, g=1.4$}
+  \caption{Example frames generated by the viscosity-density model. The parameters for this particular simulation are $\nu=4.17647, \rho = 0.001, g=1.4$}\label{fig:fluid_sim}
+\end{figure}
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{l|cc|cc}
+      \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Simulation}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}  &  \multicolumn{2}{c}{\shortstack{\textbf{Simulation}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}\\
+      \hline 
+                     &\multicolumn{2}{c|}{} &&\\
+                     & {Max difference} & {Average difference}  &  {Max difference} & {Average difference}\\
+      \emph{Frame 1}       &35    &35     &35    &35\\
+      \emph{Frame 5}       &35    &35     &35    &35\\
+      \emph{Frame 10}      &35    &35     &35    &35\\
+      \emph{Frame 15}      &35    &35     &35    &35\\
+      \emph{Frame 20}      &35    &35     &35    &35\\
+      \emph{Frame 25}      &35    &35     &35    &35\\
+      \emph{Frame 30}      &35    &35     &35    &35\\
+      \emph{Frame 35}      &35    &35     &35    &35\\
+      \emph{Frame 40}      &35    &35     &35    &35\\
+
+    \end{tabular}
+  \end{center}
+  \caption{Your caption.}\label{tab:recursive}
+\end{table}
+
+\begin{figure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/constant_i10}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/constant_i190}
+  \end{subfigure}  
+  \caption{}\label{fig:rec_const_psnr}
+\end{figure}
+
+\begin{figure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/inflow_i10}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/inflow_i1436}
+  \end{subfigure}
+
+  \begin{center}
+    Simulation
+  \end{center}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/inflow_39_s0}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/inflow_39_s120}
+  \end{subfigure}
+
+  \begin{center}
+    Simulation
+  \end{center}
+
+  \caption{}\label{fig:rec_speed_psnr}
+\end{figure}
+
+\begin{figure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/fluid_25_s0}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/fluid_25_s120}
+  \end{subfigure}
+
+  \begin{center}
+    Simulation
+  \end{center}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/fluid_100_s0}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/fluid_100_s120}
+  \end{subfigure}
+
+  \begin{center}
+    Simulation
+  \end{center}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/fluid_300_s0}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/fluid_300_s120}
+  \end{subfigure}
+
+  \begin{center}
+    Simulation
+  \end{center}
+
+  \caption{}\label{fig:rec_fluid_psnr}
 \end{figure}
@@
 
-\section{Networks architectures and hyperparameters}
-\label{app1}
+\section{Networks architectures and hyperparameters}\label{app1}
 \emph{Here we give the exact details on the architectures of the used networks.} The code for all of the models and experiments can be found at \url{https://github.com/palikar/flow_predict}.
 
-The architectures are almost entirely based on~\cite{pix2pix} and [44].
+The architectures are almost entirely based on~\cite{pix2pix} and~\cite{radford2015}.
 Both the generator and the discriminator networks are comprised of two types of blocks of layers.
@@
 
-% LocalWords:  Convolutional timestep timesteps grayscale cGANs
-% LocalWords:  preprocessing postprocessing
+% LocalWords:  Convolutional timestep timesteps grayscale cGANs GAN
+% LocalWords:  preprocessing postprocessing hyperparameters HiFlow

### 2020-03-29 charts/rec.py

@@ -1,0 +1,34 @@
+#!/usr/bin/env python
+import matplotlib
+import matplotlib.pyplot as plt
+import os
+import sys
+
+import numpy as np
+
+def main():
+
+
+
+    const_avrg = np.array([[1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102, 1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102, 1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102],
+                           [1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102, 1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102, 1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102]])
+
+    const_maxis = np.array([[1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102, 1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102, 1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102],
+                           [1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102, 1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102, 1.0414251968503936 , 0.6457401574803151 , 0.42076377952755895 , 0.2865590551181102]])
+
+
+
+    c_avrg_avrgs = np.mean(const_avrg, axis=0)
+    c_avrg_stds = np.std(const_avrg, axis=0)
+
+    c_max_avrgs = np.mean(const_maxis, axis=0)
+    c_max_stds = np.std(const_maxis, axis=0)
+
+    
+    for i in range(0, 10, 5):
+        print('{:.2}({:.2}) & {:.2}({:.2})'.format(c_avrg_avrgs[i], c_avrg_stds[i], c_max_avrgs[i], c_max_stds[i]))
+    
+    
+
+if __name__ == '__main__':
+    main()

### 2020-03-29 charts/recursive.py

@@ -9,164 +9,374 @@ import numpy as np
 plt.style.use('ggplot')
 plt.rcParams.update({'figure.max_open_warning': 0})
 
+matplotlib.rc('xtick', labelsize=19)
+matplotlib.rc('ytick', labelsize=24)
+matplotlib.rcParams['xtick.labelsize'] = 32
+matplotlib.rcParams['ytick.labelsize'] = 32
+
+
 
 def consant_i20():
-
-    data = [
-        [],
-        [],
-        [],
-        [],
-        [],
-        [],
-        [],
-        []]
     
-    matplotlib.rc('xtick', labelsize=17)
-    matplotlib.rc('ytick', labelsize=17)
+    data = [[ 2.571741192740507,10.109071645898151,10.598509900666894,11.05769828253386,11.436962238663762,11.764233023137926,12.080388590751136,12.30865445082995,12.526633035271825,12.703773594887204,12.834665576078958,12.925021982172344,12.926355726871765,12.964345518817222,12.965563931931746,12.936429627496484,12.936837154978761,12.894988007489577,12.860183667661104,12.842644568269383,12.821734344872597,12.798248090634248,12.77048535148311,12.737879565574165,12.66012943655369,12.62017951549442,12.580577618963162,12.511945445398068,12.462028569797495,12.428131877744256,12.401155471585291,12.351013547133967,12.331495955170862,12.319214386091348,12.308696296984822,12.27669657287942,12.266948006719405,12.260274873657142,12.252365793037008,12.238389279744993 ],[ 2.463828602571298,8.937841161376097,8.92330069625012,8.922498245721052,8.896608165157247,8.872432132961363,8.881102863074364,8.863208306160093,8.877835003764945,8.90000170610554,8.920176569949433,8.933482311404347,8.898200660025479,8.899025251559703,8.879354632465338,8.842699310493444,8.825649315864286,8.77339964020493,8.715918389267804,8.65549022611428,8.577597266134031,8.486227981997585,8.384860468537603,8.277303376991823,8.140925832750934,8.025763973854808,7.908363845128434,7.770024504722145,7.638775457336631,7.513841888767071,7.387788585561564,7.2411362530491585,7.099353712440167,6.949036735006167,6.786142451666263,6.599530503738188,6.414538002011303,6.2269486672062335,6.039429486138564,5.853428407489729 ],[ 2.5400532704557865,9.734245932655572,10.14559448729173,10.5281482606058,10.832679667465236,11.09758273769787,11.34961207021748,11.5191470659
[…]

### 2020-03-29 charts/single.py

@@ -6,6 +6,11 @@ import sys
 plt.style.use('ggplot')
 plt.rcParams.update({'figure.max_open_warning': 0})
 
+matplotlib.rc('xtick', labelsize=19)
+matplotlib.rc('ytick', labelsize=24)
+matplotlib.rcParams['xtick.labelsize'] = 32
+matplotlib.rcParams['ytick.labelsize'] = 32
+
 
 def constant_models():
 
@@ -22,9 +27,6 @@ def constant_models():
     labels.append('with pressure')
     labels.append('without pressure')
 
-    matplotlib.rc('xtick', labelsize=13)
-    matplotlib.rc('ytick', labelsize=17)
-
     plt.figure(figsize=(17, 10))
 
     x = [i for i in range(1, len(data.keys())+1)]
@@ -32,17 +34,17 @@ def constant_models():
     plt.boxplot(box_data, labels=labels)
 
     for (_, times), i  in zip(data.items(), x):
-        plt.scatter([i]*len(times), times, alpha=0.5, linewidths=None)
+        plt.scatter([i]*len(times), times,  s=[90]*len(times), alpha=0.5, linewidths=None)
 
 
     plt.gca().spines['top'].set_visible(False)
     plt.gca().spines['right'].set_visible(False)
 
-    plt.ylabel('PSNR', fontsize=16)
-    plt.title('Constant model (single image performance)', fontsize=17)
+    plt.ylabel('PSNR', fontsize=32)
+    plt.title('Constant model (single image performance)', fontsize=36)
 
     # plt.show()
-    plt.savefig('single_const_psnr.png')
+    plt.savefig('single_const_psnr.eps')
 
 
 def speed_models():
@@ -60,27 +62,26 @@ def speed_models():
     labels.append('with pressure')
     labels.append('without pressure')
 
-    matplotlib.rc('xtick', labelsize=13)
-    matplotlib.rc('ytick', labelsize=17)
-
     plt.figure(figsize=(17, 10))
 
     x = [i for i in range(1, len(data.keys())+1)]
 
+    
     plt.boxplot(box_data, labels=labels)
 
     for (_, times), i  in zip(data.items(), x):
-        plt.scatter([i]*len(times), times, alpha=0.5, linewidths=None)
+        plt.scatter([i]*len(times), times,  s=[90]*len(times), alpha=0.5, linewidths=None)
 
-
+    
     plt.gca().spines['top'].set_visible(False)
[…]

### 2020-03-29 paper/eccv2020submission.tex
Slowly but surely getting there

@@
 The viscosity-density and inflow speed models are evaluated with several simulations with different parameters.
-As it is unpracticed to give the results of the evaluation of each simulation, here we present only several of them.
+As it is impractical to give the results of the evaluation of each simulation, here we present only several of them.
 The showed results, however, are representative of the general performance of our models.
@@
 
-The constant model is evaluated with a single simulation --- the one it was trained with.
-\reffig{fig:rec_const_psnr} presents the results of the recursive application.
+The constant model is evaluated with a single simulation --- the one it was trained with.~\reffig{fig:rec_const_psnr} presents the results of the recursive application.
 During the evaluation, we noticed that the models can more accurately predict a simulation when the starting frame is further in the simulation.
 That is, its index relative to the first frame is higher.
-The plots for the constant model in \reffig{fig:rec_const_psnr} illustrate this.
+The plots for the constant model in~\reffig{fig:rec_const_psnr} illustrate this.
 
-For the inflow speed model, we present the results from two different simulations in \reffig{fig:rec_speed_psnr}.
+For the inflow speed model, we present the results from two different simulations in~\reffig{fig:rec_speed_psnr}.
 We can see the same trend that predicting frames with smaller index is harder.
-We, however, like to note that the networks appear to be handling the parameters properly and adjust the predicted frames accordingly.\reffig{fig:rec_fluid_psnr} presents two simulations of the viscosity-density model.
-
-We noticed that across all model types, for some of the predicted frames, certain visual artifacts can occur.
-In some cases, those are in the form of a pattern that spans across the image.
-This pattern seems to be recognized by the models as not part of the flow and does not disrupt the structure of the flow.
-Other artifacts, however, can look much more like features of the fluid flow.
-In this case, the network will develop them as it develops the real flow.
-These artifacts accumulate with each predicted frame and become apparent after around the 10.\@ frame.
-In our experiments, we managed to minimize the artifacts by making the networks bigger but we never could mitigate them completely.
-
-We again do not explicitly give the correlation between the predicted and real frames.
-In all cases, the correlation stayed very close to $1$ and varied in the range $[0.98, 0.99998]$.
-The CFD-metrics are summarized in [].
-
-\begin{figure}[H]
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_1}
-  \end{subfigure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_1}
-  \end{subfigure}
-
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_5}
-  \end{subfigure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_5}
-  \end{subfigure}
-
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_10}
-  \end{subfigure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_10}
-  \end{subfigure}
-
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_15}
-  \end{subfigure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_15}
-  \end{subfigure}
-
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_20}
-  \end{subfigure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_20}
-  \end{subfigure}
-
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_25}
-  \end{subfigure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_25}
-  \end{subfigure}
-
-  \caption{These frames are generated by the constant model. The artifacts become apparent after the 10.\@ one.}\label{fig:const_sim}
-\end{figure}
-
-\begin{figure}[H]
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_1}
-  \end{subfigure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_1}
-  \end{subfigure}
-
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_5}
-  \end{subfigure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_5}
-  \end{subfigure}
-
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_10}
-  \end{subfigure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_10}
-  \end{subfigure}
-
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_15}
-  \end{subfigure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_15}
-  \end{subfigure}
-
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_20}
-  \end{subfigure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_20}
-  \end{subfigure}
-
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_25}
-  \end{subfigure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_25}
-  \end{subfigure}
-
-  \caption{Example frames generated by the viscosity-density model. The parameters for this particular simulation are $\nu=4.17647, \rho = 0.001, g=1.4$}\label{fig:fluid_sim}
-\end{figure}
-
-\begin{table}
-  \begin{center}
-    \begin{tabular}{l|cc|cc}
-      \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Simulation}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}  &  \multicolumn{2}{c}{\shortstack{\textbf{Simulation}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}\\
-      \hline 
-                     &\multicolumn{2}{c|}{} &&\\
-                     & {Max difference} & {Average difference}  &  {Max difference} & {Average difference}\\
-      \emph{Frame 1}       &35    &35     &35    &35\\
-      \emph{Frame 5}       &35    &35     &35    &35\\
-      \emph{Frame 10}      &35    &35     &35    &35\\
-      \emph{Frame 15}      &35    &35     &35    &35\\
-      \emph{Frame 20}      &35    &35     &35    &35\\
-      \emph{Frame 25}      &35    &35     &35    &35\\
-      \emph{Frame 30}      &35    &35     &35    &35\\
-      \emph{Frame 35}      &35    &35     &35    &35\\
-      \emph{Frame 40}      &35    &35     &35    &35\\
-
-    \end{tabular}
-  \end{center}
-  \caption{Your caption.}\label{tab:recursive}
-\end{table}
+We,x however, like to note that the networks appear to be handling the parameters properly and adjust the predicted frames accordingly.\reffig{fig:rec_fluid_psnr} presents two simulations of the viscosity-density model.
 
@@
 
+We noticed that across all model types, for some of the predicted frames, certain visual artifacts can occur.
+In some cases, those are in the form of a pattern that spans across the image.
+This pattern seems to be recognized by the models as not part of the flow and does not disrupt the structure of the flow.
+Other artifacts, however, can look much more like features of the fluid flow.
+In this case, the network will develop them as it develops the real flow.
+These artifacts accumulate with each predicted frame and become apparent after around the 10.\@ frame.
+In our experiments, we managed to minimize the artifacts by making the networks bigger but we never could mitigate them completely.
+
+We again do not explicitly give the correlation between the predicted and real frames.
+In all cases, the correlation stayed very close to $1$ and varied in the range $[0.98, 0.99998]$.
+The difference-metrics are summarized in~\reftab{tab:recursive_inflow} and~\reftab{tab:recursive_fluid}.
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{l|cc|cc}
+      \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Simulation 8}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}  &  \multicolumn{2}{c}{\shortstack{\textbf{Simulation 39}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}\\
+      \hline 
+                     &\multicolumn{2}{c|}{} & &\\
+                     & {Average difference} & {Max difference}  &  {Max difference} & {Average difference}\\
+      \emph{Frame 1}       &34.27(0.02) & 52.72(0.40)    &35.91(0.02) & 51.76(0.38)   \\
+      \emph{Frame 5}       &33.86(0.11) & 60.41(1.62)    &35.84(0.10) & 53.13(0.54)   \\
+      \emph{Frame 10}      &33.99(0.17) & 66.04(2.16)    &36.01(0.15) & 54.59(1.14)   \\
+      \emph{Frame 15}      &33.80(0.20) & 76.40(3.67)    &35.91(0.20) & 58.90(1.97)   \\
+      \emph{Frame 20}      &34.27(0.22) & 75.39(3.07)    &35.89(0.24) & 62.60(2.94)   \\
+      \emph{Frame 25}      &33.91(0.22) & 83.45(3.06)    &35.93(0.28) & 61.07(2.60)   \\
+      \emph{Frame 30}      &34.13(0.24) & 79.15(2.20)    &35.73(0.33) & 66.69(4.21)   \\
+      \emph{Frame 35}      &34.38(0.23) & 83.52(2.09)    &35.94(0.35) & 65.55(4.18)   \\      
+    \end{tabular}
+  \end{center}
+  \caption{Your caption.}\label{tab:recursive_inflow}
+\end{table}
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{l|cc|cc}
+      \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Simulation 8}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}  &  \multicolumn{2}{c}{\shortstack{\textbf{Simulation 39}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}\\
+      \hline 
+                     &\multicolumn{2}{c|}{} & &\\
+                     & {Average difference} & {Max difference}  &  {Max difference} & {Average difference}\\
+      \emph{Frame 1}       &35.87(0.03) & 52.04(0.38)           &35.27(0.00) & 52.16(1.45)   \\
+      \emph{Frame 5}       &36.33(0.16) & 54.48(0.89)           &35.27(0.02) & 54.23(3.28)   \\
+      \emph{Frame 10}      &35.75(0.24) & 55.87(1.57)           &35.28(0.04) & 54.89(3.31)   \\
+      \emph{Frame 15}      &35.77(0.30) & 58.47(2.10)           &35.29(0.06) & 55.67(2.79)   \\
+      \emph{Frame 20}      &35.66(0.32) & 59.87(2.54)           &35.30(0.09) & 56.59(2.05)   \\
+      \emph{Frame 25}      &35.63(0.37) & 60.86(2.54)           &35.32(0.11) & 57.54(2.48)   \\
+      \emph{Frame 30}      &35.64(0.40) & 61.16(3.37)           &35.34(0.13) & 58.30(3.05)   \\
+      \emph{Frame 35}      &35.78(0.39) & 63.11(1.57)           &35.36(0.15) & 59.17(3.42)   \\      
+    \end{tabular}
+  \end{center}
+  \caption{Your caption.}\label{tab:recursive_fluid}
+\end{table}
+
 \section{Conclusion}\label{conclusion}
@@
 We built several models that can generalize different parts of the parameters of the simulations and gave concrete numbers that quantify the results.
-
 We see our work as preliminary research and we believe that the approach can be further developed and investigated.
@@
 \end{itemize}
+\clearpage
+\begin{figure}[H]
+  \vspace*{-2.5cm}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_1}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_1}
+  \end{subfigure}
 
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_5}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_5}
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_10}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_10}
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_15}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_15}
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_20}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_20}
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_25}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_25}
+  \end{subfigure}
+
+  \caption{These frames are generated by the constant model. The artifacts become apparent after the 10.\@ one.}\label{fig:const_sim}
+\end{figure}
+\vspace*{-1cm}
+\begin{figure}[H]
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_1}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_1}
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_5}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_5}
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_10}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_10}
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_15}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_15}
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_20}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_20}
+  \end{subfigure}
+
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_25}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_25}
+  \end{subfigure}
+
+  \caption{Example frames generated by the viscosity-density model. The parameters for this particular simulation are $\nu=4.17647, \rho = 0.001, g=1.4$}\label{fig:fluid_sim}
+\end{figure}
 \clearpage

### 2020-03-29 charts/rec.py

@@ -6,27 +6,102 @@ import sys
 
 import numpy as np
 
-def main():
+
+def inflow_39():
+    
+    inflow_avrg = np.array([[ 35.896,35.874,35.869,35.838,35.799,35.756,35.743,35.765,35.818,35.864,35.885,35.879,35.849,35.814,35.781,35.738,35.692,35.647,35.629,35.657,35.715,35.776,35.8,35.807,35.772,35.743,35.708,35.666,35.617,35.563,35.534,35.548,35.612,35.682,35.734,35.748,35.73,35.698,35.662,35.619 ],[ 35.913,35.91,35.917,35.896,35.869,35.835,35.826,35.849,35.907,35.964,35.992,35.993,35.971,35.95,35.934,35.906,35.867,35.825,35.804,35.828,35.885,35.947,35.979,35.994,35.969,35.944,35.917,35.884,35.842,35.787,35.757,35.766,35.827,35.895,35.944,35.957,35.945,35.923,35.896,35.857 ],[ 35.928,35.94,35.964,35.959,35.948,35.932,35.939,35.977,36.047,36.113,36.151,36.158,36.143,36.121,36.112,36.091,36.063,36.03,36.023,36.059,36.121,36.186,36.221,36.238,36.208,36.182,36.155,36.128,36.095,36.052,36.03,36.047,36.108,36.174,36.226,36.241,36.226,36.201,36.177,36.145 ],[ 35.943,35.962,35.998,36.006,36.002,35.988,36.004,36.058,36.141,36.217,36.269,36.295,36.292,36.279,36.27,36.255,36.232,36.203,36.204,36.254,36.337,36.419,36.47,36.507,36.501,36.492,36.472,36.444,36.414,36.372,36.356,36.385,36.465,36.552,36.619,36.648,36.65,36.64,36.623,36.585 ],[ 35.882,35.846,35.823,35.775,35.723,35.669,35.646,35.656,35.698,35.736,35.746,35.731,35.692,35.649,35.61,35.556,35.494,35.435,35.408,35.428,35.476,35.531,35.553,35.561,35.524,35.488,35.444,35.394,35.341,35.273,35.229,35.231,35.29,35.36,35.416,35.435,35.427,35.4,35.36,35.301 ],[ 35.9,35.886,35.882,35.844,35.802,35.766,35.756,35.779,35.838,35.892,35.921,35.926,35.908,35.879,35.857,35.824,35.776,35.725,35.701,35.722,35.77
[…]

### 2020-03-29 charts/single.py

@@ -18,8 +18,8 @@ def constant_models():
     labels = []
     box_data = []
 
-    data['with'] = [42.4267183875451 , 43.78148944993617]
-    data['without'] = [37.73239422055144 , 42.99703106930973 , 43.02076006161946]
+    data['with'] = [42.4267183875451 , 43.78148944993617, 38.40345812572034 , 31.116301500139375 , 30.37560326297156 , 29.362363717887963 , 34.59130832566979 , 38.37602182790361 , 33.13829763767398 , 41.07864349729163]
+    data['without'] = [37.73239422055144 , 42.99703106930973 , 43.02076006161946, 42.380817879629305 , 33.832192800572635 , 37.29558487343366 , 35.618496045124644 , 40.663238902192695 , 37.53103078541188 , 29.66568572886583 , 38.50229110243776]
 
     box_data.append(data['with'])
     box_data.append(data['without'])
@@ -27,7 +27,7 @@ def constant_models():
     labels.append('with pressure')
     labels.append('without pressure')
 
-    plt.figure(figsize=(17, 10))
+    plt.figure(figsize=(12, 7))
 
     x = [i for i in range(1, len(data.keys())+1)]
 
@@ -40,8 +40,8 @@ def constant_models():
     plt.gca().spines['top'].set_visible(False)
     plt.gca().spines['right'].set_visible(False)
 
-    plt.ylabel('PSNR', fontsize=32)
-    plt.title('Constant model (single image performance)', fontsize=36)
+    plt.ylabel('PSNR', fontsize=36)
+    plt.title('Constant model', fontsize=36)
 
     # plt.show()
     plt.savefig('single_const_psnr.eps')
@@ -53,8 +53,9 @@ def speed_models():
     labels = []
     box_data = []
 
-    data['with'] = [32.70363132431171 , 32.37544378610233 , 33.22313390003679, 33.80816838419148 , 33.1802077172184 , 33.873630834872216 , 33.95285390084521 ,33.67447951182013 , 33.179886956867975 , 34.17147778053133]
-    data['without'] = [32.038006486935075 , 32.192804717704554 , 32.184300070511554, 32.48270450488618 , 32.311327037629844 , 32.19408204987984 , 32.35434794736937 , 32.15279210676768 , 32.04192581940871 , 32.10279251816919]
[…]

### 2020-03-29 paper/eccv2020submission.tex
Adding some cptions

@@
 \begin{figure}
+  \begin{subfigure}{.3\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/single_const_psnr}
+  \end{subfigure}
+  \begin{subfigure}{.3\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/single_speed_psnr}
+  \end{subfigure}
+  \begin{subfigure}{.3\textwidth}
+    \centering
+    \includegraphics[width=1\linewidth]{imgs/charts/single_fluid_psnr}
+  \end{subfigure}
+  \caption{The evaluation samples for the constant model show how inconsistent its performance can be.
+We assume this is due to the limited data that the consent model uses.
+In contrast to that, we see how the viscosity-density model achieves significantly higher average PSNR.\@ On the other hand, the usage of the pressure field decreases the performance of the viscosity-density model.
+The may be because of the overall complexity of the model.
+The pressure field only adds another component to it that makes it even more hard to train.}\label{fig:single_psnr}
+\end{figure}
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{lcc|cc}
+      \textbf{Model type} & \multicolumn{2}{c|}{\textbf{Max difference}}  &  \multicolumn{2}{c}{\textbf{Average difference}}\\
+      \hline 
+      \multicolumn{3}{c|}{}&&\\
+                 & \underline{With pr.} & \underline{without pr.}  &  \underline{With pr}.& \underline{without pr.}\\
+
+      Constant           &14.56(1.97)&44.04(18.73)&0.60(0.29)&0.72(0.54)  \\
+      Inflow speed       &32.16(0.55)&45.68(1.21)&0.55(0.05)&0.93(0.07)   \\
+      Viscosity-density  &57.00(42.46)&14.70(2.65)&13.85(13.43)&0.37(0.09)\\
+    \end{tabular}
+  \end{center}
+  \caption{All of the given numbers are in percent. In the brackets we also give the standard deviation of the corresponding metric. }\label{tab:single}
+\end{table}
+
+\begin{figure}
 
@@
     \includegraphics[width=1\linewidth]{imgs/single_constant_y}
-
   \end{subfigure}
@@
   \end{subfigure}
-
   \begin{center}
@@
     \centering
-    % \caption{Fluid model, x-velocity fields}
     \includegraphics[width=1\linewidth]{imgs/single_fluid_x_1}
@@
     \centering
-    % \caption{Fluid model, y-velocity fields}
     \includegraphics[width=1\linewidth]{imgs/single_fluid_y_1}
@@
     \centering
-    % \caption{Fluid model, x-velocity fields}
     \includegraphics[width=1\linewidth]{imgs/single_fluid_x_2}
@@
     \centering
-    % \caption{Fluid model, y-velocity fields}
     \includegraphics[width=1\linewidth]{imgs/single_fluid_y_2}
   \end{subfigure}
-
   \begin{center}
@@
 \end{figure}
-
-\begin{figure}
-  \begin{subfigure}{.3\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/charts/single_const_psnr}
-  \end{subfigure}
-  \begin{subfigure}{.3\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/charts/single_fluid_psnr}
-  \end{subfigure}
-  \begin{subfigure}{.3\textwidth}
-    \centering
-    \includegraphics[width=1\linewidth]{imgs/charts/single_speed_psnr}
-  \end{subfigure}
-
-  \caption{}\label{fig:single_psnr}
-\end{figure}
-
-\begin{table}
-  \begin{center}
-    \begin{tabular}{lcc|cc}
-
-      \textbf{Model type} & \multicolumn{2}{c|}{\textbf{Max difference}}  &  \multicolumn{2}{c}{\textbf{Average difference}}\\
-      \hline 
-      \multicolumn{3}{c|}{}&&\\
-                 & \underline{With pr.} & \underline{without pr.}  &  \underline{With pr}.& \underline{without pr.}\\
-
-      Constant          &  14.6(3.89)&44.0(3.1e+02)&0.599(0.0818)&0.721(0.294)  \\
-
-      Inflow speed      &  32.2(0.297)&45.7(1.47)&0.546(0.00217)&0.929(0.00533) \\
-
-      Viscosity-density &  57.0(1.8e+03)&14.7(7.04)&13.8(1.8e+02)&0.374(0.00824) \\
-    \end{tabular}
-  \end{center}
-  \caption{Your caption.}\label{tab:single}
-\end{table}
 
@@
 For this section, we also limit ourselves only to models that do use the pressure field of the simulations.
+All of the given plots show the mean results for each frame across the evaluations of several models that differ only in the used seed during training.
+We also plot the standard divination across the evaluations.
 
@@
   \end{subfigure}  
-  \caption{}\label{fig:rec_const_psnr}
+  \caption{The simulation that starts at the 10.\@ frame exhibits unintuitive results.
+This happens because the PSNR is based on MSE and it can go up if the network produces a homogeneous black image.
+In this case the PSNR can get higher in the second of the predicted frames.
+This, however, does not meant that the visual fidelity of the frames is good.}\label{fig:rec_const_psnr}
 \end{figure}
@@
   \end{subfigure}
-
   \begin{center}
-    Simulation
+    Recursive evaluations of the inflow speed model on simulation with $g=1.5$.
+To note is that this simulations was part of the training set.
+This can explain why the PSNR drops slightly faster on the next charts when it comes to the simulation starting at the 120.\@frame.
   \end{center}
-
   \begin{subfigure}{.5\textwidth}
@@
   \end{subfigure}
-
   \begin{center}
-    Simulation
+    Recursive evaluations of the inflow speed model on simulation with $g=3.9358$.
   \end{center}
-
-  \caption{}\label{fig:rec_speed_psnr}
+  \caption{In the evaluations of the inflow speed models, we consistently saw the same behavior as in the constant models.
+The simulations that at are started at a frame with smaller index are of a lower quality.}\label{fig:rec_speed_psnr}
 \end{figure}
@@
   \end{subfigure}
-
   \begin{center}
-    Simulation
+    Recursive evaluations of the viscosity-density model on simulation with $\rho=4.1764$ and $\nu=0.001023$.
   \end{center}
-
   \begin{subfigure}{.5\textwidth}
@@
   \end{subfigure}
-
   \begin{center}
-    Simulation
+    Recursive evaluations of the viscosity-density model on simulation with $\rho=5.7647$ and $\nu=0.001517$.
   \end{center}
-
   \begin{subfigure}{.5\textwidth}
@@
   \end{subfigure}
-
   \begin{center}
-    Simulation
+    Recursive evaluations of the viscosity-density model on simulation with $\rho=6.8235$ and $\nu=0.002876$.
   \end{center}  
-
-  \caption{}\label{fig:rec_fluid_psnr}
+  \caption{All of the simulations for the charts are from the test set of the viscosity-density model.
+The evaluations with starting frame of 0 are consistent with the results from the other models.
+The evaluations starting at frame 120 are, however, much more stable as indicated by the standard deviation.
+We again attribute that to the over all stability of the model due to the large amount of train data used to train the models of this type.}\label{fig:rec_fluid_psnr}
 \end{figure}
@@
   \end{center}
-  \caption{Your caption.}\label{tab:recursive_inflow}
+  \caption{}\label{tab:recursive_inflow}
 \end{table}
@@
 % LocalWords:  preprocessing postprocessing hyperparameters HiFlow
+% LocalWords:  unintuitive

### 2020-03-29 charts/single_table.py

@@ -29,36 +29,36 @@ def main():
     np_fluid_avrg = np.array([0.42235304314329736 , 0.5787415254237288 , 0.33393451463790447 , 0.30568432203389834 , 0.3313731041456016 , 0.3340954788386537 , 0.31267950693374424 ])
     np_fluid_max = np.array([16.124258474576273 , 14.990394260400619 , 13.283522534668721 , 19.36700442989214 , 11.396986710963457 , 11.501868842987145 , 16.20593278120185 ])
 
-    print("{:.3}({:.3})&{:.3}({:.3})&{:.3}({:.3})&{:.3}({:.3})".format(
+    print("{:.2f}({:.2f})&{:.2f}({:.2f})&{:.2f}({:.2f})&{:.2f}({:.2f})".format(
         np.mean(p_const_max),
-        np.var(p_const_max),
+        np.std(p_const_max),
         np.mean(np_const_max),
-        np.var(np_const_max),
+        np.std(np_const_max),
         np.mean(p_const_avrg),
-        np.var(p_const_avrg),
+        np.std(p_const_avrg),
         np.mean(np_const_avrg),
-        np.var(np_const_avrg)))
+        np.std(np_const_avrg)))
 
     
-    print("{:.3}({:.3})&{:.3}({:.3})&{:.3}({:.3})&{:.3}({:.3})".format(
+    print("{:.2f}({:.2f})&{:.2f}({:.2f})&{:.2f}({:.2f})&{:.2f}({:.2f})".format(
         np.mean(p_speed_max),
-        np.var(p_speed_max),
+        np.std(p_speed_max),
         np.mean(np_speed_max),
-        np.var(np_speed_max),
+        np.std(np_speed_max),
         np.mean(p_speed_avrg),
-        np.var(p_speed_avrg),
+        np.std(p_speed_avrg),
         np.mean(np_speed_avrg),
-        np.var(np_speed_avrg)))
+        np.std(np_speed_avrg)))
 
-    print("{:.3}({:.3})&{:.3}({:.3})&{:.3}({:.3})&{:.3}({:.3})".format(
+    print("{:.2f}({:.2f})&{:.2f}({:.2f})&{:.2f}({:.2f})&{:.2f}({:.2f})".format(
         np.mean(p_fluid_max),
-        np.var(p_fluid_max),
+        np.std(p_fluid_max),
         np.mean(np_fluid_max),
-        np.var(np_fluid_max),
[…]

### 2020-03-30 paper/eccv2020submission.tex
Small fixes

@@
   \end{center}
-  \caption{All of the given numbers are in percent. In the brackets we also give the standard deviation of the corresponding metric. }\label{tab:single}
+  \caption{All of the given numbers are in percent. In the parenthesis we also give the standard deviation of the corresponding metric. }\label{tab:single}
 \end{table}
@@
   \begin{center}
+    Inflow speed model
+  \end{center}
+  \begin{center}
     \begin{tabular}{l|cc|cc}
-      \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Simulation 8}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}  &  \multicolumn{2}{c}{\shortstack{\textbf{Simulation 39}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}\\
+     \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Start index: 120}\\$g=1.9487$}}& \multicolumn{2}{c}{\shortstack{\textbf{Start index: 120}\\$g=3.9358$}}\\
       \hline 
                      &\multicolumn{2}{c|}{} & &\\
-                     & {Average difference} & {Max difference}  &  {Max difference} & {Average difference}\\
+                     & {Average difference} & {Max difference}  &  {Average difference} & {Max difference}\\
       \emph{Frame 1}       &34.27(0.02) & 52.72(0.40)    &35.91(0.02) & 51.76(0.38)   \\
@@
   \end{center}
-  \caption{}\label{tab:recursive_inflow}
+  \caption{Again, all of the numbers are in percents and are averaged across the evaluations of models trained only with difference in the used seed.
+The standard deviation is given in the parenthesis.
+To note is that the maximum difference is high for almost all frames.
+This is to be expected from our models as they primarily target the visual quality of the results.
+The average difference on the other hand stays relatively stable across the frames.
+Still, average difference of over 30\% unsatisfactory even for course simulation.}\label{tab:recursive_inflow}
 \end{table}
@@
   \begin{center}
+    Viscosity-density model
+  \end{center}
+  \begin{center}
     \begin{tabular}{l|cc|cc}
-      \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Simulation 8}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}  &  \multicolumn{2}{c}{\shortstack{\textbf{Simulation 39}\\$\nu=4.17647, \rho = 0.001, g=1.4$}}\\
+      \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Start index: 120}\\$\rho=4.1764, \nu=0.001023$}}&\multicolumn{2}{c}{\shortstack{\textbf{Start index: 120}\\$\rho=6.8235, \nu=0.002876$}}\\
       \hline 
                      &\multicolumn{2}{c|}{} & &\\
-                     & {Average difference} & {Max difference}  &  {Max difference} & {Average difference}\\
+                     & {Average difference} & {Max difference}  &  {Average difference} & {Max difference}\\
       \emph{Frame 1}       &35.87(0.03) & 52.04(0.38)           &35.27(0.00) & 52.16(1.45)   \\
@@
   \end{center}
-  \caption{Your caption.}\label{tab:recursive_fluid}
+  \caption{For the viscosity-density model the average differences are again stable across the frames of the predicted simulations.
+The maximum differences grow as the predictions get more inaccurate and more artefacts appear in the predicted frames.}\label{tab:recursive_fluid}
 \end{table}

### 2020-03-31 paper/paper.tex
Updating the paper name

--- 2020-03-30 paper/eccv2020submission.tex
@@
 Computational Fluid Dynamics (CFD) is a field that deals with performing simulations of fluid flows.
-The task usually consists of setting certain initial conditions in a defined space and solving a large mathematical problem for each timestep of the simulation.
-Two central points of interest in CFD are the processing time needed for simulation and the accuracy of the results.
+The task usually consists of setting certain initial conditions in a defined space and solving a large mathematical problem for each timestep of a given simulation.
+Two central points of interest in CFD are the processing time needed for a simulation and the accuracy of the results.
 It is clear that low processing time and high accuracy are desired but often a certain trade-off has to be made.
@@
 
-We've concentrated our study on 2D simulations of incompressible fluid flow around an object in a channel according to the Navier-Stokes equations.
+We've concentrated our study on 2D simulations of incompressible fluid flow around an object in a channel according to the Navier-Stokes equations~\cite{bistafa2018}.
 This setup has three adjustable parameters --- the inflow speed, the viscosity and the density of the fluid.
@@
 In itself, this equation is then transformed and brought into a suitable for solving form.
-A common technique is the finite difference method (FDM).
-This can provide accurate results at the cost of large computational time.
+A common technique is the finite difference method (FDM)~\cite{bashar2011,petersson2018,zhang2014,nahit2011}.
+This method can provide accurate results at the cost of large computational time.
 The generated results are in the form of raw numbers representing the velocities and pressure fields which have to be visualized separately.
@@
 
-In recent years there has been a large interest in neural networks and their capabilities.
-Convolutional Neural Networks (CNNs) in particular have been successfully applied in a wide variety of contexts and have proven to be a valuable tool.
+In recent years there has been a large interest in neural networks and their capabilities~\cite{krizhevsky2012,simonyan2014,zeiler2011,liu2017,ronneberger2015}.
+Convolutional Neural Networks (CNNs)~\cite{long2014} in particular have been successfully applied in a wide variety of contexts~\cite{eremeev2019,schulz2019,zhangyang2019,yang2019} and have proven to be a valuable tool.
 One of the major fields where the performance of CNNs is recognized is image processing.
-A lot of research has shown how CNNs can achieve state-of-the-art performance in tasks like image classification, image segmentation of image-to-image mapping.
+A lot of research has shown how CNNs can achieve state-of-the-art performance in tasks like image classification~\cite{xie2019,xie2016aggregated,he2015}, image segmentation~\cite{xie2016aggregated,choi2020cars} of image-to-image mapping~\cite{liu2017,radford2015,park2019}.
 With our research, we try to tie CFD and CNNs together and show how image processing approaches can be applied to performing numerical simulations.
@@
 
-We try to apply the approach of [pix2pix] in our work.
-In recent years GANs show impressive results in image generation.
+We base our work on the approach of~\cite{pix2pix}.
+In recent years GANs show impressive results in image generation~\cite{DashGALA17,ZhangXLZHWM16,karras2017progressive}.
 Conditional GANs (cGANs) extend these capabilities of the generator network and allow it to learn image-to-image translation tasks.
-We wanted to show that conditional GANs can be used in the context of numerical simulations.
+We want to show how conditional GANs can be used in the context of numerical simulations.
 In this case, the generation of a frame of a simulation is conditioned on the previous frame of the same simulation.
@@
 We achieve that by investigating how a cGANs generalizes the different parameters of the investigated simulation.
-Two subsets of the parameters are defined --- fluid parameters (viscosity and density) and the inflow speed of the fluid.
+Two subsets of the parameters are defined --- fluid parameters (kinematic viscosity and density) and the inflow speed of the fluid.
 For each of these two subsets, we train separate models and evaluate their performance in different use cases.
@@
 On the other side, we also want to see how the inaccuracies in the predicted images can accumulate over time.
-Hence also evaluate the models by recursive application where the output of the network is used again as an input for a certain amount of timesteps.
+Hence, we also evaluate the models by recursive application where the output of the network is used again as an input for a certain amount of timesteps.
 More details about the evaluations are given in \refsec{eval}.
@@
 This makes the handling of data in image form convenient.
-We assumed that a neural network can process the information in this form more easily.
+Based on the previous works, we assume that fully convolutional neural network can process information in this form more easily.
 Furthermore, convolutional neural networks are well-established models for performing image processing tasks.
-We were interested in how a numerical task can be turned into an image processing task as in certain situations, the image result has the priority.
+We were interested in how a numerical task can be turned into an image processing task as in certain situations, the image results have the priority.
 We also think that the image processing can be done much quicker in a more optimal way.
@@
 \section{Related Work}\label{related_work}
+There has been a long-standing interest whether or not neural networks can be used in strictly mathematical contexts~\cite{neville2002,lample2019}.
+When it comes to differential equations,~\cite{lagaris1998} has demonstrated for the first time how neural networks can be applied to solve PDEs and ODEs by designing a loss function based on a particular equation.
+More recently, a similar approach has been presented in~\cite{avrutskiy2017}.
+With the emergence of deep learning~\cite{krizhevsky2012}, DNNs have been successfully applied in numerical tasks as well~\cite{wei2017,battaglia2016}.
+By flow problems, CNNs have been successfully applied in analyzing and calculating properties of flow fields~\cite{georgiou2018} and enhancing the quality of low-resolution simulations~\cite{tempoGan} while fully connected networks have helped in liquid splash modeling~\cite{hu2017}.
+
+In CFD, DNNs have been used in a wide variety of contexts.
+Turbulence models have been developed in~\cite{beck2018},~\cite{pfeiffer2019} has developed a network that predicts the motion of organs during operation and~\cite{tompson2016} uses a highly tailored neural network to solve Euler equations for fluid flow and thus accelerate the simulation process~\cite{thuerey2018} solves the problem of the Reynolds-Averaged Navier-Stokes (RANS) simulation similarly to us.
+They do not use cGANs, do not target the image representation of the simulation and tackle different equation from us but they too try to map initial conditions to a solution through an end-to-end model.
+
+The Navier-Stokes equations have also been a point of interest with respect to neural networks.~\cite{raissi2018} models the motion of particles in a fluid through a specifically designed network that encodes physical principles based on the Navier-Stokes equations.~\cite{baymani2010} has derived a trial solution of the equations in terms of a neural network.
+In contrast to these works, we aim at using a model with general architecture and applied it to a specific numerical simulation while approaching the problem from image processing point of view.~\cite{guo2016} deals with a similar problem by trying to predict the stabilized state of a laminar flow using a general model.
+The task, however, does not require the recursive application of the model but a single one.
+
+By now, the image-to-image translation through CNNs is well established and has found numerous applications~\cite{zhao2020,liu2017,ZhangXLZHWM16,park2019}.~\cite{pix2pix} has specifically stated how the ``community-driven research'' has popularized their work by applying it in different ways~\cite{Moschoglou2019,Kim2020,Chen2019}.
+We see our work as a demonstration of how cGANs can also be applied to numerical simulation context.
 
@@
 The task is to build a network that can predict the next frame of the simulation based on the previous one.
-Each frame represents a time step of the simulation and consists of a three-channel image.
+Each frame represents a timestep of the simulation and consists of a three-channel image.
 Two of the channels encode the velocity fields in both directions and the third channel is the pressure field of the fluid.
-We were interested in how the usage of the pressure field affects the performance of the built models.
+We are interested in how the usage of the pressure field affects the performance of the built models.
 Therefore, for each model two variants are trained --- one that uses the pressure field and one that does not.
@@
 We did not construct a single holistic model that can handle all of the simulation's parameters.
-Our efforts were concentrated on building a couple of smaller ones that take into account subsets of the parameters.
+Our efforts are concentrated on building a couple of smaller ones that take into account subsets of the parameters.
 The studied models are:
@@
 \end{list}
-By evaluating each model we want to see how a network can generalize each of the parameter subsets and to what extent
+By evaluating each model we want to see how a network can generalize each of the parameter subsets and to what extent.
 
 \subsection{Simulation Setup and Data generation}
-\emph{To study the performance of conditional GANs on generating frames of the concrete simulation we generated the training data ourselves.
+\emph{To study the performance of the models on predicting frames of a concrete simulation, we generated the training data ourselves.
 In what follows we give details about the process.} The training data was generated by performing numerous simulations of incompressible fluid flow around a rectangular object in a channel.
@@
 \end{list}
-The simulation setup has three separate adjustable parameters --- inflow speed $g$, fluid density $\rho$ and fluid viscosity $\nu$.
+The simulation setup has three separate adjustable parameters --- inflow speed $g$, fluid density $\rho$ and fluid kinematic viscosity $\nu$.
 
@@
 \begin{list}{$\circ$}{}
-\item[$\cdot$] constant: a single simulation with \ldots.
-\item[$\cdot$] varying inflow speed: \ldots simulations with different inflow speed. The inflow speeds are in the range of \ldots with a step of \ldots.
-\item[$\cdot$] varying viscosity and density of the fluid: \ldots simulations all with different fluid viscosity and density.
-The viscosity was in the range of \ldots with a step of \ldots and the density was in the range of \ldots with a step of \ldots.
+\item[$\cdot$] constant: a single simulation with $\rho=0.2, \nu=0.0009, g=1.5$.
+\item[$\cdot$] varying inflow speed: $40$ simulations with different inflow speed. The inflow speeds are in the range of $[1.5,4.0]$ with a step of $0.0625$.
+\item[$\cdot$] varying viscosity and density of the fluid: $324$ simulations all with different fluid viscosity and density.
+The viscosity was in the range of $[0.003, 0.0009]$ with a step of $0.0000064$ and the density was in the range of $[1.0, 10.0]$ with a step of $0.028$.
 We used the product of the two-parameter ranges to perform simulations with all of the possible combinations between the two parameters.
@@
 The choice of concrete values for the parameters is deliberate.
-All of the values are chosen so that the Reynolds number of the simulations in the range of [90, 450].
+All of the values are chosen so that the Reynolds number~\cite{trinh2010critical} of the simulations in the range of $[90, 450]$.
 This keeps the flow laminar while still making it interesting enough.
-We were interested whether the built models can predict the emerging Kármán vortex street behind the object in the channel.
+We were interested whether the built models can predict the emerging \emph{Kármán vortex street}~\cite{karaman1911} behind the object in the channel.
 Thus the Reynolds numbers were chosen so that the effect can occur.
@@
 The simulations were performed numerically by solving the differential equation describing the flow --- the Navier-Stokes equation.
-This was done with a numerical solver library --- \emph{HiFlow}~\cite{gawlok2017} ---  that works on the base of the Finite element method.
-The solver supports parallelization with MPI and OpenMP and we used 12 MPI processes to run each simulation.
+This was done with a numerical solver library --- \emph{HiFlow}~\cite{gawlok2017} ---  that works on the base of the Finite element method~\cite{strang2008analysis}.
+The solver supports parallelization with \emph{MPI}~\cite{mpi} and \emph{Open}MP~\cite{dagum1998openmp} and we used 12 MPI processes to run each simulation.
 For all of the simulations, the timestep for of solver was set to $0.035$ seconds.
@@
 The numerical solver on itself cannot be used to render the simulation results to images.
-For this reason, we used \emph{ParaView} to load the simulation data and exported it as a sequence of images in PNG format.
+For this reason, we used \emph{ParaView}~\cite{ahrens2005} to load the simulation data and exported it as a sequence of images in \emph{PNG} format.
 We opted out for using grayscale images as early experiments with RGB-images did not deliver satisfying results.
@@
 Each frame of the simulation was exported as three separate grayscale images.
-The images were finally cropped to select a subset of the space that contains the object and space behind it.
+Finally, the images were cropped to select a subset of the space that contains the object and space behind it.
 
 Because the number of simulations in each set is different, we also generated a different number of images per simulation based on the corresponding set.
-For the constant dataset, we rendered 1904 frames of the simulation (66 seconds of simulated physical time).
-For the inflow speed dataset --- overall 10050 frames coming from the 40 simulations (335 frames per simulation for 12 seconds of simulated physical time).
-For the viscosity-density model --- overall 104328 frames from 334 simulations (322 frames per simulation for 11 seconds of simulated physical time).
+For the constant dataset, we rendered $1904$ frames of the simulation ($66$ seconds of simulated physical time).
+For the inflow speed dataset --- overall $10050$ frames coming from the $40$ simulations ($335$ frames per simulation for $12$ seconds of simulated physical time).
+For the viscosity-density model --- overall $104328$ frames from $334$ simulations ($322$ frames per simulation for $11$ seconds of simulated physical time).
 Even though the simulations in the different datasets represent different time intervals, they are all long enough to develop the flow patterns that we are interested in.
 
-After all of the images were generated, a test-train split was created for each of the datasets The split for the inflow speed and viscosity-density sets were done manually.
+After all of the images were generated, a test-train split was created for each of the datasets.
+The split for the inflow speed and viscosity-density sets were done manually.
 For the inflow speed set, we selected every fourth simulation to be part of the test set and for the viscosity-density set --- every 25th.
@@
 
-The objective for the generator network is comprised of two parts --- the value of the discriminator as well as a L1 distance loss between the target and the predicted images.
-According to~\cite{pix2pix} the L1 loss promotes less blurring and captures the low frequency details of the images.
-The L1 loss is given by:
+The objective for the generator network is comprised of two parts --- the value of the discriminator as well as a $L1$ distance loss between the target and the predicted images.
+According to~\cite{pix2pix} the $L1$ loss promotes less blurring and captures the low frequency details of the images.
+The $L1$ loss is given by:
 \begin{equation}
@@
 \noindent\textbf{Networks Architectures:} For our generator we use the U-Net~\cite{ronneberger2015} variant proposed in~\cite{pix2pix}.
-It is a standard encoder-decoder~\cite{hinton2006} model that skip connections between parts of the encoder and the decoder.
-We also experimented with ResNet based generator but the results were not satisfactory.
-The network uses blocks of layers of the from convolution-normalization-ReLu.
+It is a standard encoder-decoder~\cite{hinton2006} model with skip connections between parts of the encoder and the decoder.
+We also experimented with ResNet~\cite{he2015} based generator but the results were not satisfactory.
+Our networks use blocks of layers of the from convolution-normalization-ReLu~\cite{batchnorm}.
 The encoder-decoder first downsamples the input till a bottleneck layer is reached and what follows is an upsampling to the original size of the input image.
@@
 \noindent\textbf{Training details:} We train the described three models with the generated datasets.
-When loading the images in memory, we first resize them to $1024\times 256$.
+When loading the images in memory, we first resize them to $1024\times 256$ (height $\times$ width).
 We then apply random crops as well as add random noise to each channel of the images.
 We do this to force the generator to learn the actual features of the simulation and make over-fitting harder.
-Before the input images are fed into the networks, we also multiply them with a mask of the object in the channel.
-This is an image that has zero value in the area where the object is located and one for every other location.
+Before the images are fed into the networks, we also multiply them with a mask of the object in the channel.
+This is an image that has zero value in the area where the object is located and values of one for every other location.
 The multiplication with the mask results in an input image with values of zero in the area of the object.
@@
 In all cases, the parameters are real values.
-In order for the network to be able to use them as part of the input, we transform these values in constant single-channel images with a value equal to one of the parameters.
+In order for the network to be able to use them as part of the input, we transform these values in constant single-channel images with a value equal to the corresponding parameters.
 This means that for each simulation parameter there is an extra channel in the for the generator network.
-Thus, depending on the model being trained, the network can take anywhere between 3 (velocity fields and object mask) and 6 (velocity and pressure fields, object mask and two parameter channels) channel input.
+Thus, depending on the model being trained, the network can take anywhere between 3 --- velocity fields and object mask --- and 6 --- velocity and pressure fields, object mask and two parameter channels --- channel input.
 The output of the generator, however, can either be 2 or 3 channel image depending on whether the pressure field is used or not.
 
-For the training procedure, we follow the standard approach proposed by~\cite{goodfellow2014}.
+For the training procedure, we follow the standard approach proposed in~\cite{goodfellow2014}.
 With each mini-batch, we first optimize the discriminator and then the generator with the discussed objectives.
@@
 Because of the differences in the amount of data available for training each model type, suitable epoch numbers were chosen for each of them.
-The constant models were trained for 45 epochs, the inflow speed models for 30 epochs and the viscosity-density models for 10 epochs.
+The constant models were trained for $45$ epochs, the inflow speed models for $30$ epochs and the viscosity-density models for $10$ epochs.
 
-All of the models were trained and evaluated on a single Nvidia GTX 980Ti GPU.\@ The implementation of the models was done in the PyTorch python library for machine learning.
+All of the models were trained and evaluated on a single Nvidia GTX 980Ti GPU.\@ The implementation of the models was done in the \emph{PyTorch}~\cite{paszke2017automatic} python library for machine learning.
 
 \section{Evaluation}\label{eval}
-\noindent\textbf{Evaluation Metrics:} When it comes to the evaluation, we have two separate views of the results generated by the models.
+\noindent\textbf{Evaluation Metrics:} When it comes to the evaluation, we have two separate views on the results generated by the models.
 
 On one hand, we are dealing with image data that is meant to be perceived by a human observer.
-This implies that full accuracy is not essential and therefore we place the importance on the perceived qualities of the results.
+This implies that full accuracy is not essential and therefore we place the importance on the perceived qualities of the predicted frames.
 This makes sense as in our case a human is concerned with the general development of the simulation over time.
-Under those considerations have chosen appropriate metrics to compare the predicted simulation frames with the real ones.
-In this aspect, the first of the metrics is Peak Signal to Noise Ratio (PSNR).
-It is related to the mean secured error (MSE) and it's given by
+Under those considerations we have chosen appropriate metrics to compare the predicted simulation images with the real ones.
+In this aspect, the first of the metrics is \emph{Peak Signal to Noise Ratio} (PSNR).
+It is related to the Mean Squared Error (MSE) and it is given by
 \begin{equation}
@@
 \end{equation}
-PSNR is measured in decibel (dB) and it is a common metric used to evaluate lossy compression algorithms.
-It measures the difference between the original and reconstructed images and considers the fidelity of the reconstruction.
+PSNR is measured in decibel (dB) and it is a common metric used to evaluate lossy compression algorithms~\cite{psnr1,psnr2}.
+It measures the difference between the original and reconstructed images and considers the visual fidelity of the reconstruction.
 This makes the metric suitable in our case.
@@
 We think that if the predicted images differ only in a factor from the real ones, the models can accurately capture the relative difference between the pixels of the target image.
-For this reason, we opted for also evaluating the results through correlation.
+For this reason, we opted for also evaluating the results through statistical correlation.
 
@@
 Classical solvers are evaluated in terms of the actual differences between the real and generated result and not the perceived differences.
-For those reasons, we have chosen two more metrics --- average difference and maximal differences.
-We calculated them based on differences between the corresponding pixels of the predicted and the real simulation frame.
-Both metrics are then averaged across the test set and are given in perceptual values.
+For those reasons, we have chosen two more metrics --- average absolute difference and maximal absolute differences.
+We calculate them based on differences between the corresponding pixels of the predicted and the real simulation frames.
+Both metrics are then averaged across the test set and are given in percentual values.
 The evaluation with these metrics should represent how well our models perform the simulation in the context of a CFD system.
@@
 \noindent\textbf{Details Evaluation:}
-\emph{In this subsection, we want to give several details on the training and evaluating approach}
+\emph{In this subsection, we want to give several details on the training and evaluating approach.}
 \begin{itemize}
@@
 \item[$\cdot$] For each model, the whole training and evaluating procedure was done ten times with different seeds for the random number generators of our python scripts.
-We report the results of each run and give them in a form of error plots or explicitly give the variance of all runs.
+We report the results of each run and give them in a form of error plots or explicitly give the standard deviation of all runs.
 \item[$\cdot$] All of the reported results for the individual runs are averaged across the simulation frames in the training sets.
@@
 The first of them is to see how well a single frame of the simulation is predicted.
-In this case, we pass all of the simulation frames in the test set to the network and evaluate the predicted frames.
-The models use only real simulation data for their predictions.
+In this case, we feed all of the simulation frames in the test set to the network and evaluate the predicted frames.
 
@@
   \end{center}
-  \caption{All of the given numbers are in percent. In the parenthesis we also give the standard deviation of the corresponding metric. }\label{tab:single}
+  \caption{All of the given numbers are in percents. In the parenthesis we also give the standard deviation of the corresponding metric.}\label{tab:single}
 \end{table}
@@
 The constant model is evaluated with a single simulation --- the one it was trained with.~\reffig{fig:rec_const_psnr} presents the results of the recursive application.
-During the evaluation, we noticed that the models can more accurately predict a simulation when the starting frame is further in the simulation.
-That is, its index relative to the first frame is higher.
+During the evaluation, we noticed that the models can more accurately predict the images when the starting frame is further in the simulation.
+That is, its index relative to the first frame of the simulation is higher.
 The plots for the constant model in~\reffig{fig:rec_const_psnr} illustrate this.
@@
 We can see the same trend that predicting frames with smaller index is harder.
-We,x however, like to note that the networks appear to be handling the parameters properly and adjust the predicted frames accordingly.\reffig{fig:rec_fluid_psnr} presents two simulations of the viscosity-density model.
+We, however, like to note that the networks appear to be handling the parameters properly and adjust the predicted frames accordingly.\reffig{fig:rec_fluid_psnr} presents two simulations of the viscosity-density model.
 
@@
 
-\begin{table}
+\begin{table}[H]
   \begin{center}
@@
 The average difference on the other hand stays relatively stable across the frames.
-Still, average difference of over 30\% unsatisfactory even for course simulation.}\label{tab:recursive_inflow}
+Still, average difference of over 30\% unsatisfactory even for coarse simulation.}\label{tab:recursive_inflow}
 \end{table}
 
-\begin{table}
+\begin{table}[H]
   \begin{center}
@@
 \section{Conclusion}\label{conclusion}
-The results presented in this paper suggest that solving a numerical task trough image-to-image translation is can be a viable approach.
+The results presented in this paper suggest that solving a numerical task trough image-to-image translation can be a viable approach.
 We showed how conditional GANs can be used to learn the image representations of the solutions of a fluid simulation according to the Navier-Stokes equations.
 We built several models that can generalize different parts of the parameters of the simulations and gave concrete numbers that quantify the results.
-We see our work as preliminary research and we believe that the approach can be further developed and investigated.
+Even though the accuracy of the results is not high enough for the predicted simulations to be considered ``true'', the visual quality of the images allows a human observer to see the general development of the fluid flow.
+
+We believe that out approach can be extended to other simulation types as well.
+We see our work as preliminary research and we believe that the method can be further developed and investigated.
 Strategies for improving the models that were considered but not implemented include:
@@
 As we use the U-Net architecture, there are also skip connections between each block $i$ in the encoder and the block $n-i$ in the decoder where $n$ is the total number of blocks in the network.
-The skip connections concatenate the results both blocks $i$ and $i-i$.
+The skip connections concatenate the results from both blocks $i$ and $i-i$.
 
@@
 \noindent\textbf{Discriminator Architecture:}
-We adopt the $70\times70$ variant of the decoder form [pix2pix]. The architecture is:\newline
-\texttt{C64-C128-C256-C512}
+We adopt the $256\times256$ variant of the decoder form [pix2pix]. The architecture is: \texttt{C64-C128-C256-C512}
 
@@
 Also, a final convolution is applied after the last layers that produced the one-dimensional output of the discriminator.
-A sigmoid function is applied after the convolution.
+A sigmoid function is applied after this convolution.
 \end{subappendices}
@@
 % LocalWords:  preprocessing postprocessing hyperparameters HiFlow
-% LocalWords:  unintuitive
+% LocalWords:  unintuitive convolutional parallelization percentual

### 2020-03-31 paper/paper.tex
Wraping things up

@@
 This was done with a numerical solver library --- \emph{HiFlow}~\cite{gawlok2017} ---  that works on the base of the Finite element method~\cite{strang2008analysis}.
-The solver supports parallelization with \emph{MPI}~\cite{mpi} and \emph{Open}MP~\cite{dagum1998openmp} and we used 12 MPI processes to run each simulation.
+The solver supports parallelization with \emph{MPI}~\cite{mpi} and \emph{OpenMP}~\cite{dagum1998openmp} and we used 12 MPI processes to run each simulation.
 For all of the simulations, the timestep for of solver was set to $0.035$ seconds.
@@
     \centering
+    \large{x-velocity}
     \includegraphics[width=1\linewidth]{imgs/single_constant_x}
@@
     \centering
+    \large{y-velocity}
     \includegraphics[width=1\linewidth]{imgs/single_constant_y}
@@
     \centering
-    \includegraphics[width=1\linewidth]{imgs/single_speed_x_1}
+    \includegraphics[width=1\linewidth]{imgs/x_recursive_0_speed_8}
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=1\linewidth]{imgs/single_speed_y_1}
+    \includegraphics[width=1\linewidth]{imgs/y_recursive_0_speed_8}
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=1\linewidth]{imgs/single_speed_x_2}
+    \includegraphics[width=1\linewidth]{imgs/x_recursive_0_speed_39}
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=1\linewidth]{imgs/single_speed_y_2}
+    \includegraphics[width=1\linewidth]{imgs/y_recursive_0_speed_39}
   \end{subfigure}
   \begin{center}
-    Images form the inflow speed model. The upper two are from simulation with $g=1.3$ and the lower ones form simulation with $g=0.1$
+    Images form the inflow speed model. The upper two are from simulation with $g=1.9487$ and the lower ones form simulation with $g=3.9358$
   \end{center}
@@
     \centering
-    \includegraphics[width=1\linewidth]{imgs/single_fluid_x_1}
+    \includegraphics[width=1\linewidth]{imgs/x_recursive_0_fluid_25}
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=1\linewidth]{imgs/single_fluid_y_1}
+    \includegraphics[width=1\linewidth]{imgs/y_recursive_0_fluid_25}
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=1\linewidth]{imgs/single_fluid_x_2}
+    \includegraphics[width=1\linewidth]{imgs/x_recursive_0_fluid_300}
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=1\linewidth]{imgs/single_fluid_y_2}
+    \includegraphics[width=1\linewidth]{imgs/y_recursive_0_fluid_300}
   \end{subfigure}
   \begin{center}
-  Images form the viscosity-density model. The upper two are from simulation with $\nu=1.3, \rho=2.3$ and the lower ones form simulation with $\nu=1.3, \rho=2.3$
+  Images form the viscosity-density model. The upper two are from simulation with $\rho=4.1764, \nu=0.001023$ and the lower ones form simulation with $\rho=4.1764, \nu=0.001023$.
   \end{center}
@@
 
-\begin{figure}
+\begin{figure}[H]
+  \vspace*{-4cm}
   \begin{subfigure}{.5\textwidth}
@@
 \end{figure}
-
-\begin{figure}
+\vspace*{-1cm}
+\begin{figure}[H]
   \begin{subfigure}{.5\textwidth}
@@
 To note is that this simulations was part of the training set.
-This can explain why the PSNR drops slightly faster on the next charts when it comes to the simulation starting at the 120.\@frame.
+This can explain why the PSNR drops slightly faster on the next charts when it comes to the simulation starting at the 120.
+\@frame.
   \end{center}
@@
 
+\noindent\textbf{Performance:} All of the models were evaluated on an Nvidia GTX 980Ti GPU.\@In all cases, the forward propagation of a single simulation frame took between 5 and 20 ms (milliseconds).
+In comparison, during the data generation, HiFlow needed between 1000 and 1500 ms for a single simulation timestep while using 12 MPI processes.
+This does not include the time needed for rendering the results of the simulation.
+To note is that this is not a one-to-one comparison as HiFlow runs on the CPU and uses MPI and OpenMP for parallelization.
+We, however, think that the results show the potential of our approach when it comes to performance.
+
 \section{Conclusion}\label{conclusion}
@@
 \end{itemize}
-\clearpage
 \begin{figure}[H]
-  \vspace*{-2.5cm}
+  \vspace*{-4.5cm}
   \begin{subfigure}{.5\textwidth}
     \centering
+    \large{x-velocity}
     \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_1}
@@
     \centering
+    \large{y-velocity}
     \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_1}
@@
     \centering
+    \large{x-velocity}
     \includegraphics[width=1\linewidth]{imgs/sims/fluid/x_step_1}
@@
     \centering
+    \large{y-velocity}
     \includegraphics[width=1\linewidth]{imgs/sims/fluid/y_step_1}

### 2020-05-07 paper/paper.tex
Correcting the paper

@@
 In itself, this equation is then transformed and brought into a suitable for solving form.
-A common technique is the finite difference method (FDM)~\cite{bashar2011,petersson2018,zhang2014,nahit2011}.
+In a general case, basic technique that can be used is the finite difference method (FDM)~\cite{bashar2011,petersson2018,zhang2014,nahit2011}.
 This method can provide accurate results at the cost of large computational time.
@@
 We were interested in how a numerical task can be turned into an image processing task as in certain situations, the image results have the priority.
-We also think that the image processing can be done much quicker in a more optimal way.
-Those considerations urged us to conduct the research presented in this paper.
+We believe that this image processing approach can be used to generate a simulation image much faster than a numerical approach with some loss in accuracy.
+The accuracy loss is the subject of our research.
 
@@
 They do not use cGANs, do not target the image representation of the simulation and tackle different equation from us but they too try to map initial conditions to a solution through an end-to-end model.
+Our approach is not exactly comparable to the one of~\cite{thuerey2018} as we are considering a different numeric problem (the Navier-Stokes equations).
+Also,~\cite{thuerey2018} tries to map the boundary conditions of the problem to the solutions.
+We, on the other hand, map a solution of the studied simulation to the next one.
 
@@
 All of the values are chosen so that the Reynolds number~\cite{trinh2010critical} of the simulations in the range of $[90, 450]$.
-This keeps the flow laminar while still making it interesting enough.
+This causes a transitional flow with vortex shedding effect.
 We were interested whether the built models can predict the emerging \emph{Kármán vortex street}~\cite{karaman1911} behind the object in the channel.
@@
 Conditional GANs also feed an input image $x$ to the generator, $G: x,z \rightarrow y$.~\cite{pix2pix} and~\cite{wang2016} suggest that in certain cases the usage of $z$ can be usefully but we decided not to include for our generator as we want a deterministic network.
+The discriminator network is modeled with the function $D:x,y \rightarrow v$ that evaluates the likelihood of $y$ being a real image.
+To note is that the discriminator network has access to the real image $x$ and tries to guess, if $y$ is the real or generated output.
 
-We adopt the objective for the discriminator network as we modify it slightly by leaving out the random vector $z$.
+We adopt the objective for the discriminator network and we modify it slightly by leaving out the random vector $z$.
 \begin{equation}
-\mathcal{L}_{cGAN} (G, D) = (\mathbb{E}[\log D (x,y)] + \mathbb{E}[\log D (x, G(x))])/2
+  \mathcal{L}_{cGAN} (G, D) = (\mathbb{E}[\log D (x,y)] + \mathbb{E}[\log D (x, G(x))])/2 \\
+  = (\log D (x,y) + \log D (x, G(x)))/2
 \end{equation}
 where $x$ is the input image and $y$ is the target image.
+We leave out the expected value calculation as we do not use the random vector $z$ in our objective.
 In contrast to unconditional GANs, both the generator and the discriminator network have access to the input image.
@@
 \end{equation}
-For all of the models we used $\lambda = 100$.
+For all of the models we used $\lambda = 100$ as done in~\cite{pix2pix}. We also experimented with lower values for $\lambda$ but results were not as good.
 
@@
 
-For the discriminator, we follow the method of pix2pix and we use their PatchGAN.\@ This is a convolutional network that examines only patches of the input.
-It tries to guess if each patch is from a real or generated image.
-We use patches of size $256\times 256$ pixels.
+For the discriminator, we follow the method of~\cite{pix2pix} and we use their PatchGAN discriminator network.\@ This is a convolutional network that classifies patches of the input as real or predicted.
+To not is that the whole image is given as an input.
+The majority of the results in~\cite{pix2pix} show that a patches of size $70\times 70$ yield the best results but in our case, the experiments showed otherwise.
+We, therefore, we opted out for using patches of size $286\times 286$ pixels.
 
 \noindent\textbf{Training details:} We train the described three models with the generated datasets.
-When loading the images in memory, we first resize them to $1024\times 256$ (height $\times$ width).
+When loading the images in memory, we first resize them to an appropriated for a network size of $1024\times 256$ (width $\times$ height).
 We then apply random crops as well as add random noise to each channel of the images.
@@
 The multiplication with the mask results in an input image with values of zero in the area of the object.
+The predicted images are also multiplied with the mask.
+This procedure lets us examine how well the network generates the pixels in the places that we are interested in --- the places where the flow occurs.
 The object mask itself is also given as an input to the generator network.
+This gives the network the information of where the object is.
+This information cannot be embedded in the other input images as the zeroed values in the location of the object are interpreted as velocity values by network.
 
@@
 With each mini-batch, we first optimize the discriminator and then the generator with the discussed objectives.
-We use Stochastic Gradient Descent~\cite{kiefer1952} with the Adam optimizer~\cite{kingma2014} with a learning rate of $0.0002$ and momentum parameters $\beta_1=0.9$ and $\beta_2=0.999$.
-The used batch size for the constant and inflow speed models was set to 3 and for the viscosity-density models to 4.
+We use Stochastic Gradient Descent~\cite{kiefer1952} with the Adam optimizer~\cite{kingma2014} with a learning rate of $0.0002$ and standard momentum parameters $\beta_1=0.9$ and $\beta_2=0.999$.
+The used batch size for the constant and inflow speed models was set to $3$ and for the viscosity-density models to $4$.
 Those are relatively small numbers for batch sizes but~\cite{pix2pix} suggests that the U-Net architecture benefits from small batches in image-to-image translation problems.
@@
 Typical PSNR values of lossy image and video compression algorithms are between $30$ and $50$ dB.
+Higher PSNR values are desired, as the value of PSNR is inversely proportional to the value of MSE.
 
@@
 We think that if the predicted images differ only in a factor from the real ones, the models can accurately capture the relative difference between the pixels of the target image.
-For this reason, we opted for also evaluating the results through statistical correlation.
+For this reason, we opted for also evaluating the results through statistical correlation between the predicted and the real images.
+Naturally, we want to see if the models can generated images with correlation close to $1.0$.
 
@@
 The evaluation with these metrics should represent how well our models perform the simulation in the context of a CFD system.
+As their are both difference measures, lower values are desired for these metrics.
 
-\noindent\textbf{Details Evaluation:}
+\noindent\textbf{Evaluation Details:}
 \emph{In this subsection, we want to give several details on the training and evaluating approach.}
@@
     \begin{tabular}{lcc|cc}
-      \textbf{Model type} & \multicolumn{2}{c|}{\textbf{Max difference}}  &  \multicolumn{2}{c}{\textbf{Average difference}}\\
+      \textbf{Model type} & \multicolumn{2}{c|}{\textbf{Max difference(\%) }}  &  \multicolumn{2}{c}{\textbf{Average difference(\%)}}\\
       \hline 
@@
 To note is that this is not a one-to-one comparison as HiFlow runs on the CPU and uses MPI and OpenMP for parallelization.
+Also, we performed all the real simulations with HiFlow on a Intel Xeon E5-2650 v4 CPU.
+
 We, however, think that the results show the potential of our approach when it comes to performance.
@@
 
-This configuration results in a receptive field of $256\times256$.
+This configuration results in a receptive field of $286\times286$.
 This means that for each $256\times256$ region of the input, the discriminator tries to guess if the region is from a real image or from a generated one.

### 2020-05-07 paper/paper.tex
Final touches

@@
 
-We adopt the objective for the discriminator network and we modify it slightly by leaving out the random vector $z$.
+We adopt the objective function the discriminator network and we modify it slightly by leaving out the random vector $z$.
 \begin{equation}
-  \mathcal{L}_{cGAN} (G, D) = (\mathbb{E}[\log D (x,y)] + \mathbb{E}[\log D (x, G(x))])/2 \\
-  = (\log D (x,y) + \log D (x, G(x)))/2
+  \begin{split}
+    \mathcal{L}_{cGAN} (G, D) &= (\mathbb{E}[\log D (x,y)] + \mathbb{E}[\log D (x, G(x))])/2 \\
+    &= (\log D (x,y) + \log D (x, G(x)))/2
+  \end{split}
 \end{equation}
 where $x$ is the input image and $y$ is the target image.
-We leave out the expected value calculation as we do not use the random vector $z$ in our objective.
+We leave out the expected value calculation as we do not use the random vector $z$ in our loss function.
 In contrast to unconditional GANs, both the generator and the discriminator network have access to the input image.
@@
                      &\multicolumn{2}{c|}{} & &\\
-                     & {Average difference} & {Max difference}  &  {Average difference} & {Max difference}\\
+                     & {Average difference \%} & {Max difference \%}  &  {Average difference \%} & {Max difference \%}\\
       \emph{Frame 1}       &34.27(0.02) & 52.72(0.40)    &35.91(0.02) & 51.76(0.38)   \\
@@
 To note is that this is not a one-to-one comparison as HiFlow runs on the CPU and uses MPI and OpenMP for parallelization.
-Also, we performed all the real simulations with HiFlow on a Intel Xeon E5-2650 v4 CPU.
+In our case the used CPU was Intel Xeon E5-2650 v4.
 

### 2020-06-02 final/figures/network/meth.tex
Adding some nice figures

\documentclass{standalone}

\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{tkz-euclide}

\pgfplotsset{compat=1.6}

\usetikzlibrary{positioning,calc}
\usetikzlibrary{arrows} 
\usetikzlibrary{patterns} 
\usetikzlibrary{shapes}
\usetikzlibrary{decorations.pathmorphing}

\begin{document}

\tikzset{
  cascaded/.style = {
    general shadow = {
      shadow scale = 1,
      shadow xshift = -2ex,
      shadow yshift = 2ex,
      draw,
      thick,
      fill = white},
    general shadow = {
      shadow scale = 1,
      shadow xshift = -1ex,
      shadow yshift = 1ex,
      draw,
      thick,
      fill = white},
    fill = white, 
    draw,
    thick,
    minimum width = 2.5cm,
    minimum height = 1.3cm},
  squarednode/.style={rectangle, draw=green!60, fill=green!5, very thick, minimum width = 2.5cm, minimum height = 1.3cm}
}

\def\BeforeLight{2}
\begin{tikzpicture}

  \node[draw,minimum width = 2.5cm, minimum height = 1.3cm, thick] at (0,3) (img) {\shortstack{Initial\\Image}};
  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em, thick] (net) at (0, 0) {Network};
  \node[cascaded] at (0.3, -3) (images) {Images};

  \node[draw=green!60, fill=green!5, very thick, minimum width = 0.6cm, minimum height = 0.6cm] at (1.7, 3.5) (params_1) {\shortstack{Simulation\\Parameters}};

  \draw[->, shorten >=3pt, shorten <=3pt, thick ] (img) edge (net);
  \draw[->, shorten >=3pt, shorten <=3pt, thick ] (net) edge (0, -2);
  \draw[->, shorten >=3pt, shorten <=3pt, thick] (0, -1.5) -- (2, -1.5) -- (2, 2) -- (0, 2);

\end{tikzpicture}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-06-02 final/figures/pipeline/meth.tex
Adding some nice figures

\documentclass{standalone}

\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{tkz-euclide}

\pgfplotsset{compat=1.6}

\usetikzlibrary{positioning,calc}
\usetikzlibrary{arrows} 
\usetikzlibrary{patterns} 
\usetikzlibrary{shapes}
\usetikzlibrary{decorations.pathmorphing}

\begin{document}

\tikzset{
  cascaded/.style = {
    general shadow = {
      shadow scale = 1,
      shadow xshift = -2ex,
      shadow yshift = 2ex,
      draw,
      thick,
      fill = white},
    general shadow = {
      shadow scale = 1,
      shadow xshift = -1ex,
      shadow yshift = 1ex,
      draw,
      thick,
      fill = white},
    fill = white, 
    draw,
    thick,
    minimum width = 2.5cm,
    minimum height = 1.3cm},
  squarednode/.style={rectangle, draw=green!60, fill=green!5, very thick, minimum width = 2.5cm, minimum height = 1.3cm}
}

\def\BeforeLight{2}
\begin{tikzpicture}
  % \draw[step=1cm, gray!20!white, very thin] (-5,-5) grid (5,5);

  % \node[draw, minimum height=1cm, minimum width=3cm] at (0, 3) (n_1) {Numerical Problem};
  \node[draw,ellipse,minimum width = 0.6cm, minimum height = 1.6cm, thick] at (0, 3) (problem) {\shortstack{Numerical\\Problem}};
  \node[draw,ellipse,minimum width = 0.6cm, minimum height = 1.6cm, thick] at (0, 0) (solution) {\shortstack{Raw Solution\\Data}};

  \node[cascaded] at (0.3,-3) (images) {Images};

  \node[draw,minimum width = 0.6cm, minimum height = 0.8cm, thick] at (2.0, 1.5) (solver) {\shortstack{CFD\slash PDE\\Solver}};
  \node[draw,minimum width = 0.6cm, minimum height = 0.8cm, thick] at (2.5, -1.5) (visu) {\shortstack{Visualization\\Tool}};

  \draw[->, shorten >=3pt, shorten <=3pt, thick ] (problem) edge (solution);
  \draw[->, shorten >=3pt, shorten <=3pt, thick ] (solution) edge (0, -2);

  \draw[-, dashed, shorten >=3pt, shorten <=3pt, thick ] (0.0, 1.5) edge (solver);
  \draw[-, dashed, shorten >=3pt, shorten <=3pt, thick ] (0.0, -1.5) edge (visu);

  \node[draw=green!60, fill=green!5, very thick, minimum width = 0.6cm, minimum height = 0.6cm] at (2, 4) (params_1) {\shortstack{Simulation\\Parameters}};
  \node[draw=green!60, fill=green!5, very thick, minimum width = 0.6cm, minimum height = 0.6cm] at (3.5, 2.3) (params_2) {\shortstack{Solver\\Parameters}};
  \node[draw=green!60, fill=green!5, very thick, minimum width = 0.6cm, minimum height = 0.6cm] at (3.5, -0.7) (params_3) {\shortstack{Visualization\\Parameters}};

\end{tikzpicture}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-06-04 final/figures/net/fig.tex
Kinda wraping the presi

--- 2019-12-06 progress_update/figs/pressure_optional/fig.tex
@@
-\documentclass[border=5mm]{standalone}
+\documentclass{standalone}
 \usepackage{tikz}
@@
   roundnode/.style={circle, draw=green!60, fill=green!5, very thick, minimum width = 2.5cm, minimum height = 1.3cm},
-  squarednode/.style={rectangle, draw=red!60, fill=red!2, very thick, minimum width = 2.5cm, minimum height = 1.3cm},
+  squarednode/.style={rectangle, draw, thick, minimum width = 2.5cm, minimum height = 1.3cm},
 }
+\resizebox{\columnwidth}{!}{%
   \begin{tikzpicture}
@@
 
-  \node[squarednode] (pressure_i) at (0, -2.3) {Pressure};
+  \node[squarednode] (pressure_i) at (-0.1, -2.3) {Pressure};
   \node[squarednode] (pressure_o) at (8, -2.3) {Pressure};
@@
 
-  \draw  [dashed] (-1.5,-1.2) rectangle (9.5,-3.4);
-
   \node[text width=1cm,align=center] (x_y) at (time_t.center) {$x$\&$y$ \\ Velocities};  
@@
 
-\end{tikzpicture}
+  \node[draw=green!60, fill=green!5, very thick, minimum width = 0.6cm, minimum height = 0.6cm] at (-0.2, 1.3) (params_1) {\shortstack{Simulation\\Parameters}};
+
+\end{tikzpicture}}
 

### 2020-06-04 project/train_models.sh
Having a nice wrap of the project

@@ -192,3 +192,6 @@ do
     
 done
 
+
+
+python train.py --data ./data/generated_data/ --model-type 'c' --model-name "time_1" --threads 4 --batch-size 3 --shuffle --epochs 1 --lr_policy step --seed ${RANDOM} --print-summeries --test-train-split 0.8 --val-train-split 0.1 --output-dir "./results_c/time_${RANDOM}/" --evaluate --g_nfg 32 --g_layers 5 --use-pressure --no-train

### 2020-06-05 project/config.py
Starting the good work here

@@ -21,34 +21,3 @@ config['evaluation_recursive_samples'] = 20
 config['full_simulaiton_samples'] = 25
 
 config['lambda_L1'] = 100
-
-config['adam_lr'] = 0.0002
-config['adam_b1'] = 0.9
-config['adam_b2'] = 0.999
-
-
-# config['input_width'] = 1024
-# config['input_height'] = 256
-
-# config['g_input_nc'] = 3
-# config['g_output_nc'] = 2
-
-# config['g_nfg'] = 34
-# config['g_layers'] = 5
-
-# config['d_input_nc'] = 12
-
-# config['d_nfg'] = 22
-# config['d_layers'] = 4
-
-# config['output_dir'] = './model_output'
-
-# config['evaluation_snapshots_cnt'] = 5
-# config['evaluation_recursive_samples'] = 5
-# config['full_simulaiton_samples'] = 5
-
-# config['lambda_L1'] = 100
-
-# config['adam_lr'] = 0.001
-# config['adam_b1'] = 0.9
-# config['adam_b2'] = 0.999

### 2020-06-05 project/utils.py

@@ -30,7 +30,7 @@ class RedirectStdStreams(object):
 class Logger(object):
     def __init__(self, log_file):
         self.terminal = sys.stdout
-        self.log = open(log_file, "a")
+        self.log = open(log_file, "a") 
 
     def write(self, message):
         self.terminal.write(message)

### 2020-06-05 proper_project/config.py

@@ -1,0 +1,58 @@
+
+class BaseConfig(object):
+    
+    def __init__(self):
+
+        self.input_width = 1024
+        self.input_height = 256
+
+        self.evaluation_snapshots_cnt = 7
+        self.evaluation_recursive_samples = 20
+        self.full_simulaiton_samples = 25
+
+        self.g_ngf = 0
+        self.g_layersl = 0
+
+        self.d_ngf = 0
+        self.d_layers = 0
+
+        self.adam_lr = 0.0002
+        self.adam_b1 = 0.9
+        self.adam_b2 = 0.999
+
+    def argparse(self, parser):
+        pass
+
+    def post_config(self):
+        pass
+
+        
+class SimpleConfig(BaseConfig):
+
+    def __init__(self):
+        BaseConfig.__init__(self)
+
+        self.g_ngf = 64
+        self.g_layers = 3
+
+        self.d_ngf = 32
+        self.d_layers = 3
+
+class AdvanceConfig(BaseConfig):
+
+    def __init__(self):
+        BaseConfig.__init__(self)        
+
+        self.g_ngf = 64
+        self.g_layers = 7
+
+        self.d_ngf = 48
+        self.d_layers = 3
+
+        
+
+default_config = "simple"
+configuration_classes = {
+    "simple" : SimpleConfig,
+    "complicated" : AdvanceConfig
+}

### 2020-06-05 proper_project/main.py

@@ -1,0 +1,57 @@
+#!/usr/bin/env python
+
+import os
+import sys
+import argparse
+
+from config import configuration_classes as CONFIGURATIONS
+from config import default_config as DEFAULT_CONFIG
+
+
+VERSION_MSG = ["experimental" ]
+
+
+
+def train(parser, args):
+    conf = args.config
+
+    conf_object = CONFIGURATIONS[conf]()
+
+    print(f'config: {conf}')
+    
+
+def test(args):
+    pass
+
+def visu(args):
+    pass
+
+def main():
+    
+    parser = argparse.ArgumentParser(
+        prog="flow", description="Train, evaluate and visualize"
+    )
+
+    parser.add_argument("--version", "-v", action="version", version=("\n".join(VERSION_MSG)), help="Print veriosn inormation")
+    parser.add_argument('--seed', dest='seed', type=int, default=42, help='Random seed to use.')
+
+    subparsers = parser.add_subparsers(title="Commands", description="All phases of ML", dest="command", metavar="Command",)
+
+    
+    parser_train = subparsers.add_parser("train", description="Train the models", help="Training the models")
+    parser_eval = subparsers.add_parser("eval", description="Eval the models", help="Evaluating the models")
+    parser_visu = subparsers.add_parser("visu", description="Visualize results", help="Visualizign the results")
+
+    parser_train.add_argument('--config', dest='config', default=DEFAULT_CONFIG, help='Configuration')
+
+    args = parser.parse_known_args()
+
+    if args[0].command == 'train':
+        train(parser, args[0])
+    elif args[0].command == 'eval':
+        test(parser, args[0])
+    elif args[0].command == 'visu':
+        visu(parser, args[0])
+
+if __name__ == '__main__':
+    main()
